---
title: "clustering_land_disp_id"
author: "Helio"
date: "2023-12-12"
output: html_document
---


cluster y displacements along with the landmark ids using neiborhood clustering
- this achieves that clusters are close together spatially (based on landmark id) and also have similar displacement values
- we could use this to remove artefactual points in component plots
```{r}


# tmp_testk1$nmf_k<- 1
# tmp_testk2$nmf_k<- 2
# tmp_testk3$nmf_k<- 3


dta_generated_1_pred1$nmf_k<- 1
dta_generated_2_1_pred$nmf_k<- 2
dta_generated_3_pred$nmf_k<- 3

colnames(dta_generated_1_pred1)
colnames(dta_generated_2_1_pred)   
colnames(dta_generated_3_pred)  


dta_generated_1_2_3_pred<-bind_rows(dta_generated_1_pred1,
          dta_generated_2_1_pred,
          dta_generated_3_pred)


# now compute the displacements and average acrposs videos

dta_generated_1_2_3_pred$expression<- str_extract(dta_generated_1_2_3_pred$filename, 
                                                  "(?<=posed)_.*?(?=_day)")

dta_generated_1_2_3_pred$filename

dta_generated_1_2_3_pred

dta_generated_1_2_3_pred_long<- dta_generated_1_2_3_pred%>%
          # subset(as.numeric(as.factor(filename)) ==100)%>%
       group_by(filename,expression,nmf_k, bin_frame )%>%
  summarise_if(is.numeric, mean,na.rm = T)%>%
     pivot_longer(cols = c(-filename,-expression,-nmf_k, -bin_frame), 
                  names_to = c(".value", "landmark"), 
                names_pattern = "([xy])_(\\d+)") %>%
   group_by(filename,nmf_k )%>%
  arrange(bin_frame, as.numeric(landmark))
    

dta_generated_1_2_3_pred_long
dta_generated_1_2_3_pred_long

dta_generated_1_2_3_pred_long$landmark<- as.numeric(dta_generated_1_2_3_pred_long$landmark)


dta_generated_1_2_3_pred_long$file_nmf<-paste0(dta_generated_1_2_3_pred_long$filename, paste0("_nmf",
                                                                                              dta_generated_1_2_3_pred_long$nmf_k))


dta_generated_1_2_3_pred_long_agg<- dta_generated_1_2_3_pred_long%>%
    # subset(as.numeric(filename)<3 & bin_frame<3 & nmf_k<2)%>%
  # subset(as.numeric(filename)<3 & bin_frame<3 & nmf_k<2)%>%
     # group_by(filename )%>%
    arrange(filename,nmf_k,bin_frame)%>%
  ungroup()%>%#just for safety
  # group so that displacement id computed within file name in each recreated data
  group_by(file_nmf, landmark) %>%
  mutate(
    x_displacement = x - lag(x, default = first(x)),
    y_displacement = y - lag(y, default = first(y))) %>%
  ungroup()%>%
   group_by(file_nmf,filename, expression, nmf_k, landmark,bin_frame)%>%
  summarise_if(is.numeric, mean,na.rm = T)

  # not sure about this step. lets stary by normalising within component
# dta_generated_1_2_3_pred_long_agg$landmark <- as.numeric(dta_generated_1_2_3_pred_long_agg$landmark)

#pay special attention to groupings, as a precaution, make sure to ungroup before any computations
 dta_generated_1_2_3_pred_long_agg
 
 dta_generated_1_2_3_pred_long_agg%>%
  ungroup()%>%
      # group_by(file_nmf)%>%
    mutate(x_sum_norm = normalize_between_0_and_1(x_displacement),
         y_sum_norm = normalize_between_0_and_1(y_displacement^2) #check this
         )%>%
    ungroup()%>%
   subset(file_nmf == "./cut_posed_angry_day2_p5.csv_nmf1") %>%
   ggplot(aes(x,y,colour = y_sum_norm))+
   geom_point()+
   geom_delaunay_segment2()+
       scale_y_reverse()+
      transition_time(bin_frame)  # Animate over the 'frame' variable
    ease_aes('linear')  #

    
    
    library(ggplot2)
library(gganimate)
library(ggforce)

# Assuming dta_generated_1_2_3_pred_long_agg is your data frame
# dta_optimized <- dta_generated_1_2_3_pred_long_agg %>%
#    subset(file_nmf == "./cut_posed_angry_day2_p5.csv_nmf1")
#   subset(bin_frame<15)

  dta_generated_1_2_3_pred_long_agg$x_path<- dta_generated_1_2_3_pred_long_agg$x
  dta_generated_1_2_3_pred_long_agg$y_path<-dta_generated_1_2_3_pred_long_agg$y
   # 
   # dta_generated_1_2_3_pred_long_agg$y_path<- if_else(landmark<17,
   #                                                     dta_generated_1_2_3_pred_long_agg$y_path,
   #                                                    landmark<17,
   #                                                     dta_generated_1_2_3_pred_long_agg$y_path,
   #                                                    
   #                                                    
   #                                                    
   #                                                     )
   # 
   # Define segments to connect
   
   # Creating a boundary polygon
dta_boundary <- dta_optimized[dta_optimized$bin_frame == 1, ] 


# Function to generate segment data inline
generate_segments <- function(df, indices) {
  rbind(
    data.frame(x = df$x[indices], y = df$y[indices],
               xend = df$x[c(indices[-1], indices[1])],
               yend = df$y[c(indices[-1], indices[1])]),
    data.frame(x = df$x[c(indices[-1], indices[1])], y = df$y[c(indices[-1], indices[1])],
               xend = df$x[indices],
               yend = df$y[indices])
  )
}

# for on the fly dsta subsetting = doesn't work
generate_segments <- function(indices) {
  data.frame(
    x = .data$x[indices],
    y = .data$y[indices],
    xend = .data$x[c(indices[-1], indices[1])],
    yend = .data$y[c(indices[-1], indices[1])]
  )
}

# Define landmarks for each feature
face_indices <- 0:16
mouth_indices <- 48:67
eyebrow_indices <- c(11:21, 22:26)
nose_indices <- c(27:30, 31:35)
eye_indices <- c(36:40, 42:47)
  



dta_generated_1_2_3_pred_long_agg<-
  
  dta_generated_1_2_3_pred_long_agg%>%
  mutate(landmark_group = case_when(
    landmark %in% 0:16 ~ 'face',
    landmark %in% 48:67 ~ 'mouth',
    landmark %in% c(11:21) ~ 'eyebrows1',
    landmark %in% c(22:26) ~ 'eyebrows2',
    landmark %in% c(27:30) ~ 'nose1',
     landmark %in% c(31:35) ~ 'nose2',
    landmark %in% c(36:41) ~ 'eyes1',
    landmark %in% c(42:47) ~ 'eyes2',
    TRUE ~ 'other'  # for any points not in the specified ranges
  ))

dta_generated_1_2_3_pred_long_agg$landmark_group

 dta_generated_1_2_3_pred_long_agg %>%
   # subset(as.numeric(as.factor(file_nmf)) ==32)%>%
  subset(file_nmf=="./cut_posed_angry_day1_p16.csv_nmf1")%>%
     mutate(y_sum_norm = if_else(landmark_group == "face", 0,y_sum_norm))%>%
ggplot(aes(x, y, fill =y_sum_norm)) +
   geom_point(colour = "white") +
   geom_voronoi_tile(alpha = .8) +
  geom_voronoi_segment(alpha = .1,colour = "white") +
   geom_path(aes(group = landmark_group),colour = "white")+
    
   scale_y_reverse() +
    theme_dark()+
  theme_void()+
  theme(plot.background = element_rect(fill = "black"),
         legend.position = "none")+
  
    scale_fill_viridis_c(option = "magma")+
   transition_time(bin_frame) +
   ease_aes('linear')
 
 
 t(as.data.frame(res_k3_fit_H))
 
as.data.frame( coef(res_k3))%>%
  mutate(comp = 1:n())%>%
  gather(key,value, -comp)%>%
  # group_by(key)%>%
  mutate(value_norm1 = scale(value))%>%
  ungroup()%>%
  # group_by(comp) %>%
  mutate(value_norm2 =normalize_between_0_and_1(value)) %>%
  ggplot(aes(comp,key, fill = value))+
  geom_tile()+
  scale_fill_viridis_c(option = "inferno")
```


```{r}
 dta_generated_1_2_3_pred_long_agg$landmark_group

 unique(dta_generated_1_2_3_pred_long_agg$nmf_k)
 
 dta_generated_1_2_3_pred_long_agg2<- dta_generated_1_2_3_pred_long_agg %>%
   # subset(as.numeric(as.factor(file_nmf)) ==11)%>%
   ungroup()%>%
   group_by(nmf_k,landmark,landmark_group)%>%
   summarise_if(is.numeric, mean, na.rm = T)%>%
   ungroup()%>%
   group_by(nmf_k)%>%
        mutate(y_sum_norm = if_else(landmark_group == "face", 0,y_sum_norm))%>%
   mutate(y_sum_norm = normalize_between_0_and_1(y_sum_norm))


 
 dta_generated_1_2_3_pred_long_agg2%>%
   

ggplot(aes(x, y, fill = factor(nmf_k), colour = factor(nmf_k))) +
      # geom_delaunay_tile(colour = "white")+
   geom_voronoi_tile(aes(alpha = .1*y_sum_norm)) +
  geom_voronoi_segment(alpha = .5,colour = "white") +
   # geom_path(aes(group = landmark_group),colour = "white", alpha = .7)+
     # geom_point(aes(alpha = .1*y_sum_norm)) +
      geom_point(colour = "white") +
   scale_y_reverse() +
      facet_grid(~nmf_k)+
    theme_dark()+
  theme_void()+
  theme(plot.background = element_rect(fill = "black"),
         legend.position = "none")+
          scale_color_brewer(palette = "Dark2")
 
 
 
 dta_generated_1_2_3_pred_long_agg2
 
 
  dta_generated_1_2_3_pred_long_agg2%>%
 ungroup()%>%
    # group_by(nmf_k)%>%
    # mutate(y_sum_norm = scale(y_sum_norm))%>%
ggplot(aes(x, y, fill = y_sum_norm)) +
   geom_voronoi_tile(aes(fill =y_sum_norm))+  
    geom_voronoi_segment(alpha = .1,colour = "white") +
   geom_path(aes(group = landmark_group),colour = "white", alpha = .7)+
     # geom_point(aes(alpha = .1*y_sum_norm)) +
      geom_point(colour = "white") +
   scale_y_reverse() +
      facet_grid(~nmf_k)+
    theme_dark()+
  theme_void()+
  theme(plot.background = element_rect(fill = "black"),
         legend.position = "none")+
    scale_fill_viridis_c(option = "inferno")


  
  dta_generated_1_2_3_pred_long_agg2%>%
 ungroup()%>%
    # group_by(nmf_k)%>%
    # mutate(y_sum_norm = scale(y_sum_norm))%>%
ggplot(aes(x, y, fill = y_sum_norm, colour = y_sum_norm)) +

 geom_delaunay_tile()+
        geom_voronoi_tile(aes(fill =y_sum_norm))+  
     geom_delaunay_segment2()+
   geom_path(aes(group = landmark_group),colour = "white", alpha = .7)+
     # geom_point(aes(alpha = .1*y_sum_norm)) +
      geom_point(colour = "white") +
   scale_y_reverse() +
      facet_grid(~nmf_k)+
    theme_dark()+
  theme_void()+
  theme(plot.background = element_rect(fill = "black"),
         legend.position = "none")+
    scale_fill_viridis_c(option = "inferno")+
     scale_colour_viridis_c(option = "inferno")
  
  range(res_k3_fit_H)
```

due a linear change just so we can compute difference map


```{r}
res_k3_fit_H

activations%>%
  mutate(normalize_row())



activations<- res_k3_fit_H

activations


# Assuming your original dataframe is named 'dta_original'
# Extract only the AU columns (assuming they start from the second column)
dta_AUs <- activations[, 2:ncol(activations)]





# Sample data (replace with your dataset)
# tmp_original <- data.frame(
#   id = c("A", "B", "C"),
#   col1 = c(10, 20, 30),
#   col2 = c(40, 50, 60),
#   col3 = c(70, 80, 90)
# )

# Create a sequence of 15 steps
steps <- 1:10

# Initialize a list to store the step dataframes
list_step_dfs <- list()

# Loop through each step and each row
for (i in steps) {
  # Calculate the proportion of the target value for this step
  proportion <- i / max(steps)
  
  # Scale values for all rows at this step and retain identifiers
  tmp_step_df <- cbind(activations[1], activations[-1] * proportion)
  tmp_step_df$step <- i
  
  # Add the step dataframe to the list
  list_step_dfs[[i + 1]] <- tmp_step_df
}

# Combine all step dataframes into one
dta_steps <- do.call(rbind, list_step_dfs)

# View the result
print(head(dta_steps))


dta_steps%>%
  gather(key, value,- component,-step)%>%
  group_by(key,component)%>%
  summarise_if(is.numeric, max) %>%
ggplot(aes(key, value))+
  stat_summary(geom = "pointrange")+
  facet_grid(~component)

dta_steps
# predict()

# use this lienar animation to predict data\
dta_lin_steps_pred <- predict(mod_pls,
                              dta_steps , ncomp=17)

dta_lin_steps_pred1<- as.data.frame(dta_lin_steps_pred)

dta_lin_steps_pred1$component<- dta_steps$component
dta_lin_steps_pred1$step<- dta_steps$step


dta_lin_steps_pred1%>%
  subset(component == 1)%>%
  
  
   pivot_longer(cols = c(-step,-component), names_to = c(".value", "landmark"), 
                names_pattern = "([xy])_(\\d+)") %>%
  arrange(step, as.numeric(landmark))%>%
  ggplot(aes(x,y))+
  geom_point()+
    scale_y_reverse()+
    # geom_text(aes(label = frame_group))+
    ggtitle("approx")+
       transition_time(step) + # Animate over the 'frame' variable
    ease_aes('linear')  



dta_lin_steps_pred1%>%
  subset(component == 2)%>%
  
  
   pivot_longer(cols = c(-step,-component), names_to = c(".value", "landmark"), 
                names_pattern = "([xy])_(\\d+)") %>%
  arrange(step, as.numeric(landmark))%>%
  ggplot(aes(x,y))+
  geom_point()+
    scale_y_reverse()+
    # geom_text(aes(label = frame_group))+
    ggtitle("approx")+
       transition_time(step) + # Animate over the 'frame' variable
    ease_aes('linear')  


dta_lin_steps_pred1%>%
  subset(component == 3)%>%
  
  
   pivot_longer(cols = c(-step,-component), names_to = c(".value", "landmark"), 
                names_pattern = "([xy])_(\\d+)") %>%
  arrange(step, as.numeric(landmark))%>%
  ggplot(aes(x,y))+
  geom_point()+
    scale_y_reverse()+
    # geom_text(aes(label = frame_group))+
    ggtitle("approx")+
       transition_time(step) + # Animate over the 'frame' variable
    ease_aes('linear')  

dta_lin_steps_pred1

dta_lin_steps_pred1%>%
  # subset(component == 2)%>%
  
  
   pivot_longer(cols = c(-step,-component), names_to = c(".value", "landmark"), 
                names_pattern = "([xy])_(\\d+)") %>%
  mutate(landmark = as.numeric(landmark))%>%
  arrange(component,landmark)%>%
group_by(component, landmark) %>%
  mutate(
    x_displacement = x - lag(x, default = first(x)),
    y_displacement = y - lag(y, default = first(y))) %>%
  ungroup()%>%
   # group_by(filename, expression, nmf_k, landmark,bin_frame)%>%
  # summarise_if(is.numeric, mean,na.rm = T)
   mutate(landmark_group = case_when(
    landmark %in% 0:16 ~ 'face',
    landmark %in% 48:67 ~ 'mouth',
    landmark %in% c(11:21) ~ 'eyebrows1',
    landmark %in% c(22:26) ~ 'eyebrows2',
    landmark %in% c(27:30) ~ 'nose1',
     landmark %in% c(31:35) ~ 'nose2',
    landmark %in% c(36:41) ~ 'eyes1',
    landmark %in% c(42:47) ~ 'eyes2',
    TRUE ~ 'other'  # for any points not in the specified ranges
  )) %>%

group_by(component) %>%
  mutate(y_displacement = if_else(landmark_group == "face", 0,y_displacement))%>%
   # mutate(y_sum_norm = normalize_between_0_and_1(y_sum_norm))
 mutate(x_sum_norm = normalize_between_0_and_1(x_displacement^2),
         y_sum_norm = normalize_between_0_and_1(y_displacement^2) #check this
         )%>%
  group_by(component,landmark,landmark_group) %>%
    summarise_if(is.numeric, mean,na.rm = T)%>%
  # mutate(y_sum_norm = if_else(landmark_group == "face", 0,y_sum_norm))%>%
   # mutate(y_sum_norm = normalize_between_0_and_1(y_sum_norm))
  
  group_by(component) %>%
 mutate(x_sum_norm = normalize_between_0_and_1(x_sum_norm),
         y_sum_norm = normalize_between_0_and_1(y_sum_norm) #check this
         )%>%
 #  
 
  
  ggplot(aes(x, y, fill =y_sum_norm)) +
   geom_point(colour = "white") +
   geom_voronoi_tile(alpha = .8) +
  geom_voronoi_segment(alpha = 1,colour = "white") +
  facet_grid(~component)+
   geom_path(aes(group = landmark_group),colour = "white")+
    
   scale_y_reverse() +
    theme_dark()+
  theme_void()+
  theme(plot.background = element_rect(fill = "black"),
  legend.position = "none")+
  
    scale_fill_viridis_c(option = "inferno")
   # transition_time(step) +
   # ease_aes('linear')
  
 mod_pls$loadings 
 mod_pls$coefficients
 

```


 # check that this is sensible, plot the full changes, note that these full changes won't correspond to reduced NMF values, so perhaps the clustering might allow us to kind of reduce the dimensionality
    options(scipen = 999)


original data


```{r}
colnames(dta_all_aligned_landmarks_posed_corrected_AUS_norm_downs_10th)
```

```{r}

dta_lin_steps_pred1%>%
  # subset(component == 2)%>%
  
  
   pivot_longer(cols = c(-step,-component), names_to = c(".value", "landmark"), 
                names_pattern = "([xy])_(\\d+)") %>%
  mutate(landmark = as.numeric(landmark))%>%
  arrange(component,landmark)%>%
group_by(component, landmark) %>%
  mutate(
    x_displacement = x - lag(x, default = first(x)),
    y_displacement = y - lag(y, default = first(y))) %>%
  ungroup()%>%
   # group_by(filename, expression, nmf_k, landmark,bin_frame)%>%
  # summarise_if(is.numeric, mean,na.rm = T)
   mutate(landmark_group = case_when(
    landmark %in% 0:16 ~ 'face',
    landmark %in% 48:67 ~ 'mouth',
    landmark %in% c(11:21) ~ 'eyebrows1',
    landmark %in% c(22:26) ~ 'eyebrows2',
    landmark %in% c(27:30) ~ 'nose1',
     landmark %in% c(31:35) ~ 'nose2',
    landmark %in% c(36:41) ~ 'eyes1',
    landmark %in% c(42:47) ~ 'eyes2',
    TRUE ~ 'other'  # for any points not in the specified ranges
  )) %>%

group_by(component) %>%
  mutate(y_displacement = if_else(landmark_group == "face", 0,y_displacement))%>%
   # mutate(y_sum_norm = normalize_between_0_and_1(y_sum_norm))
 mutate(x_sum_norm = normalize_between_0_and_1(x_displacement^2),
         y_sum_norm = normalize_between_0_and_1(y_displacement^2) #check this
         )%>%
  group_by(component,landmark,landmark_group) %>%
    summarise_if(is.numeric, mean,na.rm = T)%>%
  # mutate(y_sum_norm = if_else(landmark_group == "face", 0,y_sum_norm))%>%
   # mutate(y_sum_norm = normalize_between_0_and_1(y_sum_norm))
  
  group_by(component) %>%
 mutate(x_sum_norm = normalize_between_0_and_1(x_sum_norm),
         y_sum_norm = normalize_between_0_and_1(y_sum_norm) #check this
         )%>%
 #  
 
  
  ggplot(aes(x, y, fill =y_sum_norm)) +
   geom_point(colour = "white") +
   geom_voronoi_tile(alpha = .8) +
  geom_voronoi_segment(alpha = .1,colour = "white") +
  facet_grid(~component)+
   geom_path(aes(group = landmark_group),colour = "white")+
    
   scale_y_reverse() +
    theme_dark()+
  theme_void()+
  theme(plot.background = element_rect(fill = "black"),
  legend.position = "none")+
  
    scale_fill_viridis_c(option = "inferno")
   # transition_time(step) +
   # ease_aes('linear')
  
 mod_pls$loadings 
 mod_pls$coefficients


```

# just run the clustering here

```{r}
dta_generated_1_2_3_pred_long_agg2
dta_generated_1_2_3_pred_disp_agg<- dta_generated_1_2_3_pred_disp%>%
  group_by(landmark, nmf_k)%>%
  summarise_if(is.numeric, mean, na.rm. =T)


 dta_generated_1_2_3_pred_disp<- dta_generated_1_2_3_pred_long_agg2

 # just scale this here so that we don't need to scale it during clustering
dta_generated_1_2_3_pred_disp$land_scale<- normalize_between_0_and_1(as.numeric(dta_generated_1_2_3_pred_disp$landmark))

dta_generated_1_2_3_pred_disp$nmf_k<- as.character(dta_generated_1_2_3_pred_disp$nmf_k)

 # setwd("/Users/pw22812/Library/CloudStorage/GoogleDrive-helioclemente.c@gmail.com/My Drive/2022 - University Of Birmingham/HaloStudy/Data/ExportedSets")
write_csv(dta_generated_1_2_3_pred_disp, "dta_generated_1_2_3_pred_disp.csv")




# Example data
set.seed(123)
colnames(dta_generated_1_2_3_pred_disp_agg)


dta_generated_1_2_3_pred_disp_agg<- dta_generated_1_2_3_pred_disp
colnames(dta_generated_1_2_3_pred_disp_agg)

rslt_clusters <- kmeans(dta_generated_1_2_3_pred_disp_agg[,c(13,10)], centers=3)

# Visualize the results

dta_generated_1_2_3_pred_disp_agg%>%
ggplot( aes(land_scale, y_sum_norm, color=factor(rslt_clusters$cluster))) +
  geom_point() +
  labs(color='Cluster')+
  facet_grid(~nmf_k)

dta_generated_1_2_3_pred_disp_agg$clust_k4<- rslt_clusters$cluster



dta_generated_1_2_3_pred_disp_agg%>%
  ggplot(aes(x,y, colour = factor(clust_k4)))+
  geom_point()+
  geom_text(aes(label = landmark))+
  scale_y_reverse()+
  facet_grid(~nmf_k)


```


dta_generated_1_2_3_pred_disp_agg$clust_k4_fixed<- dta_generated_1_2_3_pred_disp_agg$clust_k4


dta_generated_1_2_3_pred_disp_agg$clust_k4_fixed<- if_else(dta_generated_1_2_3_pred_disp_agg$landmark == 48,4,
                                                           if_else(dta_generated_1_2_3_pred_disp_agg$landmark == 49, 4,dta_generated_1_2_3_pred_disp_agg$clust_k4_fixed))




dta_generated_1_2_3_pred_disp_agg$clust_k4_fixed<- if_else(dta_generated_1_2_3_pred_disp_agg$landmark == 33,2,
                                                           if_else(dta_generated_1_2_3_pred_disp_agg$landmark == 34, 2,
                                                                   if_else(dta_generated_1_2_3_pred_disp_agg$landmark == 35, 2
                                                                   
                                                                ,dta_generated_1_2_3_pred_disp_agg$clust_k4_fixed)))



dta_generated_1_2_3_pred_disp_agg$clust_k4_fixed<- if_else(dta_generated_1_2_3_pred_disp_agg$landmark == 16,3,
dta_generated_1_2_3_pred_disp_agg$clust_k4_fixed)
                                                                   
                                                                

dta_generated_1_2_3_pred_disp_agg%>%
  ungroup()%>%
    mutate(y_norm2 = normalize_between_0_and_1(y_sum_norm))%>%
  # group_by(nm)%>%
  # summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(x,y, colour = y_sum_norm))+
    geom_point()+
  # geom_point(aes(colour = factor(clust_k4_fixed)))+
  # geom_text(aes(label = landmark))+
  scale_y_reverse()+
  facet_grid(~nmf_k)+
  geom_delaunay_segment2(alpha = .2)



dta_generated_1_2_3_pred_disp_agg%>%
  group_by(nmf_k)%>%
  mutate(y_norm2 = normalize_between_0_and_1(y_sum_norm))%>%
  
  # summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(x,y, colour = y_norm2))+
    geom_point()+
  # geom_point(aes(colour = factor(clust_k4_fixed)))+
  # geom_text(aes(label = landmark))+
  scale_y_reverse()+
  # facet_grid(~nmf_k)+
  geom_delaunay_segment2(alpha = .2)+
  scale_colour_viridis_c(option = "magma")+
  facet_grid(nmf_k~clust_k4_fixed)

```