---
title: "delaunay faces and meshes"
author: "Helio"
date: "2022-12-25"
output: html_document
---







# landmarks and normalisation

```{r}
require(data.table)

View(df_OF_output_land)
df_OF_output_land

colnames(df_OF_output_land)
unique(df_OF_output_land$filename)



# lets start by taking one single subject and plotting the change

# but to do that we fist need to normalise and alligh

library(data.table)


df_OF_output_land$filename
# select one test sample
test_happy <-df_OF_output_land%>%
  subset(filename == "./cut_posed_happy_day2_p6.csv")
  
test_happy_dcast<- df_OF_output_land%>%
group_by(filename)%>%
  gather(key, value, -frame, -timestamp,-filename) %>%
  mutate(coordinate = substr(key,1,1))%>%
  mutate(lanmark_id = substr(key,3,4)) %>%
  dcast(filename+lanmark_id+frame+timestamp~coordinate, value.var = "value",  mean)

# now compute differences before doing any alligning, etc
# but lets normalise to max

maxnormalize <- function(x, ...) {
    return((x - min(x,na.rm = T, ...)) /(max(x,na.rm = T, ...) - min(x,na.rm = T, ...))) }


# norm and diff
options(scipen = 999)

unique(test_happy_dcast$filename)

max(test_happy_dcast$frame)

test_happy_dcast<- test_happy_dcast %>%
      group_by(filename,frame)%>%
  mutate(x_new_norm = maxnormalize(x),
         y_new_norm = maxnormalize(y))%>%
  group_by(lanmark_id)%>%
  mutate(x_norm_diff= x_new_norm - lag(x_new_norm),
         y_norm_diff= y_new_norm - lag(y_new_norm))%>%
    mutate(x_norm_diff_abs= (x_norm_diff),
         y_norm_diff_abs= (y_norm_diff))%>%
  # compute a summ - also consider a roling sum
   mutate(x_norm_diff_abs_sum= sum(x_norm_diff_abs, na.rm = TRUE),
         y_norm_diff_abs_sum= sum(y_norm_diff_abs, na.rm = TRUE))%>%
  

  
  # do a cummulative summ
  # subset(frame == 100)%>%
  mutate(fill_x_y = (x_norm_diff_abs_sum+y_norm_diff_abs_sum)/2)%>%
  group_by(lanmark_id)%>%
  #the line below just ignores NA (introduced in lag) which would throw error to cumsum otehrwise
      mutate(cum_x_norm_abs_diff = cumsum(ifelse(is.na(x_norm_diff_abs), 0, x_norm_diff_abs)) + x_norm_diff_abs*0,
             cum_y_norm_abs_diff = cumsum(ifelse(is.na(y_norm_diff_abs), 0, y_norm_diff_abs)) + y_norm_diff_abs*0)%>%
  mutate(cum_x_y_norm_abs_diff_mean_fill = ((cum_x_norm_abs_diff+cum_y_norm_abs_diff)/2))%>%
  # just y
  mutate(cum_x_y_norm_abs_diff_mean_fill_norm = maxnormalize(cum_y_norm_abs_diff))
  # summarise_if(is.numeric, max,na.rm = T)%>%
  
  # this plots the largest change
  # ggplot(aes(x = x_new_norm, y = 1-y_new_norm, fill = fill_x_y, colour = fill_x_y))+
  # geom_point()
# this plots the degree ochangedFiles( # this plots the largest change
test_happy_dcast%>%
  ggplot(aes(x = x_new_norm, y = 1-y_new_norm, colour = cum_x_y_norm_abs_diff_mean_fill_norm))+
  geom_point(alpha = .8)+
     scale_color_viridis_c(option = "magma")
  
  # ggforce::geom_delaunay_segment(data = test_happy_dcast_min, aes(x = x_new_norm, y = 1-y_new_norm, colour =1-cum_x_y_norm_abs_diff_mean_fill))
  
  # ggplot(aes(as.numeric(frame), x_norm_diff_abs))+
  # geom_line()
  # geom_line(aes(y = x_norm_diff_abs), linetype = "dotted")
  # 

test_happy_dcast
  

test_happy_dcast%>%
  subset(frame == 120)%>%

         summarise_if(is.numeric, mean,na.rm = T)%>%
    ggplot(aes(x = x_new_norm, y = 1-y_new_norm, colour = cum_x_y_norm_abs_diff_mean_fill_norm, fill = cum_x_y_norm_abs_diff_mean_fill_norm))+

     geom_point(aes(colour = cum_x_y_norm_abs_diff_mean_fill_norm),alpha = .8)+
  # ggforce::stat_delvor_summary()
  geom_delaunay_segment2()+
     scale_color_viridis_c(option = "magma")
    
  
  
# 
# library(deldir)
#   frame_1<- subset(test_happy_dcast, test_happy_dcast$frame == 1)
# dxy <- deldir(frame_1$x_new_norm, frame_1$y_new_norm)

maxnormalize <- function(x, ...) {
    return((x - min(x, ...)) /(max(x, ...) - min(x, ...))) }

df_OF_output_land_f10_dcast_norm<- df_OF_output_land_f10_dcast%>%
    group_by(filename,frame)%>%
  mutate(x_new_norm = maxnormalize(x),
         y_new_norm = maxnormalize(y))
```



<!-- proper alligments etc -->
maxnormalize <- function(x, ...) {
    return((x - min(x, ...)) /(max(x, ...) - min(x, ...))) }

df_OF_output_land_f10_dcast_norm<- df_OF_output_land_f10_dcast%>%
    group_by(filename,frame)%>%
  mutate(x_new_norm = maxnormalize(x),
         y_new_norm = maxnormalize(y))

df_OF_output_land_f10_dcast_norm%>%
  group_by(lanmark_id)%>%
summarise_if(is.numeric, mean, na.rm = T)%>%
  ggplot(aes(x_new_norm, y_new_norm))+
  geom_point()+
  ylim(1,0)

df_OF_output_land_f10_dcast_normagg<-df_OF_output_land_f10_dcast_norm%>%
  group_by(lanmark_id)%>%
summarise_if(is.numeric, mean, na.rm = T)

# First, isolate the points of interest (the subject's left and right eyes)

left_eye  <- df_OF_output_land_f10_dcast_normagg[df_OF_output_land_f10_dcast_normagg$lanmark_id == 42,]
right_eye <- df_OF_output_land_f10_dcast_normagg[df_OF_output_land_f10_dcast_normagg$lanmark_id == 39,] 

# Now find the difference in the y co-ordinates and x co-ordinates between these two points:

diff_x <- left_eye$x_new_norm - right_eye$x_new_norm
diff_y <- left_eye$y_new_norm - right_eye$y_new_norm


# The arctangent of the ratio will be the angle you need to rotate all the points by:

theta  <- atan2(-diff_y, diff_x)

mat <- matrix(c(cos(theta), sin(theta), -sin(theta), cos(theta)), 2)

df_OF_output_land_f10_dcast_normagg[,8:9] <- t(apply(df_OF_output_land_f10_dcast_normagg[,6:7], 1, function(x) mat %*% x))


df_OF_output_land_f10_dcast_normagg %>%
  ggplot(aes(V1, V2, label = lanmark_id)) + 
  geom_point(color = 'gray') +
  geom_text() +
  scale_y_reverse() +
  theme_bw()


df_OF_output_land_f10_dcast_normagg


install.packages("ggvoronoi")

?ggvoronoi::stat_voronoi
write_csv(df_OF_output_land_f10_dcast_normagg, "df_OF_output_land_f10_dcast_normagg.csv")
df_OF_output_land_f10_dcast_normagg %>%
  arrange(lanmark_id)%>%
  ggplot(aes(V1, V2, label = lanmark_id)) + 
  ggvoronoi::stat_voronoi(geom="path", outline = c(df_OF_output_land_f10_dcast_normagg$V1, df_OF_output_land_f10_dcast_normagg$V2)) +
  geom_point()+
  ylim(1,0)


write_csv(pca_AUs, "pca_AUs.csv")


# coded landmarks
library(readxl)
codeLandmarksAUs <- read_excel("codeLandmarksAUs.xlsx")
View(codeLandmarksAUs)
codeLandmarksAUs%>%
  arrange(lanmark_id)%>%
  ggplot(aes(V1, V2, label = lanmark_id)) + 
  # geom_path()+
  # ggvoronoi::stat_voronoi(geom="path", outline = c(df_OF_output_land_f10_dcast_normagg$V1, df_OF_output_land_f10_dcast_normagg$V2)) +
  geom_point()+
  ylim(1,0)+
  theme_bw()

codeLandmarksAUs


df_OF_output_AUsW_unblind_posed_binned1

library(readxl)
LANDMARKNMF <- read_excel("LANDMARKNMF.xlsx")
View(LANDMARKNMF)

LANDMARKNMF[is.na(LANDMARKNMF)] <- 0

pairing AOIs to landmarks

Lanmarking
```{r}
library(readxl)
LANDMARKNMF <- read_excel("Library/CloudStorage/GoogleDrive-helioclemente.c@gmail.com/My Drive/2022 - University Of Birmingham/HaloStudy/Data/LANDMARKNMF.xlsx")
View(LANDMARKNMF)
LANDMARKNMF


NMFresk3test<- as.data.frame(res_k3@fit@H)%>%
  mutate(component = 1:n())%>%
  gather(AU, coef, -component)%>%
  group_by(component)%>%
  mutate(max_comp = max(coef),
         coef = coef/max_comp,
         # AU = substring(AU,8,40),
         AU_code = substring(AU,4,5)
         )%>%
  arrange(AU_code)



LANDMARKNMF


NMFresk3test

LANDMARKNMF<- LANDMARKNMF1
colnames(LANDMARKNMF)
colnames(LANDMARKNMF[,c(1,8:9,12:31)])

LANDMARKNMF_dcast<- LANDMARKNMF[,c(1,8:9,12:31)]%>%
gather(AU, land1_0,-c(1:3,21:23))%>%
gather(comp, land1_0_nmf, -c(1:3,7:8))

library(ggvoronoi)

left_join(LANDMARKNMF_dcast,NMFresk3test)%>%
  mutate(V1_1 = if_else(land1_0_nmf == 1, V1, NULL),
         V2_2 = if_else(land1_0_nmf == 1, V2, NULL)) %>%
  group_by(lanmark_id, component, AU)%>%
  summarise_if(is.numeric, mean, na.rm = T) %>%
  mutate(coef2 = if_else(land1_0_nmf == 1, coef,0))%>%
  ggplot(aes(V1_1, V2_2, color = coef2))+
  geom_point(aes(size = coef2), alpha = .5)+
  # geom_point( aes(x = V1_1, y = V2_2, color = coef2, fill = coef2))+
  ggvoronoi::stat_voronoi(geom="path")+
  geom_point(aes(x = V1, y = V2))+
  # geom_point(aes(size = coef), alpha = .1)+
  ylim(1,0)+
  facet_grid(~component)+
  scale_color_viridis_c(option = "magma")

  
LANDMARKNMF_dcast

# 

install.packages("ggforce")
library(ggforce)
left_join(LANDMARKNMF_dcast,NMFresk3test)%>%
  mutate(V1_1 = if_else(land1_0 == 1, V1, NULL),
         V2_2 = if_else(land1_0 == 1, V2, NULL)) %>%
  # group_by(lanmark_id)%>%
  # summarise_if(is.numeric, mean, na.rm = T) %>%
  mutate(coef2 = if_else(land1_0 == 1, coef,0))%>%
  ggplot(aes(V1_1, V2_2, color = coef2, fill=coef2 ))+
  geom_point(aes(size = coef2), alpha = .5)+
    # ggvoronoi::stat_voronoi(geom="path" )
  # geom_point( aes(x = V1_1, y = V2_2, color = coef2, fill = coef2))+

  geom_point(aes(x = V1, y = V2))+
  # geom_point(aes(size = coef), alpha = .1)+
  ylim(1,0)+
  facet_grid(~component)+
    geom_delaunay_tile(aes(x =V1, V2, fill = lanmark_id), alpha = 0.3, colour = 'black')+
  # geom_delaunay_segment2()+
  scale_color_viridis_c(option = "magma")

NMFresk3test$component
LANDMARKNMF_dcast$component<- as.numeric(substr(LANDMARKNMF_dcast$comp,4,4))

left_join(LANDMARKNMF_dcast,NMFresk3test)%>%
  mutate(V1_1 = if_else(land1_0 == 1, V1, NULL),
         V2_2 = if_else(land1_0 == 1, V2, NULL)) %>%
  # group_by(lanmark_id)%>%
  # summarise_if(is.numeric, mean, na.rm = T) %>%
  mutate(coef2 = if_else(land1_0 == 1, coef,0))%>%
  ggplot(aes(V1_1, V2_2, color = coef2, fill=coef2 ))+
  geom_point(aes(size = coef2), alpha = .5)+
    # ggvoronoi::stat_voronoi(geom="path" )
  # geom_point( aes(x = V1_1, y = V2_2, color = coef2, fill = coef2))+

  geom_point(aes(x = V1, y = V2))+
  # geom_point(aes(size = coef), alpha = .1)+
  ylim(1,0)+
  facet_grid(~component)+
    geom_delaunay_tile(aes(x =V1, V2), alpha = 0.1, colour = 'black')+
      geom_delaunay_segment2(aes(x =V1, V2, colour = coef2))+
  # geom_delaunay_segment2()+
  scale_color_viridis_c(option = "magma")

```
