---
title: "halo_facestudy_spoken_analysis"
author: "Helio"
date: '2022-08-30'
output: html_document
---



dependencies: preprocss_halofaces.Rmd
df_OF_output_AUsW_unblind_posed_binned

related script:analysys_halofacestudy.Rmd
related data: df_OF_output_AUsW_unblind_posed



for the actual analyses we want
1- learn spatiotemporal structure suing NMF
2 - does drug vs no drug differ in NMF metrics?
3- can we separate groups based on NMF components using BADIA

spatiotemporal dynamics
- movement substates (initiation, sustainment, etc)
- if we use kmean clustering, do we have differences into how many substaes are there
- or if we use a fixed number of substates, are there significant temporal differences (e.g. duration, recurrence)

preferences
```{r}
library(tidyverse)
library(data.table)

library(NMF)

```

for the NMF we will start with k = 3 given our findings in the posed (we have a good prior for 3). 
But then we will also do 1 to 4 to to compare.

fit nmf just spoken
```{r}

unique(df_OF_output_AUsW_unblind_spoken1_2_binned$posed.spoken)

df_OF_output_AUsW_unblind_spoken1_2$bin

# use only the "spoken" condition
df_OF_output_AUsW_unblind_spoken1_binned<- subset(df_OF_output_AUsW_unblind_spoken1_2_binned,
                                           posed.spoken == "spoken")



# fit
colnames(df_OF_output_AUsW_unblind_spoken1_binned)
res_k3_spoken1 <- NMF::nmf(df_OF_output_AUsW_unblind_spoken1_binned[,17:33], r = 3, 
                  nrun = 200, #number of runs to try and update for
                  seed=123456, #specific seed for reproducibility
                 .options = list( 'v')) #verbose



# plot(res_k3_spoken1) - this only work for multyiple fits with multiple ks
# summary(res_k3_spoken1) #dont run

# basis components 
NMF::basismap(res_k3_spoken1) # weights/ amplitudes
# memory exhaust - takes a lot of time

# mixture coefficients 
coefmap(res_k3_spoken1) #hidden variables

# access more info
# res_k3_em

```


some custom visualisations

custom visalisation of H (mixing components)
```{r}
# chool_talk$AU_NM 

as.data.frame(res_k3_spoken1@fit@H)%>%
  mutate(component = 1:n())%>%
  gather(AU, coef, -component)%>%
  group_by(component)%>%
  mutate(max_comp = max(coef),
         coef = coef/max_comp,
         # AU = substring(AU,8,40),
         AU_code = substring(AU,4,5)
         )%>%
  arrange(AU_code)%>%
  ggplot(aes(component,AU, fill = coef))+
  geom_tile()+
  theme_classic()+
  # scale_fill_viridis_()
  scale_fill_viridis_c(option = "inferno")+
  xlab("K")+
  p$graphstyle_int+
guides(fill=guide_colorbar(ticks.colour = NA))

```


store components in the dataset
```{r}
# store nmftable in DF
df_OF_output_AUsW_unblind_spoken1$NMFtable_k3<- as.data.frame(res_k3_spoken1@fit@W)$V1

# store components
df_OF_output_AUsW_unblind_spoken1_binned$k3_comp1 = as.data.frame(res_k3_spoken1@fit@W)$V1
df_OF_output_AUsW_unblind_spoken1_binned$k3_comp2 = as.data.frame(res_k3_spoken1@fit@W)$V2
df_OF_output_AUsW_unblind_spoken1_binned$k3_comp3 = as.data.frame(res_k3_spoken1@fit@W)$V3



# visualisation based on time


# chool_talk$ts_smooth<- 

colnames(df_OF_output_AUsW_unblind_spoken1_binned)
# colnames(  df_OF_output_AUsW_unblind_spoken1[,c(1,6:7,9:10,33:35)])
  
  
  df_OF_output_AUsW_unblind_spoken1_binned[,c(1,2:3,9:10,34:36)]%>%
  gather(component, coef,-bin_frame, -subject, -expression, -drug.placebo,-filename)%>%
  
      group_by(filename,component,subject,expression)%>%
  mutate(coef_max = max(coef),
         coef = coef/coef_max) %>%
  
  group_by(expression, component, bin_frame,subject)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(Dataset, coef , color = Dataset, fill = Dataset))+
  ggplot(aes(bin_frame, coef, color = component))+
  geom_smooth()+
  # geom_smooth(aes(group = subject), se = F)+
  # stat_summary(aes(group = subject, color = component), geom = "smooth")+
  facet_grid(~expression )+
  theme_classic()+
   xlab("time bin")+
  p$graphstyle_int+
   scale_color_viridis_d(option = "magma")
  
  
  # ts by expression
   df_OF_output_AUsW_unblind_spoken1_binned[,c(1,2:3,9:10,34:36)]%>%
  gather(component, coef,-bin_frame, -subject, -expression, -drug.placebo,-filename)%>%
  
      group_by(filename,component,subject,expression)%>%
  mutate(coef_max = max(coef),
         coef = coef/coef_max) %>%
  
  group_by(expression, component, bin_frame,subject)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(Dataset, coef , color = Dataset, fill = Dataset))+
  ggplot(aes(bin_frame, coef, color = expression))+
  geom_smooth()+
  # geom_smooth(aes(group = subject), se = F)+
  # stat_summary(aes(group = subject, color = component), geom = "smooth")+
  facet_grid(~component  )+
  theme_classic()+
   xlab("time bin")+
  p$graphstyle_int+
   scale_color_viridis_d(option = "magma")
  
  
  # heatmap
  
  
  # chool_talk$ts_hm<-
df_OF_output_AUsW_unblind_spoken1_binned[,c(1,2:3,9:10,34:36)]%>%
  gather(component, coef,-bin_frame, -subject, -expression, -drug.placebo,-filename)%>%
  group_by(filename,component)%>%
  mutate(coef_max = max(coef),
         coef = coef/coef_max)%>%
  # mutate_at(c("coef"), scale)%>%
  group_by(component, expression, bin_frame)%>%

  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(Dataset, coef , color = Dataset, fill = Dataset))+
  ggplot(aes(bin_frame, component, fill= coef))+
  geom_tile()+
  xlab("time bin")+
  scale_fill_viridis_c(option = "magma")+
  # geom_smooth(se = F)+
  facet_grid(~expression)+
  theme_classic()+
  p$graphstyle_int+
  guides(fill=guide_colorbar(ticks.colour = NA))+
  theme(panel.spacing = unit(1, "cm"))




library(patchwork)
# 
# chool_talk$ts_nmf_heat_NMF <- (chool_talk$ts_smooth/
#   chool_talk$ts_hm)+
#   plot_layout(heights = c(1,2))
# 
# chool_talk$ts_nmf_heat_NMF
# 
# ggsave("ts_nmf_heat_NMF.tiff", chool_talk$ts_nmf_heat_NMF, device = "tiff",
#        width = 10, height = 7, dpi = 800)

```

combine sooken and posed

```{r}
spoken_NMF<- df_OF_output_AUsW_unblind_spoken1_binned[,c(1,2:3,9:10,34:36)]

posed_NMF<- 
df_OF_output_AUsW_unblind_posed_binned[,c(1,2:3,9:10,34:36)]

df_OF_output_AUsW_unblind_spoken1_binned$k3_comp3

posed_NMF$k3_comp1<- posed_NMF$comp1
posed_NMF$k3_comp2<- posed_NMF$comp3
posed_NMF$k3_comp3<- posed_NMF$comp2

posed_NMF$comp1<- NULL
posed_NMF$comp2<- NULL

posed_NMF$comp3<- NULL

posed_NMF$posed_spoken<- "posed"
spoken_NMF$posed_spoken<- "spoken"


bind_rows(posed_NMF, spoken_NMF)%>%
  gather(component, coef,-bin_frame, -subject, -expression, -drug.placebo,-filename,-posed_spoken)%>%
  subset(expression!= "neutral")%>%
  
      group_by(filename,component,subject,expression,posed_spoken)%>%
  mutate(coef_max = max(coef),
         coef = coef/coef_max) %>%
  
  group_by(expression, component, bin_frame,subject,posed_spoken)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(Dataset, coef , color = Dataset, fill = Dataset))+
  ggplot(aes(bin_frame, coef, color = component))+
  geom_smooth()+
  # geom_smooth(aes(group = subject), se = F)+
  # stat_summary(aes(group = subject, color = component), geom = "smooth")+
  facet_grid(posed_spoken~expression )+
  theme_classic()+
   xlab("time bin")+
  p$graphstyle_int+
   scale_color_viridis_d(option = "magma")

posed_spoken_bindrows<- bind_rows(posed_NMF, spoken_NMF)%>%
  group_by(filename,posed_spoken, expression, drug.placebo,subject)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

write_csv(posed_spoken_bindrows, "posed_spoken_bindrows.csv")
```

plots

```{r}
df_OF_output_AUsW_unblind_spoken1_binned$drug.placebo


# drug vs placebo by expression
 df_OF_output_AUsW_unblind_spoken1_binned[,c(1,2:3,9:10,34:36)]%>%
  gather(component, coef,-bin_frame, -subject, -expression, -drug.placebo,-filename)%>%
  
      group_by(filename,component,subject,expression)%>%
  mutate(coef_max = max(coef),
         coef = coef/coef_max) %>%
  
  group_by(expression, component, bin_frame,subject,drug.placebo)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(Dataset, coef , color = Dataset, fill = Dataset))+
  ggplot(aes(bin_frame, coef, color = drug.placebo))+
  geom_smooth()+
  # geom_smooth(aes(group = subject), se = F)+
  # stat_summary(aes(group = subject, color = component), geom = "smooth")+
  facet_grid(expression~component  )+
  theme_classic()+
   xlab("time bin")+
  p$graphstyle_int+
   scale_color_viridis_d(option = "magma")
 
 
 # average effect of drug
 
 df_OF_output_AUsW_unblind_spoken1_binned[,c(1,2:3,9:10,34:36)]%>%
  gather(component, coef,-bin_frame, -subject, -expression, -drug.placebo,-filename)%>%
  
      group_by(filename,component,subject,expression)%>%
  mutate(coef_max = max(coef),
         coef = coef/coef_max
         ) %>%
  
  group_by( component, bin_frame,subject,drug.placebo)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(Dataset, coef , color = Dataset, fill = Dataset))+
  ggplot(aes(bin_frame, coef, color = drug.placebo))+
  geom_smooth()+
  # geom_smooth(aes(group = subject), se = F)+
  # stat_summary(aes(group = subject, color = component), geom = "smooth")+
  facet_grid(~component  )+
  theme_classic()+
   xlab("time bin")+
  p$graphstyle_int+
   scale_color_viridis_d(option = "magma")
 
 

```


heatmap - confusion maps


```{r}

 df_OF_output_AUsW_unblind_spoken1_binned[,c(1,2:3,9:10,34:36)]%>%
  gather(component, coef,-bin_frame, -subject, -expression, -drug.placebo,-filename)%>%
        group_by(filename,component,subject,expression)%>%
  mutate(coef_max = max(coef),
         coef = coef/coef_max
         ) %>%
  group_by(expression, component, drug.placebo)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(expression, component, fill = coef))+
    geom_tile()+
  facet_grid(~drug.placebo)+
  theme_classic()+
    scale_fill_viridis_c(option="magma")

```


export for classification


```{r}


# agg

colnames(df_OF_output_AUsW_unblind_spoken1_binned)
df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts <- df_OF_output_AUsW_unblind_spoken1_binned%>%
  ungroup()%>%
  select(c(3,9:10,17:36))%>%
  # gather( component, coef, -timebin,-Emotion, -Dataset, -morph, -filename)%>%
  group_by(subject,drug.placebo, expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)



write_csv(df_OF_output_AUsW_unblind_spoken1_binned, 
          "df_OF_output_AUsW_unblind_spoken1_binned.csv")


df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$test_ind<- if_else(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$drug.placebo == "drug", 1, 0)


write_csv(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts, 
          "df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts.csv")
nmfk4_agg_no_ts


```


should we do some filtering and smoothing before NMF

```{r}
colnames(df_OF_output_AUsW_unblind_spoken1_binned)

ma_zoo<- function(x, na.rm = TRUE) {
    return(zoo::rollmean(x,k = 5, fill = NA)) }

options(scipen = 999)


ADD_.1<- function(x, na.rm = TRUE) {
    return(x+.01) }


df_OF_output_AUsW_unblind_spoken1_binned_NOZERO<- df_OF_output_AUsW_unblind_spoken1_binned%>%
    ungroup()%>%
  group_by(filename)%>%
  mutate_at(17:33, ADD_.1)
  



df_OF_output_AUsW_unblind_spoken1_binned_ma<- df_OF_output_AUsW_unblind_spoken1_binned_NOZERO %>%
  ungroup()%>%
  group_by(filename)%>%
  mutate_at(17:33, ma_zoo)


df_OF_output_AUsW_unblind_spoken1_binned_ma<-df_OF_output_AUsW_unblind_spoken1_binned_ma%>%
    group_by(filename)%>%
fill(17:33, .direction = "up")%>%
  fill(17:33, .direction = "down")

  

```


moving average before NMF


```{r}

df_OF_output_AUsW_unblind_spoken1_binned_ma

colnames(df_OF_output_AUsW_unblind_spoken1_binned_ma[,17:33])

table(is.na( df_OF_output_AUsW_unblind_spoken1_binned_ma[,17:33]))

res_k3_spoken1_ma <- NMF::nmf(df_OF_output_AUsW_unblind_spoken1_binned_ma[,17:33], r = 3, 
                  nrun = 200, #number of runs to try and update for
                  seed=123456, #specific seed for reproducibility
                 .options = list( 'v')) #ver

# ife


as.data.frame(res_k3_spoken1_ma@fit@H)%>%
  mutate(component = 1:n())%>%
  gather(AU, coef, -component)%>%
  group_by(component)%>%
  mutate(max_comp = max(coef),
         coef = coef/max_comp,
         # AU = substring(AU,8,40),
         AU_code = substring(AU,4,5)
         )%>%
  arrange(AU_code)%>%
  ggplot(aes(component,AU, fill = coef))+
  geom_tile()+
  theme_classic()+
  # scale_fill_viridis_()
  scale_fill_viridis_c(option = "inferno")+
  xlab("K")+
  p$graphstyle_int+
guides(fill=guide_colorbar(ticks.colour = NA))
```
```{r}
df_OF_output_AUsW_unblind_spoken1_binned_ma$NMFtable_k3<- as.data.frame(res_k3_spoken1_ma@fit@W)$V1

# store components
df_OF_output_AUsW_unblind_spoken1_binned_ma$k3_comp1 = as.data.frame(res_k3_spoken1_ma@fit@W)$V1
df_OF_output_AUsW_unblind_spoken1_binned_ma$k3_comp2 = as.data.frame(res_k3_spoken1_ma@fit@W)$V2
df_OF_output_AUsW_unblind_spoken1_binned_ma$k3_comp3 = as.data.frame(res_k3_spoken1_ma@fit@W)$V3



# visualisation based on time


# chool_talk$ts_smooth<- 

colnames(df_OF_output_AUsW_unblind_spoken1_binned_ma)
  
  df_OF_output_AUsW_unblind_spoken1_binned_ma[,c(1,2:3,9:10,34:36)]%>%
  gather(component, coef,-bin_frame, -subject, -expression, -drug.placebo,-filename)%>%
  
      group_by(filename,component,subject,expression)%>%
  mutate(coef_max = max(coef),
         coef = coef/coef_max) %>%
  
  group_by(expression, component, bin_frame,subject)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(Dataset, coef , color = Dataset, fill = Dataset))+
  ggplot(aes(bin_frame, coef, color = component))+
  geom_smooth()+
  # geom_smooth(aes(group = subject), se = F)+
  # stat_summary(aes(group = subject, color = component), geom = "smooth")+
  facet_grid(~expression )+
  theme_classic()+
   xlab("time bin")+
  p$graphstyle_int+
   scale_color_viridis_d(option = "magma")
  
  
  # ts by expression
   df_OF_output_AUsW_unblind_spoken1_binned_ma[,c(1,2:3,9:10,34:36)]%>%
  gather(component, coef,-bin_frame, -subject, -expression, -drug.placebo,-filename)%>%
  
      group_by(filename,component,subject,expression)%>%
  mutate(coef_max = max(coef),
         coef = coef/coef_max) %>%
  
  group_by(expression, component, bin_frame,subject)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(Dataset, coef , color = Dataset, fill = Dataset))+
  ggplot(aes(bin_frame, coef, color = expression))+
  geom_smooth()+
  # geom_smooth(aes(group = subject), se = F)+
  # stat_summary(aes(group = subject, color = component), geom = "smooth")+
  facet_grid(~component  )+
  theme_classic()+
   xlab("time bin")+
  p$graphstyle_int+
   scale_color_viridis_d(option = "magma")


```



```{r}


# drug vs placebo by expression
 df_OF_output_AUsW_unblind_spoken1_binned_ma[,c(1,2:3,9:10,34:36)]%>%
  gather(component, coef,-bin_frame, -subject, -expression, -drug.placebo,-filename)%>%
  
      group_by(filename,component,subject,expression)%>%
  mutate(coef_max = max(coef),
         coef = coef/coef_max) %>%
  
  group_by(expression, component, bin_frame,subject,drug.placebo)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(Dataset, coef , color = Dataset, fill = Dataset))+
  ggplot(aes(bin_frame, coef, color = drug.placebo))+
  geom_smooth()+
  # geom_smooth(aes(group = subject), se = F)+
  # stat_summary(aes(group = subject, color = component), geom = "smooth")+
  facet_grid(expression~component  )+
  theme_classic()+
   xlab("time bin")+
  p$graphstyle_int+
   scale_color_viridis_d(option = "magma")
 
 
 # average effect of drug
 
df_OF_output_AUsW_unblind_spoken1_binned_ma[,c(1,2:3,9:10,34:36)]%>%
  gather(component, coef,-bin_frame, -subject, -expression, -drug.placebo,-filename)%>%
  
      group_by(filename,component,subject,expression)%>%
  mutate(coef_max = max(coef),
         coef = coef/coef_max
         ) %>%
  
  group_by( component, bin_frame,subject,drug.placebo)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(Dataset, coef , color = Dataset, fill = Dataset))+
  ggplot(aes(bin_frame, coef, color = drug.placebo))+
  geom_smooth()+
  # geom_smooth(aes(group = subject), se = F)+
  # stat_summary(aes(group = subject, color = component), geom = "smooth")+
  facet_grid(~component  )+
  theme_classic()+
   xlab("time bin")+
  p$graphstyle_int+
   scale_color_viridis_d(option = "magma")
 
```



JASP findings
- emotion classification is good
- but drug is not good not even within emotion


State-space for spoken stim
```{r}


df_OF_output_AUsW_unblind_spoken1_binned_ma

df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq_sum

# manual clustering

# compute speeds and displacement
unique(df_OF_output_AUsW_unblind_spoken1_binned_ma$filename)
# 304

table(df_OF_output_AUsW_unblind_spoken1_binned_ma$filename)
df_OF_output_AUsW_unblind_spoken1_binned_ma1<- 
  
  df_OF_output_AUsW_unblind_spoken1_binned_ma[,1:36]%>%
  ungroup()%>%
  group_by(filename)%>%
  ungroup()%>%
# speed calculations
  mutate(k3_comp1_speed = (abs(lag(k3_comp1) -k3_comp1))/abs((lead(bin_frame)-bin_frame)),
         k3_comp2_speed = (abs(lag(k3_comp2) -k3_comp2))/abs((lead(bin_frame)-bin_frame)),
         k3_comp3_speed = (abs(lag(k3_comp3) -k3_comp3))/abs((lead(bin_frame)-bin_frame)),
         
      # diff computations
         k3_comp1_diff = as.numeric(diff(zoo::zoo(k3_comp1), na.pad = TRUE)),
         k3_comp2_diff =as.numeric(diff(zoo::zoo(k3_comp2), na.pad = TRUE)),
         k3_comp3_diff =as.numeric(diff(zoo::zoo(k3_comp3), na.pad = TRUE)))%>%

  group_by(filename)%>%
  mutate(n_flename = n())%>%
       ungroup()%>%
  mutate(idno = rep(1:304, each = n_flename))
         
        #  # moving averages
        #  k3_comp1_diff_ma = as.numeric(zoo::rollmean(k3_comp1_diff, k = 5, fill = NA)),
        #  k3_comp2_diff_ma = as.numeric(zoo::rollmean(k3_comp2_diff, k = 5, fill = NA)),
        #  k3_comp3_diff_ma = as.numeric(zoo::rollmean(k3_comp3_diff, k = 5, fill = NA)),
        #    
        #   k3_comp1_speed_ma = as.numeric(zoo::rollmean(k3_comp1_speed, k = 5, fill = NA)),
        # k3_comp2_speed_ma = as.numeric(zoo::rollmean(k3_comp2_speed, k = 5, fill = NA)),
        #  k3_comp3_speed_ma = as.numeric(zoo::rollmean(k3_comp3_speed, k = 5, fill = NA)))%>%


df_OF_output_AUsW_unblind_spoken1_binned_ma1$filename

colnames(df_OF_output_AUsW_unblind_spoken1_binned_ma1)

# chool_talk$substate_illustration <-
df_OF_output_AUsW_unblind_spoken1_binned_ma1 %>%
  
  # compare kmean and manual clustering
  group_by(filename)%>%
   # group_by(idno)%>%
    mutate(sp_avg = (k3_comp1_speed+k3_comp2_speed+k3_comp3_speed)/3)%>%
   mutate(comp_delta_avg = (k3_comp1_diff +k3_comp2_diff+k3_comp3_diff)/3)%>%
   group_by(filename)%>%
  mutate(comp_delta_avg1 = scale(comp_delta_avg))%>%
  # mutate(df, IVMean = rowMeans(select(df, starts_with("IV")), na.rm = TRUE))
  mutate(manual_clust_sp_disp = 
           if_else(sp_avg > (mean(sp_avg, na.rm = TRUE)+ 
                               (1.5*(mad(sp_avg, na.rm = TRUE)))), 
                   # & 
                     # comp_delta_avg > (mean(abs(comp_delta_avg), na.rm = TRUE)+(.5*(mad(abs(comp_delta_avg), na.rm = TRUE)))), 
                   "transition state", "sustain state"))%>%
  group_by(filename, manual_clust_sp_disp)%>%
  
   ungroup()%>%
   subset(filename  == "./cut_spoken_angry_day1_p19.csv")%>%
      select(c(1,2,34:46))%>%
  # select(c(2,52:59, 46:47,38:41,64:66))%>%
  gather(component, coef,-bin_frame,-manual_clust_sp_disp,-filename) %>%
  mutate(var_type = if_else(grepl("diff", component ), "3. diff",
                        if_else(grepl("speed", component ), "2. speed",  
                                if_else(grepl("sp_avg", component ), "3. avg speed",  
                                        if_else(grepl("comp_delta_avg", component ), "5. avg diff",  
                            "1. NMF comp"))))) %>%

  
  # scale so we dob;t have massivelly different sizes acordss variables
   group_by(var_type)%>%
  mutate(coef_z = scale(coef))%>%
  group_by(component, bin_frame,var_type, manual_clust_sp_disp)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE) %>%
  ggplot(aes(bin_frame, coef_z, group = component))+

  geom_rect(aes(xmin = bin_frame, xmax = dplyr::lag(bin_frame), ymin = -Inf, ymax = Inf, fill = factor(manual_clust_sp_disp)), 
            alpha = .2)  +
    geom_line(aes(group = component, linetype = var_type), size = 1)+
  # geom_rect(aes(xmin=kmean_order-0.5, xmax=kmean_order+0.5))+ 
  # geom_smooth(se = F)+
  # facet_grid(expression~component)+
    # ggforce::facet_col(facets = vars(var_type), 
    #                  scales = "free_y", 
    #                  space = "free")+

  theme_classic()+
  facet_grid(var_type~.)+

  # scale_fill_viridis_d(option = "inferno")+
  theme_classic()+
  xlab("time bin")+
  ylab("coef")+
  p$graphstyle_int+
  theme(axis.text.y = element_blank(),
        legend.position = "none",
        strip.text = element_text(size = 5))+
    scale_fill_brewer(palette = "Dark2")

```

susbatate plots

```{r}
chool_talk$speed_disp_fucntionk1_spoken<-


  df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum%>%
  subset(!is.na(statespace))%>%
  ungroup()%>%
  mutate_if(is.numeric, maxnorm)%>%
  # subset(manual_clust_sp_disp == "transition state")%>%
  
  ggplot(aes(avg_disp_clust_k1,peak_sp_avg_clust_k1, color = expression))+
  geom_point(alpha = .5, size = 1.5)+
 
  # geom_smooth(aes(group = subject), se = F)+
  facet_grid(.~statespace)+
  # geom_smooth(method = "lm", formula = y~x,col="blue", se=FALSE)+
  # geom_smooth(method = "nls", formula = y~A*x^ B, se=FALSE,col="red", 
  #             method.args =list(start=c(A=0,B=0)))
  # 
  
     # geom_smooth(aes(group = expression), method = "glm", formula = y~x,
     #                  method.args = list(start=c(A=0,B=0)), size = .2)+
   geom_smooth(aes(group = expression), method = "glm", se = F, formula = y~log(x+.1),
                      method.args = list(
                                         start=c(A=0,B=0)))+
  
 # geom_smooth(aes(group = expression), method = "glm", formula = y~log(x),
 #                      method.args = list(start=c(A=0,B=0)), size = .2)+
  theme_classic()+
  ggpubr::stat_cor(p.accuracy = .001)+
  ylab("peak speed k1 - au")+
   xlab("displacement k1 - au")+
  scale_color_brewer(palette = "Dark2")+
    scale_x_continuous(breaks = c(0,.5,1), limits = c(0,1))+
  # scale_colour_viridis_d()+
  # ggpubr::stat_conf_ellipse()+
  p$graphstyle_int+
    theme(panel.spacing = unit(1, "cm"))



chool_talk$speed_disp_fucntionk2 

df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum$statespace<- df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum$manual_clust_sp_disp

chool_talk$speed_disp_fucntionk2_spoken<- 
df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum%>%
  subset(!is.na(statespace))%>%
  ungroup()%>%
  mutate_if(is.numeric, maxnorm)%>%
  # subset(manual_clust_sp_disp == "transition state")%>%
  
  ggplot(aes(avg_disp_clust_k2,peak_sp_avg_clust_k2, color = expression))+
  geom_point(alpha = .5, size = 1.5)+
 
  # geom_smooth(aes(group = subject), se = F)+
  facet_grid(.~statespace)+
  # geom_smooth(method = "lm", formula = y~x,col="blue", se=FALSE)+
  # geom_smooth(method = "nls", formula = y~A*x^ B, se=FALSE,col="red", 
  #             method.args =list(start=c(A=0,B=0)))
  # 
  
     # geom_smooth(aes(group = expression), method = "glm", formula = y~x,
     #                  method.args = list(start=c(A=0,B=0)), size = .2)+
   geom_smooth(aes(group = expression), method = "glm", se = F,formula = y~log(x+.1),
                      method.args = list(
                                         start=c(A=0,B=0)))+
  
 # geom_smooth(aes(group = expression), method = "glm", formula = y~log(x),
 #                      method.args = list(start=c(A=0,B=0)), size = .2)+
  theme_classic()+
  ggpubr::stat_cor(p.accuracy = .001)+
  ylab("peak speed k2 - au")+
   xlab("displacement k2 - au")+
  scale_color_brewer(palette = "Dark2")+
    scale_x_continuous(breaks = c(0,.5,1), limits = c(0,1))+
  # scale_colour_viridis_d()+
  # ggpubr::stat_conf_ellipse()+
  p$graphstyle_int+
    theme(panel.spacing = unit(1, "cm"))


chool_talk$speed_disp_fucntionk3_spoken <- df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum%>%
    subset(!is.na(statespace))%>%
ungroup()%>%
  mutate_if(is.numeric, maxnorm)%>%
  # subset(manual_clust_sp_disp == "transition state")%>%
  
  ggplot(aes(avg_disp_clust_k3,peak_sp_avg_clust_k3, color = expression))+
  geom_point(alpha = .5, size = 1.5)+
 
  # geom_smooth(aes(group = subject), se = F)+
  facet_grid(.~statespace)+
  # geom_smooth(method = "lm", formula = y~x,col="blue", se=FALSE)+
  # geom_smooth(method = "nls", formula = y~A*x^ B, se=FALSE,col="red", 
  #             method.args =list(start=c(A=0,B=0)))
  # 
  
     # geom_smooth(aes(group = expression), method = "glm", formula = y~x,
     #                  method.args = list(start=c(A=0,B=0)), size = .2)+
   geom_smooth(aes(group = expression), method = "glm",se = F, formula = y~log(x+.1),
                      method.args = list(
                                         start=c(A=0,B=0)))+
  
 # geom_smooth(aes(group = expression), method = "glm", formula = y~log(x),
 #                      method.args = list(start=c(A=0,B=0)), size = .2)+
  theme_classic()+
  ggpubr::stat_cor(p.accuracy = .001)+
  ylab("peak speed k3 - au")+
   xlab("displacement k3 - au")+
  scale_color_brewer(palette = "Dark2")+
  # scale_colour_viridis_d()+
  # ggpubr::stat_conf_ellipse()+
    scale_x_continuous(breaks = c(0,.5,1), limits = c(0,1))+
  p$graphstyle_int+
    theme(panel.spacing = unit(1, "cm"))

chool_talk$speed_disp_fucntionk1_spoken
chool_talk$speed_disp_fucntionk2_spoken
chool_talk$speed_disp_fucntionk3_spoken

library(patchwork)
chool_talk$speed_displace_fucn_patch_spoken<- (chool_talk$speed_disp_fucntionk1_spoken +chool_talk$speed_disp_fucntionk2_spoken+chool_talk$speed_disp_fucntionk3_spoken)+
   plot_layout(guides = "collect") & theme(legend.position = "top")


chool_talk$speed_displace_fucn_patch+  scale_x_continuous(breaks = c(0,.5,1), limits = c(0,1))
ggsave("speed_displace_fucn_patch2_spoken.tiff", chool_talk$speed_displace_fucn_patch_spoken,
       device = "tiff",
       width = 18, height = 5, dpi = 100)


```





```{r}
df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust<-
df_OF_output_AUsW_unblind_spoken1_binned_ma1 %>%
  
  # compare kmean and manual clustering
  group_by(filename)%>%
   # group_by(idno)%>%
    mutate(sp_avg = (k3_comp1_speed+k3_comp2_speed+k3_comp3_speed)/3)%>%
   mutate(comp_delta_avg = (k3_comp1_diff +k3_comp2_diff+k3_comp3_diff)/3)%>%
   group_by(filename)%>%
  mutate(comp_delta_avg1 = scale(comp_delta_avg))%>%
  # mutate(df, IVMean = rowMeans(select(df, starts_with("IV")), na.rm = TRUE))
  mutate(manual_clust_sp_disp = 
           if_else(sp_avg > (mean(sp_avg, na.rm = TRUE)+ 
                               (1.5*(mad(sp_avg, na.rm = TRUE)))), 
                   # & 
                     # comp_delta_avg > (mean(abs(comp_delta_avg), na.rm = TRUE)+(.5*(mad(abs(comp_delta_avg), na.rm = TRUE)))), 
                   "transition state", "sustain state"))

df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust<-
 df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust%>%
  ungroup()%>%
  group_by(filename, expression, subject)%>%
    # mutate(new = cumsum(manual_clust_sp_disp)) %>%
  mutate(clust_frame_no = rleid(manual_clust_sp_disp))


df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum<- df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust  %>%

group_by(filename,manual_clust_sp_disp)%>%
  mutate(clust_frame_no_bin = n(),
         # speed
         sp_avg_clust_k1 = mean(k3_comp1_speed , na.rm = TRUE),
         sp_avg_clust_k2 = mean(k3_comp2_speed , na.rm = TRUE),
         sp_avg_clust_k3 = mean(k3_comp3_speed , na.rm = TRUE),
         
          avg_disp_clust_k1 = sum(abs(k3_comp1_diff ), na.rm = TRUE),
          avg_disp_clust_k2 = sum(abs(k3_comp2_diff ), na.rm = TRUE),
          avg_disp_clust_k3 = sum(abs(k3_comp3_diff ), na.rm = TRUE),
         # sp_avg_clust_k2 = mean(k3_comp2_speed , na.rm = TRUE),
         # sp_avg_clust_k3 = mean(k3_comp3_speed , na.rm = TRUE),
         
         
        peak_sp_avg_clust_k1 = max(k3_comp1_speed , na.rm = TRUE),
          peak_sp_avg_clust_k2 = max(k3_comp2_speed , na.rm = TRUE),
          peak_sp_avg_clust_k3 = max(k3_comp3_speed , na.rm = TRUE),
         
         RMS_sd_clust_k1 = sqrt(mean(((lead(k3_comp1_speed ) - k3_comp1_speed )^2),na.rm = TRUE)),
        RMS_sd_clust_k2 = sqrt(mean(((lead(k3_comp2_speed ) - k3_comp2_speed )^2),na.rm = TRUE)),
        RMS_sd_clust_k3 = sqrt(mean(((lead(k3_comp3_speed ) - k3_comp3_speed )^2),na.rm = TRUE)))%>%
         
          # 
          # 
          # sp_sd_clust = sd(sp_avg, na.rm = TRUE),
          # RMS_sd_clust = sqrt(mean(((lead(sp_avg) - sp_avg)^2),na.rm = TRUE)),
          # RMS_diff_clust = sqrt(mean((comp_delta_avg^2),na.rm = TRUE)))   %>%
         # )%>%
group_by(filename, manual_clust_sp_disp, expression, subject, drug.placebo)%>%
  summarise_if(is.numeric, mean, na.rm  =TRUE)




#  - don't plot
colnames(df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq)

df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum%>%
  # subset(manual_clust_sp_disp == "stable state")%>%
  
  ggplot(aes(avg_disp_clust_k1,peak_sp_avg_clust_k1, color = expression))+
  geom_point(alpha = .5)+
 
  # geom_smooth(aes(group = subject), se = F)+
  facet_grid(.~manual_clust_sp_disp)+
  # geom_smooth(method = "lm", formula = y~x,col="blue", se=FALSE)+
  # geom_smooth(method = "nls", formula = y~A*x^ B, se=FALSE,col="red", 
  #             method.args =list(start=c(A=0,B=0)))
  # 
  
     # geom_smooth(aes(group = expression), method = "glm", formula = y~x,
     #                  method.args = list(start=c(A=0,B=0)), size = .2)+
   # geom_smooth(aes(group = expression), method = "glm", formula = y~x,
   #                    method.args = list(family = gaussian(link = 'log2'),
   #                                       start=c(A=0,B=0)), size = .2)+
  
 geom_smooth(aes(group = expression), method = "glm", formula = y~log(x+.1),
                      method.args = list(start=c(A=0,B=0)), size = .2)+
  theme_classic()+
  ggpubr::stat_cor()+
  scale_color_brewer(palette = "Dark2")+
  # scale_color_viridis_d(option = "inferno")+
  p$graphstyle_int



df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum%>%
  ungroup()%>%
  mutate_if(is.numeric, maxnorm)%>%
  subset(!is.na(manual_clust_sp_disp))%>%
  # subset(manual_clust_sp_disp == "transition state")%>%
  
  ggplot(aes(avg_disp_clust_k1,peak_sp_avg_clust_k1, color = expression))+
  geom_point(alpha = .5, size = 1.5)+
 
  # geom_smooth(aes(group = subject), se = F)+
  facet_grid(.~manual_clust_sp_disp)+
  # geom_smooth(method = "lm", formula = y~x,col="blue", se=FALSE)+
  # geom_smooth(method = "nls", formula = y~A*x^ B, se=FALSE,col="red", 
  #             method.args =list(start=c(A=0,B=0)))
  # 
  
     # geom_smooth(aes(group = expression), method = "glm", formula = y~x,
     #                  method.args = list(start=c(A=0,B=0)), size = .2)+
   geom_smooth(aes(group = expression), method = "glm",se = F, formula = y~log(x+.1),
                      method.args = list(
                                         start=c(A=0,B=0)))+
  
 # geom_smooth(aes(group = expression), method = "glm", formula = y~log(x),
 #                      method.args = list(start=c(A=0,B=0)), size = .2)+
  theme_classic()+
  ggpubr::stat_cor(p.accuracy = .001)+
  ylab("peak speed k1 - au")+
   xlab("displacement k1 - au")+
  scale_color_brewer(palette = "Dark2")+
    scale_x_continuous(breaks = c(0,.5,1), limits = c(0,1))+
  # scale_colour_viridis_d()+
  # ggpubr::stat_conf_ellipse()+
  p$graphstyle_int+
    theme(panel.spacing = unit(1, "cm"))




df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum_max_norm<- df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum%>%
  ungroup()%>%
  mutate_if(is.numeric, maxnorm)%>%
  subset(!is.na(manual_clust_sp_disp))

write_csv(df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum_max_norm,
          "df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum_max_norm_statespace.csv")
df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum_max_norm


write_csv(df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum,
          "df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_statespace.csv")


df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum

df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum_max_norm



df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq$sp_avg

df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum$sp_avg

df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum$peak_sp_avg_clust_k1
df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum$peak_sp_avg_clust_k2
df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum$peak_sp_avg_clust_k3


# posed
df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq$peak_sp_avg_clust_k1
df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq$peak_sp_avg_clust_k2
df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq$peak_sp_avg_clust_k3

df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq$avg_disp_clust_k1
df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq$avg_disp_clust_k2
df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq$avg_disp_clust_k3

posed_substate<-df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq
# flip to match the NMF flip
posed_substate$avg_disp_clust_k2<- df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq$avg_disp_clust_k3
posed_substate$avg_disp_clust_k3<- df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq$avg_disp_clust_k2


posed_substate$peak_sp_avg_clust_k2<- df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq$peak_sp_avg_clust_k3
posed_substate$peak_sp_avg_clust_k3<- df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq$peak_sp_avg_clust_k2


colnames(df_OF_output_AUsW_unblind_posed_binned3_nona_clust_agg4.1_main_seq)
spoken_substate<- df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum

colnames(spoken_substate)
spoken_substate_1<- spoken_substate%>%
  select(cnames_substate_select)

[,c(1,3:5,54:56,60:65,70)]

cnames_substate_select<- colnames(spoken_substate_1)
posed_substate_1<- posed_substate %>%
  select(cnames_substate_select)

posed_substate_1$posed_spoken<- "posed"

spoken_substate_1$posed_spoken<- "spoken"

spoken_substate_1$manual_clust_sp_disp<- NULL


posed_substate_1$statespace
spoken_substate_1$statespace<-sub(" .*", "", spoken_substate_1$statespace)

bind_rows(posed_substate_1, spoken_substate_1)%>%

  # df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum%>%
  subset(!is.na(statespace))%>%
  subset(expression!= "neutral")%>%
  # subset(statespace != "sustain")%>%
  ungroup()%>%
  group_by(posed_spoken)%>%
  mutate_if(is.numeric, maxnorm)%>%
  # subset(manual_clust_sp_disp == "transition state")%>%
  
  ggplot(aes(avg_disp_clust_k1,peak_sp_avg_clust_k1, color = posed_spoken))+
  geom_point(alpha = .5, size = 1.5)+
 
  # geom_smooth(aes(group = subject), se = F)+
  facet_grid(expression~statespace)+
  # geom_smooth(method = "lm", formula = y~x,col="blue", se=FALSE)+
  # geom_smooth(method = "nls", formula = y~A*x^ B, se=FALSE,col="red", 
  #             method.args =list(start=c(A=0,B=0)))
  # 
  
     # geom_smooth(aes(group = expression), method = "glm", formula = y~x,
     #                  method.args = list(start=c(A=0,B=0)), size = .2)+
   geom_smooth(method = "glm", se = T, formula = y~log(x+.1),
                      method.args = list(
                                         start=c(A=0,B=0)))+
  
 # geom_smooth(aes(group = expression), method = "glm", formula = y~log(x),
 #                      method.args = list(start=c(A=0,B=0)), size = .2)+
  theme_classic()+
  ggpubr::stat_cor(p.accuracy = .001)+
  ylab("peak speed k1 - au")+
   xlab("displacement k1 - au")+
  scale_color_brewer(palette = "Dark2")+
    scale_x_continuous(breaks = c(0,.5,1), limits = c(0,1))+
  # scale_colour_viridis_d()+
  # ggpubr::stat_conf_ellipse()+
  p$graphstyle_int+
    theme(panel.spacing = unit(1, "cm"))


# k2

bind_rows(posed_substate_1, spoken_substate_1)%>%

  # df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum%>%
  subset(!is.na(statespace))%>%
  subset(expression!= "neutral")%>%
  # subset(statespace != "sustain")%>%
  ungroup()%>%
  group_by(posed_spoken)%>%
  mutate_if(is.numeric, maxnorm)%>%
  # subset(manual_clust_sp_disp == "transition state")%>%
  
  ggplot(aes(avg_disp_clust_k2,peak_sp_avg_clust_k2, color = posed_spoken))+
  geom_point(alpha = .5, size = 1.5)+
 
  # geom_smooth(aes(group = subject), se = F)+
  facet_grid(expression~statespace)+
  # geom_smooth(method = "lm", formula = y~x,col="blue", se=FALSE)+
  # geom_smooth(method = "nls", formula = y~A*x^ B, se=FALSE,col="red", 
  #             method.args =list(start=c(A=0,B=0)))
  # 
  
     # geom_smooth(aes(group = expression), method = "glm", formula = y~x,
     #                  method.args = list(start=c(A=0,B=0)), size = .2)+
   geom_smooth(method = "glm", se = T, formula = y~log(x+.1),
                      method.args = list(
                                         start=c(A=0,B=0)))+
  
 # geom_smooth(aes(group = expression), method = "glm", formula = y~log(x),
 #                      method.args = list(start=c(A=0,B=0)), size = .2)+
  theme_classic()+
  ggpubr::stat_cor(p.accuracy = .001)+
  ylab("peak speed k3 - au")+
   xlab("displacement k3 - au")+
  scale_color_brewer(palette = "Dark2")+
    scale_x_continuous(breaks = c(0,.5,1), limits = c(0,1))+
  # scale_colour_viridis_d()+
  # ggpubr::stat_conf_ellipse()+
  p$graphstyle_int+
    theme(panel.spacing = unit(1, "cm"))

# k3

bind_rows(posed_substate_1, spoken_substate_1)%>%

  # df_OF_output_AUsW_unblind_spoken1_binned_ma1_nona_clust_agg_main_seq_sum%>%
  subset(!is.na(statespace))%>%
  subset(expression!= "neutral")%>%
  # subset(statespace != "sustain")%>%
  ungroup()%>%
  group_by(posed_spoken)%>%
  mutate_if(is.numeric, maxnorm)%>%
  # subset(manual_clust_sp_disp == "transition state")%>%
  
  ggplot(aes(avg_disp_clust_k2,peak_sp_avg_clust_k2, color = posed_spoken))+
  geom_point(alpha = .5, size = 1.5)+
 
  # geom_smooth(aes(group = subject), se = F)+
  facet_grid(expression~statespace)+
  # geom_smooth(method = "lm", formula = y~x,col="blue", se=FALSE)+
  # geom_smooth(method = "nls", formula = y~A*x^ B, se=FALSE,col="red", 
  #             method.args =list(start=c(A=0,B=0)))
  # 
  
     # geom_smooth(aes(group = expression), method = "glm", formula = y~x,
     #                  method.args = list(start=c(A=0,B=0)), size = .2)+
   geom_smooth(method = "glm", se = T, formula = y~log(x+.1),
                      method.args = list(
                                         start=c(A=0,B=0)))+
  
 # geom_smooth(aes(group = expression), method = "glm", formula = y~log(x),
 #                      method.args = list(start=c(A=0,B=0)), size = .2)+
  theme_classic()+
  ggpubr::stat_cor(p.accuracy = .001)+
  ylab("peak speed k3 - au")+
   xlab("displacement k3 - au")+
  scale_color_brewer(palette = "Dark2")+
    scale_x_continuous(breaks = c(0,.5,1), limits = c(0,1))+
  # scale_colour_viridis_d()+
  # ggpubr::stat_conf_ellipse()+
  p$graphstyle_int+
    theme(panel.spacing = unit(1, "cm"))




```


```{r}

  
bind_rows(posed_substate_1, spoken_substate_1)%>%
  subset(expression!= "neutral")%>%
    subset(!is.na(statespace))%>%
  ggplot(aes(expression, clust_frame_no_bin, color = posed_spoken))+
  geom_jitter(alpha = .1, width = .1)+
  stat_summary(geom = "pointrange")+
  facet_grid(~statespace)+
  theme_classic()


bind_rows(posed_substate_1, spoken_substate_1)%>%
  subset(expression!= "neutral")%>%
    subset(!is.na(statespace))%>%
  ggplot(aes(expression, sp_avg, color = posed_spoken))+
  geom_jitter(alpha = .1, width = .1)+
  stat_summary(geom = "pointrange")+
  facet_grid(~statespace)+
  theme_classic()


bind_rows(posed_substate_1, spoken_substate_1$)%>%
  subset(expression!= "neutral")%>%
    subset(!is.na(statespace))%>%
  ggplot(aes(expression, abs(comp_delta_avg), color = posed_spoken))+
  geom_jitter(alpha = .1, width = .1)+
  stat_summary(geom = "pointrange")+
  facet_grid(~statespace)+
  theme_classic()

```