---
title: "halo_facestudy_spoken_analysis"
author: "Helio"
date: '2022-08-30'
output: html_document
---



dependencies: preprocss_halofaces.Rmd
df_OF_output_AUsW_unblind_posed_binned

related script:analysys_halofacestudy.Rmd
related data: df_OF_output_AUsW_unblind_posed



for the actual analyses we want
1- learn spatiotemporal structure suing NMF
2 - does drug vs no drug differ in NMF metrics?
3- can we separate groups based on NMF components using BADIA

spatiotemporal dynamics
- movement substates (initiation, sustainment, etc)
- if we use kmean clustering, do we have differences into how many substaes are there
- or if we use a fixed number of substates, are there significant temporal differences (e.g. duration, recurrence)

preferences
```{r}
library(tidyverse)
library(data.table)

library(NMF)

```

for the NMF we will start with k = 3 given our findings in the posed (we have a good prior for 3). 
But then we will also do 1 to 4 to to compare.

fit nmf just spoken
```{r}

unique(df_OF_output_AUsW_unblind_spoken1_2_binned$posed.spoken)

df_OF_output_AUsW_unblind_spoken1_2$bin
df_OF_output_AUsW_unblind_spoken1_2_binned
# use only the "spoken" condition
df_OF_output_AUsW_unblind_spoken1_binned<- subset(df_OF_output_AUsW_unblind_spoken1_2_binned,
                                           posed.spoken == "spoken")



# fit
colnames(df_OF_output_AUsW_unblind_spoken1_binned)
unique(df_OF_output_AUsW_unblind_spoken1_binned$bin_frame)
# df_OF_output_AUsW_unblind_spoken1_binned

unique(df_OF_output_AUsW_unblind_spoken1_binned$expression)
res_k3_spoken1 <- NMF::nmf(df_OF_output_AUsW_unblind_spoken1_binned[,17:33], r = 3, 
                  nrun = 200, #number of runs to try and update for
                  seed=123456, #specific seed for reproducibility
                 .options = list( 'v')) #verbose

range(df_OF_output_AUsW_unblind_spoken1_binned$bin_frame)



res_spoken1_findk <- nmf(df_OF_output_AUsW_unblind_spoken1_binned[,17:33], 2:6, 
                      seed=123456,
                      nrun = 100,
                       .options = 'v')


# plot(res_k3_spoken1) - this only work for multyiple fits with multiple ks
# summary(res_k3_spoken1) #dont run

# basis components 
NMF::basismap(res_k3_spoken1) # weights/ amplitudes
# memory exhaust - takes a lot of time

# mixture coefficients 
NMF::coefmap(res_k3_spoken1) #hidden variables

# access more info
# res_k3_em

NMF::consensusmap(res_k3_spoken1)

```
face heatmaps for Spoje NMF




some custom visualisations

custom visalisation of H (mixing components)
```{r}

paper_plots$spoken_NMF
paper_plots$spoken_NMF_hm
paper_plots$spoken_NMF_ts_hm
# paper_plots

```


   
#   # panespoken_NMF_ts_hm paper_plots$spoken_NMF_ts_hm
#   paper_plots$NMF_panel_spoken <-
# (paper_plots$spoken_NMF_hm |
#   (paper_plots$spoken_NMF/paper_plots$spoken_NMF_ts_hm))+
#   plot_layout(ncol = 2, widths = c(.7,2))+
#     plot_annotation(title = "SPOKEN EXPRESSIONS")
# 
#     paper_plots$NMF_panel_spoken
#     
    
ggsave("fig2_NMF_panel_spokjen.tiff", paper_plots$NMF_panel_spoken, device = "tiff",
       width = 14, height = 7, dpi = 800)

# 
# paper_plots$panel_fig2_posed_spoken_panel<- 
#   ((paper_plots$NMF_panel_posed+ggtitle("POSED EXPRESSIONS")) /(paper_plots$NMF_panel_spoken+ggtitle("SPOKEN EXPRESSIONS")))+
#   plot_annotation(tag_levels = 'A')
# 
# paper_plots$NMF_panel_posed +
#   ggtitle("posed")
#   
# ggsave("panel_fig2_posed_spoken_panel.tiff", paper_plots$panel_fig2_posed_spoken_pane, device = "tiff",
#        width = 20, height = 14, dpi = 800)

```



```{r}
# 
posed_spoken_bindrows <- bind_rows(posed_NMF, spoken_NMF)%>%
  group_by(filename,posed_spoken, expression, drug.placebo,subject)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

posed_spoken_bindrows_ts<- bind_rows(posed_NMF, spoken_NMF)%>%
  group_by(filename, bin_frame, posed_spoken, expression, drug.placebo,subject)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)


View(posed_spoken_bindrows_ts)

colnames(posed_spoken_bindrows)

write_csv(posed_spoken_bindrows, "posed_spoken_bindrows.csv")
write_csv(posed_spoken_bindrows, "posed_spoken_bindrows_ts.csv")

caret::createDataPartition(c(2:9),
                            2, p = .7, group = "filename")
posed_spoken_bindrows_ts

library(caTools)

# ?sample.split
posed_spoken_bindrows_ts$trainLogical<-sample.split(posed_spoken_bindrows_ts$k3_comp1, group = posed_spoken_bindrows_ts$filename, SplitRatio = 0.7)


posed_spoken_bindrows_ts$trainLogical_num<-as.numeric(posed_spoken_bindrows_ts$trainLogical)
table(posed_spoken_bindrows_ts$trainLogical)/length(posed_spoken_bindrows_ts$trainLogical)
table(posed_spoken_bindrows_ts$trainLogical_num)/length(posed_spoken_bindrows_ts$trainLogical_num)


write_csv(posed_spoken_bindrows_ts, "posed_spoken_bindrows_ts.csv")

unique(posed_spoken_bindrows_ts$posed_spoken)


```


MULTIVARIATE TIMESERIES CLUSTERING
```{r}
# Load the caret package
# library(caret)
library(CMFMTS)
# ?CMFMTS::cmfmts
# Data to process (data.frame). Each row contains a time series.

df_OF_output_AUsW_unblind_spoken1_binned

colnames(df_OF_output_AUsW_unblind_spoken1_binned)
unique(df_OF_output_AUsW_unblind_spoken1_binned$posed.spoken)


colnames(df_OF_output_AUsW_unblind_spoken1_binned[c(1:10,34:36)])
# gather
df_OF_output_AUsW_unblind_spoken1_binned_gather<- gather(df_OF_output_AUsW_unblind_spoken1_binned[c(1:10,34:36)], 
                                                         key = "nm_comp", value = "nmf_comp_value", - c(1:10))
df_OF_output_AUsW_unblind_spoken1_binned_gather

# create a timeseries unique?

df_OF_output_AUsW_unblind_spoken1_binned_gather$timersies_unique <- paste0(df_OF_output_AUsW_unblind_spoken1_binned_gather$filename,                             paste0(df_OF_output_AUsW_unblind_spoken1_binned_gather$nm_comp))

unique(df_OF_output_AUsW_unblind_spoken1_binned_gather$timersies_unique)


# train_gather_comp1 <- train_gather%>%subset(timersies_unique == "./cut_posed_angry_day1_p10.csvk3_comp1")
# i need to dcast time ids to rows, because this fucntion needs each row to be a timeseries

ts_order<- c(paste0("t_",(1:100)))


# now dcast such that each row is a timeseriies
spoken_dcast_formts_maxnorm<-

df_OF_output_AUsW_unblind_spoken1_binned_gather%>%
  arrange(filename,nm_comp,bin_frame)%>%
  group_by(filename,nm_comp)%>%
  mutate(nmf_comp_value = zoo::na.approx(nmf_comp_value))%>%
  
  # potentially made a mistake here in spoken, max should be by subject and component
   group_by(filename,nm_comp)%>%
  # don't use maxnorm
  mutate(nmf_comp_value = maxnormalize(nmf_comp_value))%>%
  mutate(bin_frame = paste0("t_", paste0(bin_frame)))%>%
  arrange(filename,nm_comp,bin_frame)%>%
 data.table::dcast(timersies_unique+filename+subject+expression+drug.placebo+subject+nm_comp~bin_frame, value.var = "nmf_comp_value")

# spoken_dcast_formts_maxnorm


df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts<- df_OF_output_AUsW_unblind_spoken1_binned%>%
  group_by(filename)%>%
  mutate(comp1_maxnorm = maxnormalize(k3_comp1),
         comp2_maxnorm = maxnormalize(k3_comp2),
         comp3_maxnorm = maxnormalize(k3_comp3)
         )%>%
  group_by(filename, expression, subject,drug.placebo)%>%
  summarise_if(is.numeric,mean,na.rm = T)

write_csv(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts,
          "df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts.csv")

range(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$comp1_maxnorm)
range(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$comp2_maxnorm)
range(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$comp3_maxnorm, na.rm = T)

colnames(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts)
```

colnames(spoken_dcast_formts_maxnorm)

```{r}
ts_order
# colnames(train_gather_dcast)


# this extracts features from each timeseries - 41 in this case 
# see Multivariate times series classification through an interpretable representation
# Author links open overlay panelFrancisco J.BaldánaJosé M.Beníteza
# https://www.sciencedirect.com/science/article/pii/S0020025521004825#b0180


# we could do somethign similar where we create the features ourselves
# e.g. displacement, speed, RMSSD, jerk, etc, this gives a smaller set of data compared to 
# max_min_norm()


# max norm
#   
# train_gather_dcast_maxnorm<- train_gather%>%
#   group_by(subject)%>%
#   mutate(nmf_comp_value = maxnorm(nmf_comp_value))
  

  # reorder timeseries columns
  colnames(spoken_dcast_formts_maxnorm1)
  spoken_dcast_formts_maxnorm<- bind_cols(spoken_dcast_formts_maxnorm[,1:7], spoken_dcast_formts_maxnorm[,c(ts_order)])
  
  spoken_dcast_formts_maxnorm1<-bind_cols(spoken_dcast_formts_maxnorm[,1:7],
zoo::na.approx(spoken_dcast_formts_maxnorm[,8:107]))

  
  
  spoken_dcast_formts_maxnorm1

colnames(spoken_dcast_formts_maxnorm1)
# multivariate timeseries feature extraction

?CMFMTS::cmfmts
spoken_mts <- CMFMTS::cmfmts(dataset = spoken_dcast_formts_maxnorm1[,8:107],
                na = TRUE)


 table(is.na(spoken_dcast_formts_maxnorm1))
 table(is.na(spoken_mts))

View(spoken_mts)
colnames(train_gather_dcast_maxnorm_dcast)

library(CMFMTS)

# store essential columns

spoken_mts$filename<- spoken_dcast_formts_maxnorm$filename
spoken_mts$subject<- spoken_dcast_formts_maxnorm$subject
spoken_mts$expression<- spoken_dcast_formts_maxnorm$expression
spoken_mts$drug.placebo<- spoken_dcast_formts_maxnorm$drug.placebo
spoken_mts$nm_comp<- spoken_dcast_formts_maxnorm$nm_comp
spoken_mts$nm_comp<- spoken_dcast_formts_maxnorm$nm_comp

# drop columns with zero SD

# Calculate the sd for the selected columns
# Identify the numerical columns
num_cols <- sapply(spoken_mts, is.numeric)

num_col_names <- names(spoken_mts[,num_cols])

sd_values <- apply(spoken_mts[, num_col_names], 2, sd, na.rm = T)


# Identify the columns with a standard deviation of zero
zero_sd_cols <- names(which(sd_values == 0))

# Drop the columns with a standard deviation of zero
spoken_mts_no0Sd <- spoken_mts%>%select(-zero_sd_cols)
View(spoken_mts_no0Sd)

spoken_mts_no0Sd_no0Sd <- spoken_mts%>%select(-zero_sd_cols)

# Replace NA values with the column average
spoken_mts_no0Sd_no0Sd<- spoken_mts_no0Sd_no0Sd %>%
  mutate_if(is.numeric,funs(ifelse(is.na(.), mean(., na.rm = TRUE), .)))


# dcast
colnames(spoken_mts_no0Sd_no0Sd)
library(data.table)
 

spoken_mts_no0Sd_no0Sd_dcast<-
setDT(spoken_mts_no0Sd_no0Sd)%>%
   gather(ts_features, values, -filename,- subject, -expression,-drug.placebo, -nm_comp)%>%
  mutate(ts_features_k =  paste0(ts_features, nm_comp))%>%
  # mutate(bin_frame = paste0("t_", paste0(bin_frame)))%>%
 data.table::dcast(filename + subject+expression+drug.placebo ~ ts_features_k, value.var = "values", sep = "")

write_csv(spoken_mts_no0Sd_no0Sd, "spoken_mts_no0Sd_no0Sd.csv")
write_csv(spoken_mts_no0Sd_no0Sd_dcast, "spoken_mts_no0Sd_no0Sd_dcast.csv")

```

principal components

```{r}
colnames(spoken_mts_no0Sd_no0Sd_dcast)
spoken_PCA_maxnormpsych <-psych::principal(spoken_mts_no0Sd_no0Sd_dcast[,c(5:118)],3, scores = TRUE)

spoken_PCA_maxnormpsych

# need to have a threshold


# library(readxl)

library(readxl)
spoken_PCA_remove <- read_excel("spoken_PCA_remove.xlsx")
spoken_PCA_remove$remove

# 
spoken_mts_no0Sd_no0Sd_dcast_2<- spoken_mts_no0Sd_no0Sd_dcast%>%
select(-c(spoken_PCA_remove$remove))

spoken_mts_no0Sd_no0Sd_dcast_2
spoken_mts_no0Sd_no0Sd_dcast$PC1<-   spoken_PCA_maxnormpsych$scores[,1]
spoken_mts_no0Sd_no0Sd_dcast$PC2<-   spoken_PCA_maxnormpsych$scores[,2]
spoken_mts_no0Sd_no0Sd_dcast$PC3<-   spoken_PCA_maxnormpsych$scores[,3]


# nw pca
colnames(spoken_mts_no0Sd_no0Sd_dcast_2)
spoken_PCA_maxnormpsych2 <-psych::principal(spoken_mts_no0Sd_no0Sd_dcast_2[,c(5:61)],3, scores = TRUE)


spoken_mts_no0Sd_no0Sd_dcast_2$PC1<-   spoken_PCA_maxnormpsych2$scores[,1]
spoken_mts_no0Sd_no0Sd_dcast_2$PC2<-   spoken_PCA_maxnormpsych2$scores[,2]
spoken_mts_no0Sd_no0Sd_dcast_2$PC3<-   spoken_PCA_maxnormpsych2$scores[,3]

spoken_PCA_maxnormpsych

write_csv(spoken_mts_no0Sd_no0Sd, "spoken_mts_no0Sd_no0Sd.csv")
write_csv(spoken_mts_no0Sd_no0Sd_dcast, "spoken_mts_no0Sd_no0Sd_dcast.csv")
write_csv(spoken_mts_no0Sd_no0Sd_dcast_2, "spoken_mts_no0Sd_no0Sd_dcast2.csv")

```

```

```{r}
colnames(spoken_mts_no0Sd_no0Sd_dcast_2)

mts_maxnorm_dcast_no0Sd_removed
colnames(mts_maxnorm_dcast_no0Sd_removed)
spoken_mts_no0Sd_no0Sd
mts_maxnorm_dcast_no0Sd_removed_SCALE2$filename

library(tidyverse)

spoken_mts_no0Sd_no0Sd_dcast_2%>%
  select(c(colnames(mts_maxnorm_dcast_no0Sd_removed)))

spoken_mts_no0Sd_no0Sd_dcast_2$PC1

mts_maxnorm_dcast_no0Sd_removed$PC1
mts_maxnorm_dcast_no0Sd_removed$posed_spoken <- "posed"
spoken_mts_no0Sd_no0Sd_dcast_2$posed_spoken <- "spoken"


bind_rows(mts_maxnorm_dcast_no0Sd_removed[, c(1:4,69:72)],
          spoken_mts_no0Sd_no0Sd_dcast_2[, c(1:4,63:66)])%>%
  gather(comp,comp_value, -filename, -subject, -expression,-drug.placebo,
         -posed_spoken)%>%
  ggplot(aes(expression, comp_value))+
  stat_summary(geom = "pointrange")+
    facet_grid(~comp)


dta_test_lmer<- bind_rows(mts_maxnorm_dcast_no0Sd_removed[, c(1:4,69:72)],
          spoken_mts_no0Sd_no0Sd_dcast_2[, c(1:4,63:66)])%>%
  gather(comp,comp_value, -filename, -subject, -expression,-drug.placebo,
         -posed_spoken)
colnames(dta_test_lmer)

dta_test_lmer$subject<- as.factor(dta_test_lmer)
lmer(comp_value ~ comp+expression+posed_spoken+
       comp:expresion+
       comp:posed_spoken+
       (1|subject) REML = FALSE,
     data = dta_test_lmer)

```


random forest analysys and plots

```{r}
library(caret)

# df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts
 trainIndex_spoken <- createDataPartition(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$expression, p = .8, 
                                  list = FALSE, 
                                  times = 1)
  
 trainIndex_spoken
  
 
 spoken_train_set <- df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts[ trainIndex_spoken,]
  spoken_test_set  <- df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts[-trainIndex_spoken,]
  
# train
  
   # spoken_r.forest_mts <- train(expression ~ comp1_maxnorm + comp2_maxnorm + comp3_maxnorm, 
   #              data = spoken_train_set, 
   #              method = "rf",
   #              trControl = trainControl(method = "oob"),
   #              ntree = 21)
   
   
spoken_r.forest <- train(expression ~ comp1_maxnorm + comp2_maxnorm + comp3_maxnorm, 
                data = spoken_train_set, 
                method = "rf",
                trControl = trainControl(method = "oob"),
                ntree = 21)
   
   
   # test
   # spoken_r.forest_mts$finalModel$mtry 
   
#    
# spoken_test_set$prediction <- predict(spoken_r.forest_mts, spoken_test_set)
#    
spoken_test_set$prediction <- predict(spoken_r.forest, spoken_test_set)
   

# 
spoken_test_set_res<- confusionMatrix(spoken_test_set$prediction , as.factor(spoken_test_set$expression), mode = "everything", positive="1")
   
   
options(scipen = 999)
spoken_test_set_res
```


Confusion Matrix and Statistics

          Reference
Prediction angry happy neutral sad
   angry      10     0       1   2
   happy       0    14       0   2
   neutral     0     1       9   4
   sad         5     0       5   7

Overall Statistics
                                          
               Accuracy : 0.6667          
                 95% CI : (0.5331, 0.7831)
    No Information Rate : 0.25            
    P-Value [Acc > NIR] : 0.0000000000131 
                                          
                  Kappa : 0.5556          
                                          
 Mcnemar's Test P-Value : NA              

Statistics by Class:

                     Class: angry Class: happy Class: neutral
Sensitivity                0.6667       0.9333         0.6000
Specificity                0.9333       0.9556         0.8889
Pos Pred Value             0.7692       0.8750         0.6429
Neg Pred Value             0.8936       0.9773         0.8696
Precision                  0.7692       0.8750         0.6429
Recall                     0.6667       0.9333         0.6000
F1                         0.7143       0.9032         0.6207
Prevalence                 0.2500       0.2500         0.2500
Detection Rate             0.1667       0.2333         0.1500
Detection Prevalence       0.2167       0.2667         0.2333
Balanced Accuracy          0.8000       0.9444         0.7444
                     Class: sad
Sensitivity              0.4667
Specificity              0.7778
Pos Pred Value           0.4118
Neg Pred Value           0.8140
Precision                0.4118
Recall                   0.4667
F1                       0.4375
Prevalence               0.2500
Detection Rate           0.1167
Detection Prevalence     0.2833
Balanced Accuracy        0.6222


overall bal;amced accuracy = (0.8000    +   0.9444       +  0.7444+ 0.6222)/4

0.77775
boundary plots

```{r}

spoken_rf <-randomForest::randomForest(as.factor(expression) ~ PC1 + PC2 + PC3,
                                       data = spoken_mts_no0Sd_no0Sd_dcast_2,
                   proximity = TRUE,
                   ntree = 73
                   # mtry = 2
                   )

  
  # spoken_rf_2 <- train(expression ~ PC1 + PC2 + PC3, 
  #               data = spoken_mts_no0Sd_no0Sd_dcast_2, 
  #               method = "rf",
  #               ntree = 73,
  #              proximity = TRUE)
  
    spoken_rf_nomts <- train(expression ~ comp1_maxnorm + comp2_maxnorm + 
                         comp3_maxnorm, 
                data = df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts, 
                method = "rf",
                ntree = 21,
               proximity = TRUE)
  
# 
# Now we just create a grid of all x, y values in the range of the data using expand.grid, and get the predicted species at each pair:


# breask
getPrettyAxisBreaks(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$comp1_maxnorm)
# min max
x_min_sp <- min(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$comp1_maxnorm + 0.5)
x_max_sp <- max(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$comp1_maxnorm + 0.5)

y_min_sp <- min(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$comp2_maxnorm + 0.5)
y_max_sp <- max(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$comp2_maxnorm + 0.5)

z_min_sp <- min(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$comp3_maxnorm + 0.5)
z_max_sp <- max(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$comp3_maxnorm + 0.5)

  # breaks
xBreaks_sp <- getPrettyAxisBreaks(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$comp1_maxnorm, min.n = 4)
  
yBreaks_sp <- getPrettyAxisBreaks(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$comp2_maxnorm, min.n = 4)

zBreaks_sp <- getPrettyAxisBreaks(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$comp3_maxnorm, min.n = 4)
  
  x_min_sp <- xBreaks_sp[1]
  x_max_sp <- xBreaks_sp[length(xBreaks_sp)]
  y_min_sp <- yBreaks_sp[1]
  y_max_sp <- yBreaks_sp[length(yBreaks_sp)]
  
   z_min_sp <- zBreaks_sp[1]
  z_max_sp <- zBreaks_sp[length(zBreaks_sp)]
  # Adjust the graining
  hs_sp <- min(c(diff(range(xBreaks_sp)), diff(range(yBreaks_sp)))) / 50
  hs_z_sp <- min(c(diff(range(yBreaks_sp)), diff(range(zBreaks_sp)))) / 50
  
  # grid_sp <- as.data.frame(expand.grid(seq(x_min_sp, x_max_sp, by = hs_sp), 
  #                                   seq(y_min_sp, y_max_sp, by = hs_sp),
  #                                   seq(z_min_sp, z_max_sp, by = hs_z_sp),
  #                                   ))
  

df_sp <- expand.grid(comp1_maxnorm = seq(x_min_sp, x_max_sp, 
                                            by = hs_sp
                            # length.out = 100
                            ),
                  comp2_maxnorm = seq(y_min_sp, y_max_sp,
                                              by = hs_sp
                           # length.out = 100 
                           ),
                  
                  comp3_maxnorm = seq(z_min_sp, z_max_sp ,
                                             by = hs_z_sp
                            # length.out = 100
                            )
                  )

df_sp



  
ggplot(df_sp, aes(PC1, PC2,fill = expression)) +

  geom_tile(aes(fill = expression),alpha = 0.01, size = 0) +
  # stat_contour(data = df,aes(x =PC1, y =PC2, z = expression))
   geom_point(data =spoken_mts_no0Sd_no0Sd_dcast_2,aes( colour =expression,fill = expression),size = 3) +
  geom_point(data = spoken_mts_no0Sd_no0Sd_dcast_2, shape = 21, size = 3) +
  # theme_minimal()
  # theme_void()+

  theme_bw() +
      plot_style+
  scale_color_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")+
    # scale_color_viridis_d()+
    # scale_fill_viridis_d()+
  # theme(panel.border = element_blank(),
  #      panel.grid.major = element_blank(),
  #      panel.grid.minor = element_blank())+
  base_breaks_x(df$PC1) +
  base_breaks_y(df$PC2)+
  ylab("comp2")+
  xlab("comp1")


```


use the mts


```{r}

# spoken_rf <-randomForest::randomForest(as.factor(expression) ~ PC1 + PC2 + PC3,
#                                        data = spoken_mts_no0Sd_no0Sd_dcast_2,
#                    proximity = TRUE,
#                    ntree = 73
#                    # mtry = 2
#                    )

# spoken_rf <-randomForest::randomForest(as.factor(expression) ~ PC1 + PC2 + PC3,
#                                        data = spoken_mts_no0Sd_no0Sd_dcast_2,
#                    proximity = TRUE,
#                    ntree = 73
#                    # mtry = 2
#                    )


  
  spoken_rf <- train(expression ~ PC1 + PC2 + PC3,
                data = spoken_mts_no0Sd_no0Sd_dcast_2,
                method = "rf",
                ntree = 73,
               proximity = TRUE)

# 
# Now we just create a grid of all x, y values in the range of the data using expand.grid, and get the predicted species at each pair:


# breask
getPrettyAxisBreaks(spoken_mts_no0Sd_no0Sd_dcast_2$PC1)
# min max
x_min_sp <- min(spoken_mts_no0Sd_no0Sd_dcast_2$PC1 + 0.5)
x_max_sp <- max(spoken_mts_no0Sd_no0Sd_dcast_2$PC1 + 0.5)

y_min_sp <- min(spoken_mts_no0Sd_no0Sd_dcast_2$PC2 + 0.5)
y_max_sp <- max(spoken_mts_no0Sd_no0Sd_dcast_2$PC2 + 0.5)

z_min_sp <- min(spoken_mts_no0Sd_no0Sd_dcast_2$PC3 + 0.5)
z_max_sp <- max(spoken_mts_no0Sd_no0Sd_dcast_2$PC3 + 0.5)

  # breaks
xBreaks_sp <- getPrettyAxisBreaks(spoken_mts_no0Sd_no0Sd_dcast_2$PC1, min.n = 4)
  
yBreaks_sp <- getPrettyAxisBreaks(spoken_mts_no0Sd_no0Sd_dcast_2$PC2, min.n = 4)

zBreaks_sp <- getPrettyAxisBreaks(spoken_mts_no0Sd_no0Sd_dcast_2$PC3, min.n = 4)
  
  x_min_sp <- xBreaks_sp[1]
  x_max_sp <- xBreaks_sp[length(xBreaks_sp)]
  y_min_sp <- yBreaks_sp[1]
  y_max_sp <- yBreaks_sp[length(yBreaks_sp)]
  
   z_min_sp <- zBreaks_sp[1]
  z_max_sp <- zBreaks_sp[length(zBreaks_sp)]
  # Adjust the graining
  hs_sp <- min(c(diff(range(xBreaks_sp)), diff(range(yBreaks_sp)))) / 50
  hs_z_sp <- min(c(diff(range(yBreaks_sp)), diff(range(zBreaks_sp)))) / 50
  
  # grid_sp <- as.data.frame(expand.grid(seq(x_min_sp, x_max_sp, by = hs_sp), 
  #                                   seq(y_min_sp, y_max_sp, by = hs_sp),
  #                                   seq(z_min_sp, z_max_sp, by = hs_z_sp),
  #                                   ))
  

df <- expand.grid(PC1 = seq(x_min_sp, x_max_sp, 
                                            by = hs_sp
                            # length.out = 100
                            ),
                  PC2 = seq(y_min_sp, y_max_sp,
                                              by = hs_sp
                           # length.out = 100 
                           ),
                  
                  PC3 = seq(z_min_sp, z_max_sp ,
                                             by = hs_z_sp
                            # length.out = 100
                            )
                  )

df


df_agg<-df%>%
  group_by(expression)%>%
  summarise_if(is.numeric,mean, na.rm=T)

df$expression <- predict(spoken_rf, df)

  
ggplot(df_agg, aes(PC1, PC2,fill = expression)) +
  geom_raster(aes(fill = expression),alpha = 0.01, size = 0) +
  # geom_tile(aes(fill = expression),alpha = 0.01, size = 0) +
  # stat_contour(data = df,aes(x =PC1, y =PC2, z = expression))
   geom_point(data =spoken_mts_no0Sd_no0Sd_dcast_2,aes( colour =expression,fill = expression),size = 3) +
  geom_point(data = spoken_mts_no0Sd_no0Sd_dcast_2, shape = 21, size = 3) +
  # theme_minimal()
  # theme_void()+

  theme_bw() +
      plot_style+
  scale_color_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")+
    # scale_color_viridis_d()+
    # scale_fill_viridis_d()+
  # theme(panel.border = element_blank(),
  #      panel.grid.major = element_blank(),
  #      panel.grid.minor = element_blank())+
  base_breaks_x(df$PC1) +
  base_breaks_y(df$PC2)+
  ylab("comp2")+
  xlab("comp1")


```



boundaryplots$pc1_2_ggside_sp
library(ggside)

```{r}
df_sp$expression<- factor(df_sp$expression, levels = c('angry', 'happy', 'sad', 'neutral'))
# spoken_mts_no0Sd_no0Sd_dcast_2$expression<- factor(spoken_mts_no0Sd_no0Sd_dcast_2$expression, levels = c('angry', 'happy', 'sad', 'neutral'))

df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts

df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$expression<- factor(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$expression, levels = c('angry', 'happy', 'sad', 'neutral'))


boundaryplots$SPOKEN_PC1_2

spoken_r.forest
spoken_rf_nomts
df_sp$expression <- predict(spoken_r.forest, df_sp)


boundaryplots$SPOKEN_PC1_2<-
ggplot(df_sp, aes(comp1_maxnorm, comp2_maxnorm,fill = expression)) +
  geom_raster(aes(fill = expression),alpha = .5, size = 0)+

 # geom_tile(aes(fill = expression),alpha = 0.01, size = 0) +
   geom_point(data =df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts,aes( colour =expression,fill = expression),size = 3) +
  geom_point(data = df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts, shape = 21, size = 3) +
  
  geom_ysideboxplot(data = df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts,aes(x = expression,colour =expression), orientation = "x",alpha = .5)+
  scale_ysidex_discrete(guide = guide_axis(angle = 90))+
  geom_xsidedensity(data = df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts,aes(fill = expression,colour =expression), alpha = .5,show.legend =FALSE)+
   scale_xsidey_continuous(breaks = NULL)+
  # theme(axis.text.x = element_text(size = 10))+
  theme_bw() +
      plot_style+
     # scale_ysidex_discrete(guide = guide_axis(angle = 90))+
     theme(ggside.panel.scale = .2)+
  scale_color_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")+
  # facet_grid(~expression)

  base_breaks_x(df_sp$comp1_maxnorm) +
  base_breaks_y(df_sp$comp2_maxnorm)+
  xlab("comp1")+
  ylab("comp2")

boundaryplots$SPOKEN_PC1_2

boundaryplots$SPOKEN_PC1_2

getleg2 <-cowplot::get_legend(boundaryplots$SPOKEN_PC1_2_getleg) 

boundaryplots$SPOKEN_PC1_2_getleg<-boundaryplots$SPOKEN_PC1_2


boundaryplots$SPOKEN_PC1_2<- boundaryplots$SPOKEN_PC1_2+
  theme(plot.title = element_text(size = 16*(sf+.5), hjust = 0.5),
        # axis.title.x = element_blank(),
       legend.position = "none"
       )

```


boundaryplots$SPOKEN_PC1_2

```{r}



df_sp$expression<- factor(df_sp$expression, levels = c('angry', 'happy', 'sad', 'neutral'))

df$expression<- factor(df$expression, levels = c('angry', 'happy', 'sad', 'neutral'))
spoken_mts_no0Sd_no0Sd_dcast_2$expression<- factor(spoken_mts_no0Sd_no0Sd_dcast_2$expression, levels = c('angry', 'happy', 'sad', 'neutral'))

df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts

df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$expression<- factor(df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts$expression, levels = c('angry', 'happy', 'sad', 'neutral'))

# mts
boundaryplots$SPOKEN_PC1_2_mts<-
ggplot(df, aes(PC1, PC2,fill = expression)) +
  
  # geom_raster(aes(fill = expression),alpha = .5, size = 0)+

 geom_tile(aes(fill = expression),alpha = 0.01, size = 0) +
   geom_point(data =spoken_mts_no0Sd_no0Sd_dcast_2,aes( colour =expression,fill = expression),size = 3) +
  geom_point(data = spoken_mts_no0Sd_no0Sd_dcast_2, shape = 21, size = 3) +
  
  geom_ysideboxplot(data = spoken_mts_no0Sd_no0Sd_dcast_2,aes(x = expression,colour =expression), orientation = "x",alpha = .5)+
  scale_ysidex_discrete(guide = guide_axis(angle = 90))+
  geom_xsidedensity(data = spoken_mts_no0Sd_no0Sd_dcast_2,aes(fill = expression,colour =expression), alpha = .5,show.legend =FALSE)+
   scale_xsidey_continuous(breaks = NULL)+
  # theme(axis.text.x = element_text(size = 10))+
  theme_bw() +
      plot_style+
     # scale_ysidex_discrete(guide = guide_axis(angle = 90))+
     theme(ggside.panel.scale = .2)+
  scale_color_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")+

  base_breaks_x(df$PC1) +
  base_breaks_y(df$PC2)+
  xlab("comp1")+
  ylab("comp2")

boundaryplots$SPOKEN_PC1_2_mts

# boundaryplots$SPOKEN_PC1_2_getleg<-boundaryplots$SPOKEN_PC1_2


boundaryplots$SPOKEN_PC1_2_mts<- boundaryplots$SPOKEN_PC1_2_mts+
  theme(plot.title = element_text(size = 16*(sf+.5), hjust = 0.5),
        # axis.title.x = element_blank(),
       legend.position = "none"
       )

boundaryplots$SPOKEN_PC1_2_mts

```


```{r}
unique()

range(df_sp$comp2_maxnorm)
boundaryplots$SPOKEN_PC2_3<-
ggplot(df_sp, aes(comp2_maxnorm, comp3_maxnorm,fill = expression)) +
  # geom_raster(aes(fill = expression),alpha = .2, size = 0)+
   geom_raster(aes(fill = expression),alpha = .5, size = 0)+

  # geom_tile(aes(fill = expression),alpha = 0.01, size = 0) +
   geom_point(data =df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts,aes( colour =expression,fill = expression),size = 3) +
  geom_point(data = df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts, shape = 21, size = 3) +
  
  geom_ysideboxplot(data = df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts,aes(x = expression,colour =expression), orientation = "x",alpha = .5)+
  scale_ysidex_discrete(guide = guide_axis(angle = 90))+
  geom_xsidedensity(data = df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts,aes(fill = expression,colour =expression), alpha = .5,show.legend =FALSE)+
   scale_xsidey_continuous(breaks = NULL)+
  # theme(axis.text.x = element_text(size = 10))+
  theme_bw() +
      plot_style+
     # scale_ysidex_discrete(guide = guide_axis(angle = 90))+
     theme(ggside.panel.scale = .2)+
  scale_color_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")+

  base_breaks_x(df_sp$comp2_maxnorm) +
  base_breaks_y(df_sp$comp3_maxnorm)+
  xlab("comp2")+
  ylab("comp3")


boundaryplots$SPOKEN_PC2_3<- boundaryplots$SPOKEN_PC2_3+
  theme(plot.title = element_text(size = 16*(sf+.5), hjust = 0.5),
        # axis.title.x = element_blank(),
       legend.position = "none"
       )
boundaryplots$SPOKEN_PC2_3
```



```{r}
boundaryplots$SPOKEN_PC3_1 <-
ggplot(df_sp, aes(comp3_maxnorm, comp1_maxnorm,fill = expression)) +

  geom_raster(aes(fill = expression),alpha = .5, size = 0) +
  ##geom_tile(aes(fill = expression),alpha = 0.01, size = 0) +
   geom_point(data =df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts,aes( colour =expression,fill = expression),size = 3) +
  geom_point(data = df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts, shape = 21, size = 3) +
  
  geom_ysideboxplot(data = df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts,aes(x = expression,colour =expression), orientation = "x",alpha = .5)+
  scale_ysidex_discrete(guide = guide_axis(angle = 90))+
  geom_xsidedensity(data = df_OF_output_AUsW_unblind_spoken1_binned_agg_no_ts,aes(fill = expression,colour =expression), alpha = .5,show.legend =FALSE)+
   scale_xsidey_continuous(breaks = NULL)+
  # theme(axis.text.x = element_text(size = 10))+
  theme_bw() +
      plot_style+
     # scale_ysidex_discrete(guide = guide_axis(angle = 90))+
     theme(ggside.panel.scale = .2)+
  scale_color_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")+

  base_breaks_x(df_sp$comp3_maxnorm) +
  base_breaks_y(df_sp$comp1_maxnorm)+
  xlab("comp3")+
  ylab("comp1")


boundaryplots$SPOKEN_PC3_1<- boundaryplots$SPOKEN_PC3_1+
  theme(plot.title = element_text(size = 16*(sf+.5), hjust = 0.5),
        # axis.title.x = element_blank(),
       legend.position = "none"
       )


boundaryplots$SPOKEN_PC3_1

```


boundaryplots$SPOKEN_PC3_1
```{r}
boundaryplots$SPOKEN_PC3_1<-
ggplot(df_sp, aes(comp3_maxnorm, comp1_maxnorm,fill = expression)) +

  geom_raster(aes(fill = expression),alpha = .5, size = 0)+
  ##geom_tile(aes(fill = expression),alpha = 0.01, size = 0) +
   geom_point(data =spoken_mts_no0Sd_no0Sd_dcast_2,aes( colour =expression,fill = expression),size = 3) +
  geom_point(data = spoken_mts_no0Sd_no0Sd_dcast_2, shape = 21, size = 3) +
  
  geom_ysideboxplot(data = spoken_mts_no0Sd_no0Sd_dcast_2,aes(x = expression,colour =expression), orientation = "x",alpha = .5)+
  scale_ysidex_discrete(guide = guide_axis(angle = 90))+
  geom_xsidedensity(data = spoken_mts_no0Sd_no0Sd_dcast_2,aes(fill = expression,colour =expression), alpha = .5,show.legend =FALSE)+
   scale_xsidey_continuous(breaks = NULL)+
  # theme(axis.text.x = element_text(size = 10))+
  theme_bw() +
      plot_style+
     # scale_ysidex_discrete(guide = guide_axis(angle = 90))+
     theme(ggside.panel.scale = .2)+
  scale_color_brewer(palette = "Dark2")+
    scale_fill_brewer(palette = "Dark2")+

  base_breaks_x(df_sp$comp3_maxnorm) +
  base_breaks_y(df_sp$comp1_maxnorm)+
  xlab("comp3")+
  ylab("comp1")


boundaryplots$SPOKEN_PC3_1<- boundaryplots$SPOKEN_PC3_1+
  theme(plot.title = element_text(size = 16*(sf+.5), hjust = 0.5),
        # axis.title.x = element_blank(),
       legend.position = "none"
       )

boundaryplots$SPOKEN_PC3_1
```


Heat map

```{r}

paper_plots$conf_mat_posed 

# spoken_test_set_res<- confusionMatrix(spoken_test_set$prediction , as.factor(spoken_test_set$expression), mode = "everything", positive="1")
paper_plots$conf_mat_spoken <-
as.data.frame(confusionMatrix(spoken_test_set$prediction , as.factor(spoken_test_set$expression), mode = "everything", positive="1")[["table"]])%>%
  mutate(prop = Freq/15)%>%
  mutate(Reference = factor(Reference, levels = c('angry', 'happy', 'sad', 'neutral')),
          Prediction = factor(Prediction, levels = c('angry', 'happy', 'sad', 'neutral')))%>%
      ggplot(aes(Reference,Prediction, fill = prop))+
    geom_tile()+
       # scale_fill_viridis_c(option = "magma")
    scale_fill_viridis_c(option = "magma", breaks=c(0,.5,1),
                       limits =c(0,1))+
  xlab("Expression")+
  ylab("Prediction")+
  
  theme_bw()+
  plot_style+
  guides(fill=guide_colorbar(ticks.colour = NA))+
  theme(panel.spacing = unit(1, "cm"),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(angle = 45, hjust = 1), 
        legend.position = "top"
        )

paper_plots$conf_mat_spoken


paper_plots$spoken_classif_panel<-
(boundaryplots$SPOKEN_PC1_2 + 
  patchwork::wrap_elements(getleg2)+

  plot_spacer() +
  boundaryplots$SPOKEN_PC2_3+
    boundaryplots$SPOKEN_PC3_1+ 
  paper_plots$conf_mat_spoken)


ggsave("spoken_classif_pane.tiff",  paper_plots$spoken_classif_pane,
       device = "tiff",
       width = 20,
       # 
       height = 10,
       dpi = 800
       )

```
  
  

paper_plots$conf_mat_posed

ROCR


ROCs
```{r}
library(caret)
library(pROC)
install.packages("plotROC")

result.predicted.prob <- predict(forest.model, data.test, type="prob") # Prediction

 # Generate predictions for each class
colnames(spoken_test_set)
 test_set$prediction <- predict(r.forest_mts, test_set)
 
 spoken_test_set$prediction
 
 # one vs all
 spoken_test_set$D_ha <- if_else( spoken_test_set$prediction == "happy",1,0 )
 spoken_test_set$D_an <- if_else( spoken_test_set$prediction == "angry",1,0 ) 
 spoken_test_set$D_sa <- if_else( spoken_test_set$prediction == "sad",1,0 )  
  spoken_test_set$D_ne <- if_else( spoken_test_set$prediction == "neutral",1,0 )  
 
  colnames(spoken_test_set)
 colnames(spoken_test_set[,c(69:71, 73:75)])
 
 melt_roc(spoken_test_set[,c(69:71, 73:75)], c('D_ha', 'D_sa', 'D_an'), c("PC1", "PC2","PC3"))[,c(1:3,10:11)]%>%
 

 
 library(ROCR)
 
 # install.packages("klaR")
library(klaR)
 
 aucs = c()
 
 plot(x=NA, y=NA, xlim=c(0,1), ylim=c(0,1),
     ylab='True Positive Rate',
     xlab='False Positive Rate',
     bty='n')
 for (type.id in 1:3) {
   
  train_set$type = as.factor(train_set$expression == lvls[type.id])
   rocmod<-train(type ~ PC1 + PC2 + PC3,
                 data = train_set,
                method = "rf",
                type = "raw",
                ntree = 30)

   
   rocmod
spoken_test_set$type<- as.factor(spoken_test_set$expression == lvls[type.id])
  
  # spoken_test_set$expression




  
nbprediction = predict(rocmod, spoken_test_set)
# klaR::
score=   predict(rocmod, spoken_test_set, type = 'prob')


  # score$dots
    actual.class = spoken_test_set$expression == lvls[type.id]
  # actual.class = iris.test$Species == lvls[type.id]
?prediction
  pred <- prediction(as.numeric(nbprediction), as.numeric(actual.class))
  nbperf = performance(pred, "tpr", "fpr")

  roc.x = unlist(nbperf@x.values)
  roc.y = unlist(nbperf@y.values)
  lines(roc.y ~ roc.x, col=type.id+1, lwd=2)

  nbauc = performance(pred, "auc")
  nbauc = unlist(slot(nbauc, "y.values"))
  aucs[type.id] = nbauc
 }
 
 
 # predict test set, get probs instead of response
predictions <- as.data.frame(predict(r.forest_mts, spoken_test_set, type = "prob"))

# predict class and then attach test class
predictions$predict <- names(predictions)[1:3][apply(predictions[,1:3], 1, which.max)]
predictions$observed <- spoken_test_set$expression
head(predictions)

# 1 ROC curve, mock vs non mock
roc.happy <- roc(ifelse(predictions$observed=="happy", "happy", "rest"), as.numeric(predictions$happy))
plot(roc.happy, col = "gray60")

# others
roc.sad_main <- roc(ifelse(predictions$observed=="sad", "sad", "rest"), as.numeric(predictions$sad))

roc.sad_main$auc
roc.angry <- roc(ifelse(predictions$observed=="angry", "angry", "rest"), as.numeric(predictions$angry))
# roc.angry$auc

roc.happy$auc
roc_p<- plot(roc.happy, col = "gray60")
lines(roc.sad, col = "blue")
lines(roc.angry, col = "red")

as.data.frame(roc.sad$sensitivities)
as.data.frame(roc.happy$sensitivities)
as.data.frame(roc.angry$sensitivities)

roc.sad<- cbind(as.data.frame(roc.sad$specificities), as.data.frame(roc.sad$sensitivities))
roc.sad$expression = "sad"

rochappydf<- cbind(as.data.frame(roc.happy$specificities), as.data.frame(roc.happy$sensitivities))
rochappydf$expression<-"happy"

rocangrydf<- cbind(as.data.frame(roc.angry$specificities), as.data.frame(roc.angry$sensitivities))
rocangrydf$expressin <- "angry"

names(roc.sad) <- c('specificities', 'sensitivities', 'expression')
names(rochappydf) <- c('specificities', 'sensitivities', 'expression')
names(rocangrydf) <- c('specificities', 'sensitivities', 'expression')

roc_combined<- rbind(roc.sad,rochappydf,rocangrydf)
roc.happy$sensitivities

colnames(roc_combined)

length(roc.happy$specificities)
# 
ggplot()+
  geom_line(aes(x = sort(1- roc.happy$specificities), y = sort(roc.happy$sensitivities)),colour = "red")+
  # geom_path()
  geom_line(aes(x = sort(1-roc.sad$specificities), y = sort(roc.sad$sensitivities)),colour = "blue")+
    geom_line(aes(x = sort(1-roc.angry$specificities), y = sort(roc.angry$sensitivities)),color = "green")+
 
   geom_line(aes(x = seq(0,1,by = .1), y = seq(0,1,by = .1)),linetype = "dashed", size = 2)+
  geom_line(aes(y = rep(1,each = 11), x = seq(0,1,by = .1)),linetype = "dashed", size = 2)+
   geom_line(aes(x = rep(0,each = 11), y = seq(0,1,by = .1)),linetype = "dashed", size = 2)


paper_plots$ROC_posed<-

roc_combined%>%
  group_by(expression)%>%
  mutate(specificities = sort(1- specificities),
         sensitivities = sort(sensitivities))%>%
  ungroup()%>%
  mutate(expression = if_else(expression == "angry", paste0("angry: AUC = ",substr(as.character(roc.angry$auc),1,4)),
if_else(expression == "happy", paste0("happy: AUC = ",substr(as.character(roc.happy$auc),1,4)),
        paste0("sad:    AUC = ",substr(as.character(roc.sad_main$auc),1,4)))))%>%
ggplot(aes(x =  specificities, y = sensitivities, group = expression, colour = expression))+
  # geom_line(aes(y = rep(1,each = 44), x = seq(0,1,by = .023)), size = 1.5, colour = "black",
            # linetype = "dotted", alpha = .5)+
   # geom_line(aes(x = rep(0,each = 44), y = seq(0,1,by = .023)), size = 1.5, colour = "black",
            # linetype = "dotted", alpha = .5) +
  geom_point(aes(x = 0, y = 1),colour = "black", size = 2)+
  geom_line(size = 1.5)+
   geom_line(aes(x = seq(0,1,by = .023), y = seq(0,1,by = .023)),linetype = "dashed", size = 2, color = "black")+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
    base_breaks_x(1-roc_combined$specificities) +
  base_breaks_y(roc_combined$sensitivities)+
  annotate( "text",x = 0.15,y=1.05, label = "Perfect separation")+
  xlab("FPR")+
  ylab("TPR")+
  # annotate( "text",x = 0.0999,y=1.05, label = paste0("AUC=", roc.happy$auc)+
  
  theme_bw()+
  plot_style+
  theme(legend.position = c(.75,.2))


```




