---
title: "preprocess_halofacestudy"
author: "Helio Clemente Cuve, PhD"
date: '2022-06-06'
output: html_document
---


useful details
#experimental conditions
3 expression conditions (posed, spoken and spoken2)
3 emotion categeories (happy, angry, sad)
Spoken has 4 emotions (H. A. S and Neutral)
Spoken 2 is the additional for all but was never analysed before

# labels
each video is labeled with the day (1 or 2) - see unblinding_BMY_drugday
- this is needed to group the drug vs placebo correctly

notes
- some participants we only have day 1 data 

no data for p9 as he refused to do the task and then day 1 data only for 4, 12, 26, 34, 35, 41, 42 and 43 

Setup preferences
```{r}
# set working directory
setwd("/Volumes/GoogleDrive-113094219255455017404/My Drive/2022 - University Of Birmingham/HaloStudy/Data/openFaceProcessed")
setwd("/Volumes/GoogleDrive-113094219255455017404/My Drive/2022 - University Of Birmingham/RE-CUT_VIDEOS_23.05.22-20220523T152230Z-001/RE-CUT_VIDEOS_23.05.22/openFaceProcessed")

# load libraries
library(tidyverse)
library(data.table)
library(readr)

```

load 'csv' openFace fileand bind into one large dataframe while storing file name in a separate column

```{r}
# fcuntion to read append filename to dataframne
read_plus <- function(flnm) {
  data.table::fread(flnm) %>% 
    mutate(filename = flnm)
}

# now read them
df_OF_output <-
  list.files(pattern = "*.csv", 
             full.names = T) %>% 
  map_df(~read_plus(.))
# to do, add a progress bar


# quick inspection fo the data
df_OF_output
dim(df_OF_output)
colnames(df_OF_output)
# summary(df_OF_output) # takes time for a this big od a df
colnames(df_OF_output)
table(is.na(df_OF_output$filename))
 
### The head() and tail() functions default to 6 rows, but we can adjust the number of rows using the "n = " argument
head(df_OF_output, n = 10) #first 10 rows
tail(df_OF_output, n = 5) #last 5 rows


```

1 - now reduce the dataset into a set we actually need (AUS)
2 - merge with unblinding data
3 - do some quick visualisations

```{r}
colnames(df_OF_output)

df_OF_output_AUs<- df_OF_output[,c(1:5,680:715)]
# AU r = intensity c is presence
colnames(df_OF_output_AUs)

unique(df_OF_output_AUs$filename)

# rename action units based on a dictionary I created for the NMF tutorial
# setwd("/Volumes/GoogleDrive-113094219255455017404/My Drive/2022 - University Of Birmingham/HaloStudy/Data")

AU_OF_codes_merged <- readr::read_csv("AU_OF_codes_merged.csv")
AU_OF_transposed <- read_csv("AU_OF_transposed.csv")
AU_Wiki <- read_csv("AU_Wiki.csv")
AU_OF_transposed

# AU weights
AU_OF_codes_merged$AU_Code_OF_r<- paste0(AU_OF_codes_merged$AU_Code_OF,paste0("_",AU_OF_codes_merged$FACS_name))

# codes for AU presence
AU_OF_codes_merged$AU_Code_OF_c<- paste0("AU",AU_OF_codes_merged$AU_CODE,paste0("_c_", AU_OF_codes_merged$FACS_name))


colnames(df_OF_output_AUs)

# quick check
df_OF_output_AUs%>%
  ggplot(aes(AU01_r))+
  geom_histogram()

df_OF_output_AUs%>%
  ggplot(aes(AU01_c))+
  geom_histogram()

# rename AUS based on appended names and codes
t(AU_OF_codes_merged$AU_Code_OF_r)
t(AU_OF_codes_merged$AU_Code_OF_c)

cnames1 <- colnames(df_OF_output_AUs)
(17*2)+6
cname2<-c(cnames1[1:5],t(AU_OF_codes_merged$AU_Code_OF_r),t(AU_OF_codes_merged$AU_Code_OF_c), "filename")
# cnames1
# t(AU_OF_codes_merged$AU_Code_OF_r)
# note OF addded a new action fpr presence 28 (lipsuck) I will exclude this for now
df_OF_output_AUs$AU28_c<-NULL

# df_OF_output_AUstest<-df_OF_output_AUs
# names(df_OF_output_AUstest)<- cname2
names(df_OF_output_AUs)<- cname2


colnames(df_OF_output_AUs)

# now merge unblinding data

library(readxl)
Unblinding_BMI_drugday <- read_excel("Unblinding_BMI_drugday.xlsx")
View(Unblinding_BMI_drugday)

df_OF_output_AUs$filename
unique(
df_OF_output_AUs$filename)

# return the string between "_p and ,csv = this will be the particiapnt code

library(stringr)

df_OF_output_AUs$subject<- sub(".*_p", "", str_match(df_OF_output_AUs$filename, "p\\s*(.*?)\\s*.csv")[,2])

# testday

df_OF_output_AUs$test.day<- str_match(df_OF_output_AUs$filename, "_day\\s*(.*?)\\s*_p")[,2]


unique(df_OF_output_AUs$subject)
# how many participants do we expect = 43, checks out
Unblinding_BMI_drugday

names(Unblinding_BMI_drugday)<- make.names(names(Unblinding_BMI_drugday))
Unblinding_BMI_drugday

# merge
df_OF_output_AUs$subject<- as.factor(as.character( df_OF_output_AUs$subject))
Unblinding_BMI_drugday$subject<-as.factor(as.character(Unblinding_BMI_drugday$subject))

# expected rows()
# nrow(df_OF_output_AUs)  =131476
df_OF_output_AUs_unblind<- left_join(df_OF_output_AUs, Unblinding_BMI_drugday)

# if test.day == drugday  = "halo, vs placebo
colnames(df_OF_output_AUs_unblind)

df_OF_output_AUs_unblind$drug.placebo <- if_else(df_OF_output_AUs_unblind$test.day == df_OF_output_AUs_unblind$drug.day, "drug", "placebo")

# add emotion
# return word between 3rd and 4rth underscore df$values = sapply(strsplit(df$V1, "_"), function(x) x[3])
unique( sapply(strsplit(df_OF_output_AUs_unblind$filename, "_"), function(x) x[3]))

df_OF_output_AUs_unblind$expression <-sapply(strsplit(df_OF_output_AUs_unblind$filename, "_"), function(x) x[3])
# 2nd and 3rd undrcore
# unique( sapply(strsplit(df_OF_output_AUs_unblind$filename, "_"), function(x) x[2]))
df_OF_output_AUs_unblind$posed.spoken<- sapply(strsplit(df_OF_output_AUs_unblind$filename, "_"), function(x) x[2])


unique(df_OF_output_AUs_unblind$posed.spoken)

```

Do some quick visualizations for time, etc

```{r}
# lets see distribution of duration
df_OF_output_AUs_unblind%>%
  subset(test.day ==1)%>%
  group_by(filename,test.day, expression,posed.spoken)%>%
  summarise_at(c("timestamp", "frame"), max, na.rm = T)%>%
  ggplot(aes(frame))+
  geom_histogram()+
  theme_classic()+
  facet_grid(expression~posed.spoken)

df_OF_output_AUs_unblind%>%
  subset(test.day ==2)%>%
  group_by(filename,test.day, expression,posed.spoken)%>%
  summarise_at(c("timestamp", "frame"), max, na.rm = T)%>%
  ggplot(aes(timestamp))+
  geom_histogram()+
  theme_classic()+
  facet_grid(expression~posed.spoken)





```

Visualise heatmaps for action units

```{r}
# store weights only
colnames(df_OF_output_AUs_unblind)
df_OF_output_AUsW_unblind<- df_OF_output_AUs_unblind[,c(1:5,40:49,6:22)]

df_OF_output_AUsW_unblind%>%
  gather(AUs, AU.coefs, -(1:15))%>%
  group_by(timestamp,frame, AUs, expression,drug.placebo)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(frame), AUs, fill = AU.coefs))+
    geom_tile()+
    facet_grid(drug.placebo~expression)+
    theme_classic()+
  theme(axis.text.y = element_blank())


df_OF_output_AUsW_unblind%>%
  gather(AUs, AU.coefs, -(1:15))%>%
  group_by(timestamp,frame, AUs,posed.spoken,drug.placebo)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(frame), AUs, fill = AU.coefs))+
    geom_tile()+
    facet_grid(posed.spoken~drug.placebo)+
    theme_classic()+
  theme(axis.text.y = element_blank())+
  # scale_fill_viridis_c(option = "plasma")
  # scale_fill_viridis_c()
  scale_fill_viridis_c(option = "magma")
  
  # check emotion differences
  df_OF_output_AUsW_unblind%>%
  gather(AUs, AU.coefs, -(1:15))%>%
  group_by(timestamp,frame, AUs,expression,posed.spoken)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(frame), AUs, fill = AU.coefs))+
    geom_tile()+
    facet_grid(posed.spoken~expression)+
    theme_classic()+
  theme(axis.text.y = element_blank())+
  # scale_fill_viridis_c(option = "plasma")
  # scale_fill_viridis_c()
  scale_fill_viridis_c(option = "magma")


```


binify based on moving average to we have comparable number of bins

start by separating just emotion

```{r}
df_OF_output_AUsW_unblind_posed<- subset(df_OF_output_AUsW_unblind, 
                                         posed.spoken == "posed")

df_OF_output_AUsW_unblind_posed

df_OF_output_AUsW_unblind_posed%>%
  subset(test.day ==1)%>%
  group_by(filename,test.day, expression,posed.spoken)%>%
  summarise_at(c("timestamp", "frame"), max, na.rm = T)%>%
  ggplot(aes(frame))+
  geom_histogram()+
  theme_classic()+
  facet_grid(expression~posed.spoken)


 # = 100 bins
# average is 250
# 220/100

df_OF_output_AUsW_unblind_posed
?cut
colnames(df_OF_output_AUsW_unblind_posed)
df_OF_output_AUsW_unblind_posed_binned <-df_OF_output_AUsW_unblind_posed%>%
  group_by(filename, subject,test.day, age, gender,BMI,drug.day, drug.placebo, expression )%>%
  mutate(bin_frame = cut(frame, 100, labels = FALSE))%>%
  group_by(filename,bin_frame,subject,test.day, age, gender,BMI,drug.day, drug.placebo, expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)
 
 
df_OF_output_AUsW_unblind_posed_binned$filename
# "./cut_posed_angry_day1_p1.csv"
colnames(df_OF_output_AUsW_unblind_posed_binned)
df_OF_output_AUsW_unblind_posed_binned%>%
  subset(filename == "./cut_posed_angry_day1_p1.csv")%>%
    gather(AUs, AU.coefs, -(1:15))%>%
  group_by(bin_frame, AUs,expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(bin_frame), AUs, fill = AU.coefs))+
    geom_tile()+
    # facet_grid(posed.spoken~expression)+
    theme_classic()+
  theme(axis.text.y = element_blank())+
  scale_fill_viridis_c(option = "magma")

# unbinned
df_OF_output_AUsW_unblind_posed%>%
  subset(filename == "./cut_posed_angry_day1_p1.csv")%>%
    gather(AUs, AU.coefs, -(1:15))%>%
  group_by(frame, AUs,expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(frame), AUs, fill = AU.coefs))+
    geom_tile()+
    # facet_grid(posed.spoken~expression)+
    theme_classic()+
  theme(axis.text.y = element_blank())+
  scale_fill_viridis_c(option = "magma")


# similar
# let's check lines

df_OF_output_AUsW_unblind_posed_binned%>%
  subset(filename == "./cut_posed_angry_day1_p1.csv")%>%
    gather(AUs, AU.coefs, -(1:15))%>%
  group_by(bin_frame, AUs,expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(bin_frame), AU.coefs, group = AUs))+
    geom_line()+
    # facet_grid(posed.spoken~expression)+
    theme_classic()+
  theme(axis.text.y = element_blank())+
  scale_fill_viridis_c(option = "magma")


df_OF_output_AUsW_unblind_posed%>%
  subset(filename == "./cut_posed_angry_day1_p1.csv")%>%
    gather(AUs, AU.coefs, -(1:15))%>%
  group_by(frame, AUs,expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(frame),AU.coefs, group = AUs))+
 geom_line()+
    # facet_grid(posed.spoken~expression)+
    theme_classic()+
  theme(axis.text.y = element_blank())+
  scale_fill_viridis_c(option = "magma")


df_OF_output_AUsW_unblind_posed_binned%>%
  subset(subject == 1)%>%
    gather(AUs, AU.coefs, -(1:15))%>%
  group_by(bin_frame, AUs,expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(bin_frame), AU.coefs, group = AUs))+
   geom_smooth(se = F)+
    # facet_grid(posed.spoken~expression)+
    theme_classic()+
  theme(axis.text.y = element_blank())+
  scale_fill_viridis_c(option = "magma")


df_OF_output_AUsW_unblind_posed%>%
  subset(subject == 1)%>%
    gather(AUs, AU.coefs, -(1:15))%>%
  group_by(frame, AUs,expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(frame),AU.coefs, group = AUs))+
  geom_smooth(se = F)+
    # facet_grid(posed.spoken~expression)+
    theme_classic()+
  theme(axis.text.y = element_blank())+
  scale_fill_viridis_c(option = "magma")


table(df_OF_output_AUsW_unblind_posed_binned$bin_frame)

```


do

for the actual analyses we want
1- learn spatiotemporal structure suing NMF
2 - does drug vs no drug differ in NMF metrics?
3- can we separate groups based on NMF components using BADIA

spatiotemporal dynmaics
- movement substates (initiation, sustainement, etc)
- if we use kmean clustering, do we have differences into how many substaes are there
- or if we use a fixed number of substaes, are there significant temporal differences (e.g. duration, reccurence)


Pre-Process speech data


```{r}
unique(df_OF_output_AUsW_unblind$posed.spoken)
df_OF_output_AUsW_unblind_spoken1_2<- subset(df_OF_output_AUsW_unblind, 
                                         posed.spoken != "posed")

df_OF_output_AUsW_unblind_spoken1_2

# check how variable is duration
df_OF_output_AUsW_unblind_spoken1_2%>%
  subset(test.day ==1)%>%
  group_by(filename,test.day, expression,posed.spoken)%>%
  summarise_at(c("timestamp", "frame"), max, na.rm = T)%>%
  ggplot(aes(frame))+
  geom_histogram()+
  theme_classic()+
  facet_grid(expression~posed.spoken)

```

```{r}
df_OF_output_AUsW_unblind_spoken1_2
 # = 100 bins
# average is 250
# 220/100

df_OF_output_AUsW_unblind_spoken1_2

# ?cut
colnames(df_OF_output_AUsW_unblind_spoken1_2)

# create bins
df_OF_output_AUsW_unblind_spoken1_2_binned <-df_OF_output_AUsW_unblind_spoken1_2%>%
  group_by(filename, subject,test.day, age, gender,BMI,drug.day, drug.placebo, expression )%>%
  mutate(bin_frame = cut(frame, 100, labels = FALSE))%>%
  group_by(filename,bin_frame,subject,test.day, age, gender,BMI,drug.day, drug.placebo, expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)
 
 
df_OF_output_AUsW_unblind_spoken1_2_binned$filename

# "./cut_spoken_angry_day1_p19.csv"
colnames(df_OF_output_AUsW_unblind_spoken1_2_binned)

# quick visualisation of how the bins would be
df_OF_output_AUsW_unblind_spoken1_2_binned%>%
  subset(filename == "./cut_spoken_angry_day1_p19.csv")%>%
    gather(AUs, AU.coefs, -(1:15))%>%
  group_by(bin_frame, AUs,expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(bin_frame), AUs, fill = AU.coefs))+
    geom_tile()+
    # facet_grid(posed.spoken~expression)+
    theme_classic()+
  theme(axis.text.y = element_blank())+
  scale_fill_viridis_c(option = "magma")


# unbined for comparison
df_OF_output_AUsW_unblind_spoken1_2%>%
  subset(filename == "./cut_spoken_angry_day1_p19.csv")%>%
    gather(AUs, AU.coefs, -(1:15))%>%
  group_by(frame, AUs,expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(frame), AUs, fill = AU.coefs))+
    geom_tile()+
    # facet_grid(posed.spoken~expression)+
    theme_classic()+
  theme(axis.text.y = element_blank())+
  scale_fill_viridis_c(option = "magma")


# very similar, so we can be confident that the binification is not screwing things up
```


# let's check the same plots in lines

```{r}

df_OF_output_AUsW_unblind_spoken1_2_binned%>%
  subset(filename == "./cut_spoken_angry_day1_p19.csv")%>%
    gather(AUs, AU.coefs, -(1:15))%>%
  group_by(bin_frame, AUs,expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(bin_frame), AU.coefs, group = AUs))+
    geom_line()+
    # facet_grid(posed.spoken~expression)+
    theme_classic()+
  theme(axis.text.y = element_blank())+
  scale_fill_viridis_c(option = "magma")



df_OF_output_AUsW_unblind_spoken1_2_binned%>%
  subset(filename == "./cut_spoken_angry_day1_p19.csv")%>%
    gather(AUs, AU.coefs, -(1:15))%>%
  group_by(frame, AUs,expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(frame),AU.coefs, group = AUs))+
 geom_line()+
    # facet_grid(posed.spoken~expression)+
    theme_classic()+
  theme(axis.text.y = element_blank())+
  scale_fill_viridis_c(option = "magma")


```
compare smoothed lines for binned vs unbinned spoken data
```{r}
df_OF_output_AUsW_unblind_spoken1_2_binned%>%
  # subset(filename == "./cut_spoken_angry_day1_p19.csv")%>%
  subset(subject == 1)%>%
    gather(AUs, AU.coefs, -(1:15))%>%
  group_by(bin_frame, AUs,expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(bin_frame), AU.coefs, group = AUs))+
   geom_smooth(se = F)+
    # facet_grid(posed.spoken~expression)+
    theme_classic()+
  theme(axis.text.y = element_blank())+
  scale_fill_viridis_c(option = "magma")



df_OF_output_AUsW_unblind_spoken1_2%>%
  subset(subject == 1)%>%
    gather(AUs, AU.coefs, -(1:15))%>%
  group_by(frame, AUs,expression)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subset(drug.placebo == "drug")%>%
    ggplot(aes(as.numeric(frame),AU.coefs, group = AUs))+
  geom_smooth(se = F)+
    # facet_grid(posed.spoken~expression)+
    theme_classic()+
  theme(axis.text.y = element_blank())+
  scale_fill_viridis_c(option = "magma")


table(df_OF_output_AUsW_unblind_posed_binned$bin_frame)

```
