---
title: "Similarity and confusion plots"
author: "Helio"
date: "12/04/2021"
output: html_document
---


<!-- load("D:/OneDrive - Nexus365/Face Morph Paper/Data/Fig10Plots.RData") -->

```{r}
confusion_byds_vt_full$Em<- substr(confusion_byds_vt_full$Emotion, 1,2)
confusion_byds_vt_full$Pr<- substr(confusion_byds_vt_full$Prediction, 1,2)


paper_plots$CMatrix_byGroup_global <-confusion_byds_vt_full %>%
  subset(Emotion != "Neutral")%>%
  mutate(pair = paste0(Emotion, Prediction))%>%
  # mutate(Emotion = as.factor(Emotion))%>%
  # mutate(Emotion = relevel(Emotion, ref = "Anger"))%>%
  # mutate(Prediction = as.factor(Prediction))%>%
  # mutate(Prediction = relevel(Prediction, ref = "Anger"))%>%
  group_by(pair, Emotion,Prediction, Em, Pr, VideoType)%>%
  summarise_at(c('Freq', 'Prop'), mean, na.rm = TRUE)%>%
  ggplot(aes(Em, Pr))+
  geom_raster(aes(fill = Prop, stat = 'identity'))+
  facet_grid(~VideoType)+
    theme_classic()+
  ylab("All")+
  xlab("Emotion")+
  p$graphstyle1+
  scale_fill_viridis_c(option = "plasma", breaks = c(0, .5, 1), limits = c(0,1))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

paper_plots$CMatrix_byGroup_global



```



```{r}

confusion_byds_vt_full$Em

dataset_labs<- c("High prot.", "Low prot.")
names(dataset_labs)<- c("ADFES", "JEFFE")

paper_plots$CMatrix_byGroup <-
  confusion_byds_vt_full%>%
  subset(Emotion != "Neutral")%>%
  mutate(pair = paste0(Emotion, Prediction))%>%
  mutate(Emotion = as.factor(Emotion))%>%
  mutate(Emotion = relevel(Emotion, ref = "Anger"))%>%
  mutate(Prediction = as.factor(Prediction))%>%
  mutate(Prediction = relevel(Prediction, ref = "Anger"))%>%
  group_by(pair, Emotion,Prediction,Em,Pr, VideoType, DATASET)%>%
  summarise_at(c('Freq', 'Prop'), mean, na.rm = TRUE)%>%
  ggplot(aes(Em, Pr))+
  geom_raster(aes(fill = Prop, stat = 'identity'))+
  facet_grid(DATASET~VideoType,
             # facet_grid(Dataset~morph,
             labeller = labeller(morph = confusion_byds_vt_full$VideoType, 
                                 DATASET = dataset_labs))+
  xlab("Emotion")+
  ylab("Response")

paper_plots$CMatrix_byGroup


paper_plots$CMatrix_byGroup<- paper_plots$CMatrix_byGroup+
  theme_classic()+
  p$graphstyle1+
  scale_fill_viridis_c(option = "plasma", breaks = c(0, .4, .8), limits = c(0,.8))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

paper_plots$CMatrix_byGroup
# confusion_byds_vt_full2<-
# confusion_byds_vt_full%>%
#   subset(Emotion != "Neutral")%>%
#   mutate(pair = paste0(Emotion, Prediction))%>%
#   mutate(Emotion = as.factor(Emotion))%>%
#   mutate(Emotion = relevel(Emotion, ref = "Anger"))%>%
#   mutate(Prediction = as.factor(Prediction))%>%
#   mutate(Prediction = relevel(Prediction, ref = "Anger"))%>%
#   group_by(pair, Emotion,Prediction, VideoType)
# max(confusion_byds_vt_full2$Prop )

paper_plots$CMatrix_byGroup


```



```{r}

# create high - low morph


confusion_byds_vt_full
unique(confusion_byds_vt_full$DATASET)
unique(confusion_byds_vt_full$VideoType)

write.csv( confusion_byds_vt_full, "confusion_byds_vt_full.csv")
high_vs_low_morph<- left_join(
subset(confusion_byds_vt_full, DATASET == "ADFES" & VideoType == "Morph"),
subset(confusion_byds_vt_full, DATASET != "ADFES" & VideoType == "Morph"),
by = c('Participant', 'Em', 'Pr', 'Emotion', 'Prediction'))%>%
  subset(Emotion != "Neutral")%>%
  mutate(pair = paste0(Emotion, Prediction))%>%
  mutate(Emotion = as.factor(Emotion))%>%
  mutate(Emotion = relevel(Emotion, ref = "Anger"))%>%
  mutate(Prediction = as.factor(Prediction))%>%
  mutate(Prediction = relevel(Prediction, ref = "Anger"))%>%
  group_by(pair, Emotion,Prediction,Em,Pr)%>%
  summarise_at(c( 'Prop.x', 'Prop.y'), mean, na.rm = TRUE)%>%
  ggplot(aes(Em, Pr))+
  geom_raster(aes(fill = Prop.x-Prop.y, stat = 'identity'))+
  # # facet_grid(DATASET~VideoType,
  #            # facet_grid(Dataset~morph,
  #            labeller = labeller(morph = confusion_byds_vt_full$VideoType, 
  #                                DATASET = dataset_labs))+
  xlab("Emotion")+
  ylab("Prediction")+
  ggtitle("Morph (high - low prot)")

high_vs_low_morph <- high_vs_low_morph +
  theme_classic()+
  p$graphstyle1 +
  scale_fill_viridis_c(option = "plasma", breaks = c(-.8, 0, .8), limits = c(-.8,.8))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(size = 14),
        legend.position = "none") +
    guides(fill = guide_colourbar(ticks = FALSE, barwidth = 10, barheight = .5))


high_vs_low_morph
```


# original - high - low

```{r}

high_vs_low_original<-
left_join(
subset(confusion_byds_vt_full, DATASET == "ADFES" & VideoType != "Morph"),
subset(confusion_byds_vt_full, DATASET != "ADFES" & VideoType != "Morph"),
by = c('Participant', 'Em', 'Pr', 'Emotion', 'Prediction'))%>%
  subset(Emotion != "Neutral")%>%
  mutate(pair = paste0(Emotion, Prediction))%>%
  mutate(Emotion = as.factor(Emotion))%>%
  mutate(Emotion = relevel(Emotion, ref = "Anger"))%>%
  mutate(Prediction = as.factor(Prediction))%>%
  mutate(Prediction = relevel(Prediction, ref = "Anger"))%>%
  group_by(pair, Emotion,Prediction,Em,Pr)%>%
  summarise_at(c( 'Prop.x', 'Prop.y'), mean, na.rm = TRUE)%>%
  ggplot(aes(Em, Pr))+
  geom_raster(aes(fill = Prop.x-Prop.y, stat = 'identity'))+
  ggtitle("Original (high - low prot)")
  # # facet_grid(DATASET~VideoType,
  #            # facet_grid(Dataset~morph,
  #            labeller = labeller(morph = confusion_byds_vt_full$VideoType, 
  #                                DATASET = dataset_labs))+
  # xlab("Emotion")+
  # ylab("Prediction")+


high_vs_low_original <- high_vs_low_original +
 theme_classic()+
  p$graphstyle1 +
  scale_fill_viridis_c(option = "plasma", breaks = c(-.8, 0, .8), limits = c(-.8,.8))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        plot.title = element_text(size = 14)) +
    guides(fill = guide_colourbar(ticks = FALSE, barwidth = 10, barheight = .5))

high_vs_low_original
```

# High - original - morph


```{r}
original_vs_morph_ADFES<-  left_join(
subset(confusion_byds_vt_full, DATASET == "ADFES" & VideoType != "Morph"),
subset(confusion_byds_vt_full, DATASET == "ADFES" & VideoType == "Morph"),
by = c('Participant', 'Em', 'Pr', 'Emotion', 'Prediction'))%>%
  subset(Emotion != "Neutral")%>%
  mutate(pair = paste0(Emotion, Prediction))%>%
  mutate(Emotion = as.factor(Emotion))%>%
  mutate(Emotion = relevel(Emotion, ref = "Anger"))%>%
  mutate(Prediction = as.factor(Prediction))%>%
  mutate(Prediction = relevel(Prediction, ref = "Anger"))%>%
  group_by(pair, Emotion,Prediction,Em,Pr)%>%
  summarise_at(c( 'Prop.x', 'Prop.y'), mean, na.rm = TRUE)%>%
  ggplot(aes(Em, Pr))+
  geom_raster(aes(fill = Prop.x-Prop.y, stat = 'identity'))+
  ggtitle("High prot. (original - morph)")
  # # facet_grid(DATASET~VideoType,
  #            # facet_grid(Dataset~morph,
  #            labeller = labeller(morph = confusion_byds_vt_full$VideoType, 
  #                                DATASET = dataset_labs))+
  # xlab("Emotion")+
  # ylab("Prediction")+
  # theme_classic()+
  # p$graphstyle1+
  # scale_fill_viridis_c(option = "plasma")


original_vs_morph_ADFES<- original_vs_morph_ADFES+
  theme_classic()+
  p$graphstyle1 +
  scale_fill_viridis_c(option = "plasma", breaks = c(-.8, 0, .8), limits = c(-.8,.8))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        plot.title = element_text(size = 14),
        legend.position = "None") +
    guides(fill = guide_colourbar(ticks = FALSE, barwidth = 10, barheight = .5))




original_vs_morph_ADFES


```

# low - original - morph
```{r}
original_vs_morph_JEFEE<-  left_join(
subset(confusion_byds_vt_full, DATASET != "ADFES" & VideoType != "Morph"),
subset(confusion_byds_vt_full, DATASET != "ADFES" & VideoType == "Morph"),
by = c('Participant', 'Em', 'Pr', 'Emotion', 'Prediction'))%>%
  subset(Emotion != "Neutral")%>%
  mutate(pair = paste0(Emotion, Prediction))%>%
  mutate(Emotion = as.factor(Emotion))%>%
  mutate(Emotion = relevel(Emotion, ref = "Anger"))%>%
  mutate(Prediction = as.factor(Prediction))%>%
  mutate(Prediction = relevel(Prediction, ref = "Anger"))%>%
  group_by(pair, Emotion,Prediction,Em,Pr)%>%
  summarise_at(c( 'Prop.x', 'Prop.y'), mean, na.rm = TRUE)%>%
  ggplot(aes(Em, Pr))+
  geom_raster(aes(fill = Prop.x-Prop.y, stat = 'identity'))+
  ggtitle("Low prot. (original - morph)")
  # # facet_grid(DATASET~VideoType,
  #            # facet_grid(Dataset~morph,
  #            labeller = labeller(morph = confusion_byds_vt_full$VideoType, 
  #                                DATASET = dataset_labs))+
  # xlab("Emotion")+
  # ylab("Prediction")+
  # theme_classic()+
  # p$graphstyle1+
  # scale_fill_viridis_c(option = "plasma")



original_vs_morph_JEFEE<- original_vs_morph_JEFEE+
theme_classic()+
  p$graphstyle1 +
  scale_fill_viridis_c(option = "plasma", breaks = c(-.8, 0, .8), limits = c(-.8,.8))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(), axis.text.y = element_blank(),
        plot.title = element_text(size = 14),
        legend.position = "none") +
    guides(fill = guide_colourbar(ticks = FALSE, barwidth = 10, barheight = .5))

original_vs_morph_JEFEE
high_vs_low_original
high_vs_low_morph
original_vs_morph_ADFES
original_vs_morph_JEFEE
  
```


```{r}
paper_plots$Matrix_panel


 Study1_Matrix<- (((paper_plots$CMatrix_byGroup +  
  theme(legend.position = "none", axis.title.x = element_blank(),
                                     axis.text.x = element_blank())+
     guides(fill = guide_colourbar(ticks = FALSE, barwidth = 10, barheight = .5))
     ) /
    (paper_plots$CMatrix_byGroup_global +
    theme(legend.position = "none",
                                           # axis.title.y = element_blank(),
          strip.text = element_blank())+
  guides(fill = guide_colourbar(ticks = FALSE, barwidth = 10, barheight = .5))
  ))+ plot_layout()+plot_annotation() & theme(legend.title =
          element_text(size = 16), legend.position = 'top') |
   (paper_plots$Representation+ 
      theme(axis.title.x = element_blank())/
      (paper_plots$Representation_nodiag+
      theme(legend.position = "none")))) 
  # plot_layout(nrow = 2, ncol = 2, heights = c(2, 1), widths = c(1,1))+
   # +
   plot_annotation(tag_levels = "A") & 
  theme(plot.tag = element_text(size = 13)) 

 Study1_Matrix
 


paper_plots$CMatrix_byGrou <-  paper_plots$CMatrix_byGroup+guides(fill = guide_colourbar(ticks = FALSE, barwidth = 10, barheight = .5))


leftt_low<- (
high_vs_low_original+high_vs_low_morph)/(
 original_vs_morph_ADFES+original_vs_morph_JEFEE)+
  plot_layout(guides = 'keep')

left<- paper_plots$CMatrix_byGrou/ leftt_low

leftt_low
```


```{r}


# left <- left
   left

right<- paper_plots$Representation/ 
      paper_plots$Representation_nodiag
  

# left|right
new_matrix_plot <- left|right


# new_matrix_plot+ plot_layout(widths = c(2, 2), heights = unit(c(1, 1), c('cm', 'null')))

new_matrix_plot<- new_matrix_plot+
   plot_annotation(tag_levels = "A") & 
  theme(plot.tag = element_text(size = 16)) 


new_matrix_plot

 ggsave("Matrix_panel_new.png",  new_matrix_plot,device = 'png', width = 14, 
        height = 14, dpi = 800)  
ggsave("Study1_matrixpanel_new.tiff",  new_matrix_plot,device = 'tiff', 
       width = 14, height = 14, dpi = 800)

new_matrix_plot
```




```{r}

paper_plots$Representation <- 
bind_rows(confusion_byds_vt_full_coragg_ttest, confusion_byds_vt_full_coragg)%>%
  mutate(DATASET = as.factor(DATASET))%>%
  mutate(DATASET = relevel(DATASET, ref = 'Global'))%>%
  group_by(DATASET)%>%
  mutate(mean_acc = mean(cor_morph_orig, na.rm = TRUE))%>%
  group_by(Participant, DATASET)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subs
  ggplot(aes(DATASET, cor_morph_orig, colour = DATASET, fill = DATASET))+
  geom_half_violin(position = position_dodge(2), colour = FALSE, alpha = .3)+
  geom_jitter( width = .1,pch = 1, size = 2, alpha = .5)+
  geom_line(aes(group = Participant), colour = 'gray75', 
             size = .5, alpha = .3)+
    
  stat_summary(geom = 'errorbar', width = 0, size = 1.5)+
  stat_summary(geom = 'pointrange', width = 0, size = .5)+
    geom_hline(yintercept = 0, linetype = "dotted", size = 2, alpha  = .5)+
  theme_classic()+
    ylab("Similarity: morph - original (r)") +
  ggtitle("With diagonal")+



  p$graphstyle1+
  scale_y_continuous(breaks = c(.2, .6, 1), limits = c(.2,1))+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")
  
paper_plots$Representation<- paper_plots$Representation +
  theme(plot.title = element_text(size = 14), axis.title.x = element_blank())+
  scale_x_discrete(breaks=c("Global","ADFES","JEFFE"),
        labels=c("All", "High prot.", "Low prot."))+
  theme(axis.text.x = element_blank())+
  scale_x_discrete(breaks=c("All","ADFES","JEFFE"),
        labels=c("All", "High prot.", "Low prot."))+
  scale_color_discrete(name = "DATASET",
        labels=c("All", "High prot.", "Low prot."))+
  scale_fill_discrete(name = "DATASET",
        labels=c("All", "High prot.", "Low prot."))

paper_plots$Representation<- paper_plots$Representation+
    scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")

paper_plots$Representation
```


```{r}

# off Diagonal()
library(psych)

 confusion_byds_vt_full_cor%>%
  subset(Emotion!= Prediction)%>%
  group_by(Participant, DATASET)%>%
  mutate(cor_morph_orig = cor(Prop.x, Prop.y, use = 'complete.obs'))%>%
  # mutate(cor_morph_orig_z = fisherz(cor_morph_orig))%>%
  group_by(Participant)%>%
  mutate(cor_morph_orig_subj = cor(Prop.x, Prop.y, use = 'complete.obs'))%>%
  # mutate(cor_morph_orig_z_subj = fisherz(cor_morph_orig_subj))%>%
  group_by(Participant, DATASET)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)
 

 confusion_byds_vt_full_cor_nodiagnonal_agg 
 
 confusion_byds_vt_full_cor_nodiagnonal_agg1$DATASET<- "Global"
 
 
paper_plots$Representation_nodiag<-
bind_rows(confusion_byds_vt_full_cor_nodiagnonal_agg, confusion_byds_vt_full_cor_nodiagnonal_agg1)%>%
  # confusion_byds_vt_full_cor%>%
  # subset(Emotion!= Prediction)%>%
  mutate(DATASET = as.factor(DATASET))%>%
  mutate(DATASET = relevel(DATASET, ref = 'Global'))%>%
  # group_by(DATASET)%>%
  # mutate(mean_acc = mean(cor_morph_orig, na.rm = TRUE))%>%
  # group_by(Participant, DATASET)%>%
  # summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(Participant, DATASET)%>%
  # mutate(cor_morph_orig = cor(Prop.x, Prop.y, use = 'complete.obs'))%>%
  # # mutate(cor_morph_orig_z = fisherz(cor_morph_orig))%>%
  # group_by(Participant)%>%
  # mutate(cor_morph_orig_subj = cor(Prop.x, Prop.y, use = 'complete.obs'))%>%
  # # mutate(cor_morph_orig_z_subj = fisherz(cor_morph_orig_subj))%>%
  group_by(Participant, DATASET)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # subs
  ggplot(aes(DATASET, cor_morph_orig, colour = DATASET, fill = DATASET))+
  geom_half_violin(position = position_dodge(2), colour = FALSE, alpha = .3)+
  geom_jitter(width = .1,pch = 1, size = 2, alpha = .5)+
  geom_line(aes(group = Participant), colour = 'gray75', 
             size = .5, alpha = .3)+
    
  stat_summary(geom = 'errorbar', width = 0, size = 1.5)+
  stat_summary(geom = 'pointrange', width = 0, size = .5)+
    geom_hline(yintercept = 0, linetype = "dotted", size = 2, alpha  = .5)+
  theme_classic()+
    ylab("Similarity: morph - original (r)") +
  ggtitle("Off diagonal")+



  p$graphstyle1+
  # scale_y_continuous(breaks = c(0,.5, 1), limits = c(-.3,1))+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")

paper_plots$Representation_nodiag <-
  paper_plots$Representation_nodiag<- paper_plots$Representation_nodiag +
  theme(plot.title = element_text(size = 14),
        axis.title.x = element_blank())+
  scale_x_discrete(breaks=c("Global","ADFES","JEFFE"),
        labels=c("All", "High prot.", "Low prot."))+
  theme(legend.position = "none")

paper_plots$Representation_nodiag
  
```


correlations between confusion matrices


```{r}
confusion_byds_vt_full_coragg_ttest

confusion_byds_vt_full_ADFES_origi<- subset(confusion_byds_vt_full, 
                                            DATASET == "ADFES" & VideoType == "Original")%>%
  arrange(Participant, Emotion, Prediction)


confusion_byds_vt_full_JEFFE_origi<- subset(confusion_byds_vt_full, 
                                            DATASET != "ADFES" & VideoType == "Original")%>%
  arrange(Participant, Emotion, Prediction)


cor.test(confusion_byds_vt_full_ADFES_origi$Freq,confusion_byds_vt_full_ADFES_origi$Prop)$estimate
left_join(confusion_byds_vt_full_ADFES_origi,confusion_byds_vt_full_JEFFE_origi,
          by = c('Participant', 'Emotion', 'Prediction'))%>%
  group_by(Emotion, Prediction)%>%
  subset(Emotion != Prediction)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  
  # mutate(cor_adfes_jeffe_orig = cor.test(Prop.x, Prop.y, use = "complete")$estimate)%>%
  ggplot(aes(Prop.x, Prop.y))+
  geom_point()+
  geom_smooth(method = lm, se =F)+
   ggpubr::stat_cor()

# morph

confusion_byds_vt_full_ADFES_Morph<- subset(confusion_byds_vt_full, 
                                            DATASET == "ADFES" & VideoType == "Morph")%>%
  arrange(Participant, Emotion, Prediction)


confusion_byds_vt_full_JEFFE_Morph<- subset(confusion_byds_vt_full, 
                                            DATASET != "ADFES" & VideoType == "Morph")%>%
  arrange(Participant, Emotion, Prediction)


cor.test(confusion_byds_vt_full_ADFES_Morph$Freq,confusion_byds_vt_full_ADFES_Morph$Prop)$estimate

left_join(confusion_byds_vt_full_ADFES_origi,confusion_byds_vt_full_ADFES_Morph,
          by = c('Participant', 'Emotion', 'Prediction'))%>%
  group_by(Emotion, Prediction)%>%
  subset(Emotion != Prediction)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  
  # mutate(cor_adfes_jeffe_orig = cor.test(Prop.x, Prop.y, use = "complete")$estimate)%>%
  ggplot(aes(Prop.x, Prop.y))+
  geom_point()+
  geom_smooth(method = lm, se =F)+
   ggpubr::stat_cor()


# jeffe morph vs original


confusion_byds_vt_full_ADFES_Morph<- subset(confusion_byds_vt_full, 
                                            DATASET == "ADFES" & VideoType == "Morph")%>%
  arrange(Participant, Emotion, Prediction)


confusion_byds_vt_full_JEFFE_Morph<- subset(confusion_byds_vt_full, 
                                            DATASET != "ADFES" & VideoType == "Morph")%>%
  arrange(Participant, Emotion, Prediction)


cor.test(confusion_byds_vt_full_ADFES_Morph$Freq,confusion_byds_vt_full_ADFES_Morph$Prop)$estimate

left_join(confusion_byds_vt_full_JEFFE_origi,confusion_byds_vt_full_JEFFE_Morph,
          by = c('Participant', 'Emotion', 'Prediction'))%>%
  group_by(Emotion, Prediction)%>%
  subset(Emotion != Prediction)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  
  # mutate(cor_adfes_jeffe_orig = cor.test(Prop.x, Prop.y, use = "complete")$estimate)%>%
  ggplot(aes(Prop.x, Prop.y))+
  geom_point()+
  geom_smooth(method = lm, se =F)+
  ggpubr::stat_cor()



left_join(confusion_byds_vt_full_ADFES_Morph,confusion_byds_vt_full_JEFFE_Morph,
          by = c('Participant', 'Emotion', 'Prediction'))%>%
  group_by(Emotion, Prediction)%>%
  # subset(Emotion != Prediction)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  
  # mutate(cor_adfes_jeffe_orig = cor.test(Prop.x, Prop.y, use = "complete")$estimate)%>%
  ggplot(aes(Prop.x, Prop.y))+
  geom_point()+
  geom_smooth(method = lm, se =F)+
  ggpubr::stat_cor()



```




```{r}

# valence
paper_plots$cor_morph_orig_val<- bind_rows(db_NT_lmer_correlation_merged3_agg, db_NT_lmer_correlation_merged3_agg1)%>%
    mutate(DATASET = as.factor(DATASET))%>%
    mutate(DATASET = relevel(DATASET, ref = 'All'))%>%
    group_by(DATASET)%>%
    mutate(mean_val_cor = mean(valence_morph_orig_cor))%>%
  ggplot(aes(DATASET,valence_morph_orig_cor, colour = DATASET, fill = DATASET))+
  geom_half_violin(position = position_dodge(2), colour = FALSE, alpha = .3)+
  geom_jitter( width = .1,pch = 1, size = 2, alpha = .5)+
  geom_line(aes(group = ParticipantPrivateID), colour = 'gray75', 
             size = .5, alpha = .3)+
    
  stat_summary(geom = 'errorbar', width = 0, size = 1.5)+
  stat_summary(geom = 'pointrange', width = 0, size = .5)+
    geom_hline(yintercept = 0, linetype = "dotted", size = 2, alpha  = .5)+
  theme_classic()+
    ylab("Valence similarity \n Morph and Original")

paper_plots$cor_morph_orig_val<- paper_plots$cor_morph_orig_val+ 
  p$graphstyle1+
  scale_y_continuous(breaks = c(0, .5, 1), limits = c(-.3,1))+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  scale_x_discrete(breaks=c("All","ADFES","JEFFE"),
        labels=c("All", "High prot.", "Low prot."))+
  scale_color_discrete(name = "DATASET",
        labels=c("All", "High prot.", "Low prot."))+
  scale_fill_discrete(name = "DATASET",
        labels=c("All", "High prot.", "Low prot."))+
  theme(axis.title.x = element_blank())

paper_plots$cor_morph_orig_val<- paper_plots$cor_morph_orig_val+
   scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")

paper_plots$cor_morph_orig_val

```
intensity


```{r}
paper_plots$cor_morph_orig_int<- bind_rows(db_NT_lmer_correlation_merged3_agg, db_NT_lmer_correlation_merged3_agg1)%>%
    mutate(DATASET = as.factor(DATASET))%>%
    mutate(DATASET = relevel(DATASET, ref = 'All'))%>%
    group_by(DATASET)%>%
    mutate(mean_int_cor = mean(intensity_morph_orig_cor))%>%
  
  ggplot(aes(DATASET,intensity_morph_orig_cor, colour = DATASET, fill = DATASET))+
 geom_half_violin(position = position_dodge(2), colour = FALSE, alpha = .3)+
  geom_jitter( width = .1,pch = 1, size = 2, alpha = .5)+
  geom_line(aes(group = ParticipantPrivateID), colour = 'gray75', 
             size = .5, alpha = .3)+
    
  stat_summary(geom = 'errorbar', width = 0, size = 1.5)+
  stat_summary(geom = 'pointrange', width = 0, size = .5)+
    geom_hline(yintercept = 0, linetype = "dotted", size = 2, alpha  = .5)+
  theme_classic()+
    ylab("Intensity similarity \n Morph and Original")
  
paper_plots$cor_morph_orig_int

  
paper_plots$cor_morph_orig_int<- paper_plots$cor_morph_orig_int+ 
  p$graphstyle1+
  scale_y_continuous(breaks = c(-.5, 0, .5, 1), limits = c(-.6,1))+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  scale_x_discrete(breaks=c("All","ADFES","JEFFE"),
        labels=c("All", "High prot.", "Low prot."))+
  theme(legend.position = "none", axis.title.x = element_blank())

paper_plots$cor_morph_orig_int

```



```{r}

paper_plots$cor_morph_orig_nat <- bind_rows(db_NT_lmer_correlation_merged3_agg, db_NT_lmer_correlation_merged3_agg1)%>%
    mutate(DATASET = as.factor(DATASET))%>%
    mutate(DATASET = relevel(DATASET, ref = 'All'))%>%
    group_by(DATASET)%>%
    mutate(mean_nat_cor = mean(naturality_morph_orig_cor))%>%
  ggplot(aes(DATASET,naturality_morph_orig_cor, colour = DATASET, fill = DATASET))+
  geom_half_violin(position = position_dodge(2), colour = FALSE, alpha = .3)+
  geom_jitter( width = .1,pch = 1, size = 2, alpha = .5)+
  geom_line(aes(group = ParticipantPrivateID), colour = 'gray75', 
             size = .5, alpha = .3)+
    
  stat_summary(geom = 'errorbar', width = 0, size = 1.5)+
  stat_summary(geom = 'pointrange', width = 0, size = .5)+
    geom_hline(yintercept = 0, linetype = "dotted", size = 2, alpha  = .5)+
  theme_classic()+
      ylab("Naturality similarity \n Morph and Original")+
  scale_x_discrete(breaks=c("All","ADFES","JEFFE"),
        labels=c("All", "High prot.", "Low prot."))

paper_plots$cor_morph_orig_nat

```


```{r}

  # geom_line(aes(group = ParticipantPrivateID), colour = 'gray75', size = .1, alpha = .5)+
  # geom_boxplot( width = .3, size = 1, alpha = .5)+
  # geom_jitter(width = .1,pch = 21, size = 3, alpha = .7)+
  #  
  #   stat_summary(geom = 'point', size = 5)+
  #   theme_classic()+
  # 
  # 
  #   ylab("Naturality similarity \n Morph and Original")


 

  
  
paper_plots$cor_morph_orig_nat<- paper_plots$cor_morph_orig_nat+ 
  p$graphstyle1+
  scale_y_continuous(breaks = c(-.5, 0, .5, 1), limits = c(-.7,1))+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  # scale_x_discrete(breaks=c("All","ADFES","JEFFE"),
  #       labels=c("All", "High prot.", "Low prot."))+
  theme(legend.position = "none", axis.title.x = element_blank())
paper_plots$cor_morph_orig_nat


```



solve the accuracy issue
```{r}
# acc
paper_plots$cor_morph_orig_acc <- bind_rows(db_NT_lmer_correlation_merged3_agg, db_NT_lmer_correlation_merged3_agg1)%>%
    mutate(DATASET = as.factor(DATASET))%>%
    mutate(DATASET = relevel(DATASET, ref = 'All'))%>%
    group_by(DATASET)%>%
    mutate(mean_acc_cor = mean(acc_morph_orig_cor*(-1)))%>%
  ggplot(aes(DATASET,acc_morph_orig_cor* (-1), colour = DATASET))+
  # geom_violin(trim = FALSE, width = .5)+
    # geom_point(pch = 21, size = 3, alpha = .7)+
    # geom_boxplot(aes(y=mean_acc_cor), width = .3, size = 1, colour = 'darkred')+
  geom_boxplot( width = .3, size = 1)+
  geom_jitter(width = .1,pch = 21, size = 3, alpha = .7)+
   geom_line(aes(group = ParticipantPrivateID), colour = 'gray75', 
             size = .5, alpha = .3)+
    stat_summary(geom = 'point', size = 5)+
    theme_classic()+
    ylab("Accuracy similarity \n Morph and Original")




  
  
paper_plots$cor_morph_orig_acc<- paper_plots$cor_morph_orig_acc+ 
  p$graphstyle1+
  scale_y_continuous(breaks = c(-1, -.5, 0, .5, 1), limits = c(-1,1))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(breaks=c("All","ADFES","JEFFE"),
        labels=c("All", "High prot.", "Low prot."))+
  theme(legend.position = "none", axis.title.x = element_blank())
paper_plots$cor_morph_orig_acc



```





```{r}


paper_plots$correlations_morph_orig<-
paper_plots$cor_morph_orig_val+  theme(legend.position = "none", axis.title.x = element_blank(),
                                     axis.text.x = element_blank())+
paper_plots$cor_morph_orig_int+  theme(legend.position = "none", axis.title.x = element_blank(),
                                     axis.text.x = element_blank(), axis.text.y = element_blank())+
paper_plots$cor_morph_orig_nat+  theme(legend.position = "none", axis.title.x = element_blank(), axis.text.y = element_blank())+
paper_plots$cor_morph_orig_acc+  theme(legend.position = "none", axis.title.x = element_blank())+
plot_layout(nrow = 2, ncol = 2)
            
paper_plots$correlations_morph_orig          
            guides = 'collect')& theme(legend.position = 'top')
  
ggsave("correlations_morph_orig.png", paper_plots$correlations_morph_orig, device = 'png', width = 10, height =7 , dpi = 900) 



```

```{r}

# db_NT_lmer_correlation <- dplyr::select(db_NT_lmer, c(ParticipantPrivateID, Video, VideoType, DATASET, Emotion,
#                                               AnswerRating_Intensity, AnswerRating_Valence, 
#                                               AnswerRating_Naturality, Recognacc,
#                                               # Answe


# compute the correlations
View(db_NT_lmer_correlation_merged)


table(is.na(db_NT_lmer_correlation_merged$matched))
db_NT_lmer_correlation_merged3 %>%
  # filter(matched == "YES")%>%
  group_by(ParticipantPrivateID, DATASET)%>%
  # mutate(intensity_morph_orig_cor = cor(AnswerRating_Intensity.x, AnswerRating_Intensity.y, "complete.obs"))%>%
  # mutate(valence_morph_orig_cor = cor(AnswerRating_Valence.x, AnswerRating_Valence.y, use = "complete.obs"))%>%
  # mutate(naturality_morph_orig_cor = cor(AnswerRating_Naturality.x, AnswerRating_Naturality.y,use= "complete.obs"))%>%
  mutate(acc_morph_orig_cor = cor.test(Recognacc.x, Recognacc.y, use = "complete.obs")$estimate)%>%
  group_by(ParticipantPrivateID, DATASET)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(x = DATASET, y = acc_morph_orig_cor, color = DATASET))+
     # geom_point(pch = 21, size = 3, alpha = .7)+
    # geom_boxplot(aes(y=mean_acc_cor), width = .3, size = 1, colour = 'darkred')+
  geom_boxplot( width = .3, size = 1)+
  geom_jitter(width = .1,pch = 21, size = 3, alpha = .7)+
   geom_line(aes(group = ParticipantPrivateID), colour = 'gray75', size = .1, alpha = .5)+
    stat_summary(geom = 'point', size = 5)+
    geom_hline(yintercept = 0, linetype = "dotted", size = 2, alpha  = .5)+
  theme_classic()

library(gghalves)
library(tidyverse)
library(ggplot2)

paper_plots$cor_morph_orig_acc<- bind_rows(db_NT_lmer_correlation_merged3_agg, db_NT_lmer_correlation_merged3_agg1)%>%
# db_NT_lmer_correlation_merged3_agg%>%
    mutate(DATASET = as.factor(DATASET))%>%
    mutate(DATASET = relevel(DATASET, ref = 'All'))%>%
    group_by(DATASET)%>%
    mutate(mean_acc_cor = mean(acc_morph_orig_cor*(-1)))%>%
  ggplot(aes(DATASET,acc_morph_orig_cor* (-1), color =DATASET, fill = DATASET))+
  geom_half_violin(position = position_dodge(2), colour = FALSE, alpha = .3)+
  
  geom_jitter( width = .1,pch = 1, size = 2, alpha = .5)+
  geom_line(aes(group = ParticipantPrivateID), colour = 'gray75', 
             size = .5, alpha = .3)+
    
  stat_summary(geom = 'errorbar', width = 0, size = 1.5)+
  stat_summary(geom = 'pointrange', width = 0, size = .5)+
    geom_hline(yintercept = 0, linetype = "dotted", size = 2, alpha  = .5)+
  theme_classic()+
      ylab("Accuracy similarity \n Morph and Original")+
  scale_x_discrete(breaks=c("All","ADFES","JEFFE"),
        labels=c("All", "High prot.", "Low prot."))
  
  
paper_plots$cor_morph_orig_acc <- paper_plots$cor_morph_orig_acc + 
  p$graphstyle1+
  scale_y_continuous(breaks = c(-.5, 0, .5, 1), limits = c(-.5,1))+
  scale_color_brewer(palette = "Dark2")+
  theme(legend.position = "none", axis.title.x = element_blank())+
  scale_fill_brewer(palette = "Dark2")
paper_plots$cor_morph_orig_acc




```



Panel


```{r}
library(patchwork)
paper_plots$correlations_morph_orig<-
paper_plots$cor_morph_orig_val+  
  theme(
        axis.title.x = element_blank(), 
        legend.position = "top") +
paper_plots$cor_morph_orig_int+  
  theme(legend.position = "none", 
        axis.title.x = element_blank(),
        axis.text.x = element_blank())+
  paper_plots$cor_morph_orig_nat+  
  theme(legend.position = "none")+
paper_plots$cor_morph_orig_acc+  
  theme(legend.position = "none", 
        axis.title.x = element_blank(),
         axis.text.x = element_blank())+
plot_layout(nrow = 2, ncol = 2)
            
# paper_plots$correlations_morph_orig +          
#             guides = 'colect') & theme(legend.position = 'top')

paper_plots$correlations_morph_orig
  


ggsave("Study1_panel_Similarity_morph_orig.tiff", paper_plots$correlations_morph_orig, 
       device = 'tiff', width = 10, height =7, dpi = 900) 

ggsave("Study1_panel_Similarity_morph_orig.png", paper_plots$correlations_morph_orig, 
       device = 'png', width = 10, height =7, dpi = 900) 
```


```


```{r}
GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, 
                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
  grp <- data[1, "group"]
  newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
  newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])

  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
      1))
    quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
    aesthetics$alpha <- rep(1, nrow(quantiles))
    both <- cbind(quantiles, aesthetics)
    quantile_grob <- GeomPath$draw_panel(both, ...)
    ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
  }
  else {
    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
  }
})

geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., 
                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, 
                              show.legend = NA, inherit.aes = TRUE) {
  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, 
        position = position, show.legend = show.legend, inherit.aes = inherit.aes, 
        params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
}


```