---
title: "Predicting emotion ratings plots"
author: "Helio"
date: "05/04/2021"
output: html_document
---



work with: load("D:/OneDrive - Nexus365/Face Morph Paper/Data/Study2_plots.RData"

to do: fix typos and clean
Style


Plotting


```{r}

# Plotting preferences
sf = 1
p$graphstyle <-  theme(#base plot theme
  # axis
  axis.line.y = element_line(),
  axis.line.x = element_line(),
  axis.text.x = element_text(size = 15+(sf+.5), family = "sans", colour = "black", hjust = .8), #angle = 45,
  axis.text.y = element_text(size = 15+(sf+.5), family = "sans", colour = "black"),
  #axis.ticks = element_blank(),
  #axis.text.y = element_text(size= 18, family = "Arial Narrow", colour="black"),
  axis.title.y=element_text(size = 16*(sf+.7), margin=margin(0,5,0,0)),
  axis.title.x=element_text(size = 16*(sf+.7), margin=margin(0,5,0,0)),
  
  # strips
  strip.background = element_blank(),
  strip.text.x = element_text(size = 12*(sf+.5),  colour = "black"),
  strip.text.y = element_text(size = 12*(sf+.5),  colour = "black"),
  
  # panel
  # panel.background = element_rect(colour = NA),
  # plot.background = element_rect(colour = NA),
  # panel.border = element_rect(colour = NA),
  # panel.border = element_blank(),
  # panel.grid.major = element_blank(),
  # panel.grid.minor = element_blank(),
  # panel.background = element_blank(),
  
  # legend
  # legend.title = element_text(size = 10*(sf+.3)),
  legend.position = "top",
  legend.direction = "horizontal",
  #legend.key.size = unit(.5, "cm"),
  #legend.text = element_text(size = 10*sf),
  legend.title=element_blank(),
  #legend.text = element_blank(),
  legend.key = element_rect(colour = "transparent", fill="transparent"),
  # text
  text=element_text(size = 16*(sf+.4), family = "sans"))
 
# 
install.packages("grid")
   library(grid)
    library(ggthemes)
theme_Publication <- function(base_size=14, base_family="helvetica") {
   
      (theme_foundation(base_size=base_size, base_family=base_family)
       + theme(plot.title = element_text(face = "bold",
                                         size = rel(1.2), hjust = 0.5),
               text = element_text(),
               panel.background = element_rect(colour = NA),
               plot.background = element_rect(colour = NA),
               panel.border = element_rect(colour = NA),
               axis.title = element_text(face = "bold",size = rel(1)),
               axis.title.y = element_text(angle=90,vjust =2),
               axis.title.x = element_text(vjust = -0.2),
               axis.text = element_text(), 
               axis.line = element_line(colour="black"),
               axis.ticks = element_line(),
               panel.grid.major = element_line(colour="#f0f0f0"),
               panel.grid.minor = element_blank(),
               legend.key = element_rect(colour = NA),
               legend.position = "bottom",
               legend.direction = "horizontal",
               legend.key.size= unit(0.2, "cm"),
               legend.margin = unit(0, "cm"),
               legend.title = element_text(face="italic"),
               plot.margin=unit(c(10,5,5,5),"mm"),
               strip.background=element_rect(colour="#f0f0f0",fill="#f0f0f0"),
               strip.text = element_text(face="bold")
          ))
      
}

scale_fill_Publication <- function(...){
      library(scales)
      discrete_scale("fill","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)

}

scale_colour_Publication <- function(...){
      library(scales)
      discrete_scale("colour","Publication",manual_pal(values = c("#386cb0","#fdb462","#7fc97f","#ef3b2c","#662506","#a6cee3","#fb9a99","#984ea3","#ffff33")), ...)

}
```



Valence

```{r}
paper_plots$ADFES_valence<- subset(db_ASC_NT, db_ASC_NT $Group == "NT" & db_ASC_NT$DATASET == 'ADFES')%>%
  filter(outlier_valence == FALSE)%>%
  group_by(VideoType,Emotion, Emotion2, DATASET)%>%
  mutate(mean_in = mean(AnswerRating_Valence, na.rm = TRUE))%>%
  group_by(ParticipantPrivateID,group_pp_emotion, VideoType,Emotion,Emotion2,DATASET)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # ggplot(aes(Emotion2, AnswerRating_Valence, colour = VideoType))+
  ggplot(aes(VideoType, AnswerRating_Valence, 
             color = VideoType, fill = VideoType))+
  geom_split_violin(color = FALSE, alpha = .3)+
  geom_smooth(aes(group = ParticipantPrivateID), method = 'lm', se = F, 
              color = "gray80", alpha = .5,size = .5)+
  geom_point(fill = NA, pch = 21, position = position_jitterdodge(), alpha = .5)+
  stat_summary(fun = mean, geom = 'pointrange', width = 0.1, size = .2,
               color = "black", alpha = .8,position=position_dodge(width=0.3)) +
  stat_summary(fun.data = mean_se, geom='errorbar', width = 0,
               size = .5, color = "black",alpha = .8, linetype = 'solid',
               position=position_dodge(width=0.3)) +
    facet_grid(~Emotion2)+
  geom_smooth(aes(group = Emotion2),method = 'lm', se = F, color = "Black",
               alpha = .8,size = 1)+
  theme_classic()+
  # xlab("Emotion")+
  ylab("Valence")+
  ggtitle("High prototypicality")

paper_plots$ADFES_valence

paper_plots$ADFES_valence<- paper_plots$ADFES_valence +
  p$graphstyle+
  scale_y_continuous(breaks = c(0, 50,100), limits = c(0,100))+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  theme(axis.title.x = element_blank(), axis.text.x = element_blank())
paper_plots$ADFES_valence





```

paper_plots$JEFFE_valence

```{r}
paper_plots$JEFFE_valence<- subset(db_ASC_NT, db_ASC_NT $Group == "NT" & db_ASC_NT$DATASET == 'JEFFE')%>%
  filter(outlier_valence == FALSE)%>%
  group_by(VideoType,Emotion, Emotion2, DATASET)%>%
  mutate(mean_in = mean(AnswerRating_Valence, na.rm = TRUE))%>%
  group_by(ParticipantPrivateID, VideoType,Emotion,Emotion2,DATASET)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(VideoType, AnswerRating_Valence, 
             color = VideoType, fill = VideoType))+
  geom_split_violin(color = FALSE, alpha = .3)+
  geom_smooth(aes(group = ParticipantPrivateID), method = 'lm', se = F, 
              color = "gray80", alpha = .5,size = .5)+
  geom_point(fill = NA, pch = 21, position = position_jitterdodge(), alpha = .5)+
  stat_summary(fun = mean, geom = 'pointrange', width = 0.1, size = .2,
               color = "black", alpha = .8,position=position_dodge(width=0.3)) +
  stat_summary(fun.data = mean_se, geom='errorbar', width = 0,
               size = .5, color = "black",alpha = .8, linetype = 'solid',
               position=position_dodge(width=0.3)) +
    facet_grid(~Emotion2)+
  geom_smooth(aes(group = Emotion2),method = 'lm', se = F, color = "Black",
               alpha = .8,size = 1)+
  theme_classic()+
  # xlab("Emotion")+
  ylab("Valence")+
  ggtitle("Low protypicality")



paper_plots$JEFFE_valence <- paper_plots$JEFFE_valence +
  p$graphstyle+
  scale_y_continuous(breaks = c(0, 50,100), limits = c(0,100))+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  theme(axis.title.x = element_blank(), axis.text.x = element_blank())

paper_plots$JEFFE_valence
```

intensity


```{r}
paper_plots$ADFES_intensity<- subset(db_ASC_NT, db_ASC_NT$Group == "NT" 
                                     & db_ASC_NT$DATASET == 'ADFES')%>%
  filter(outlier_intensity == FALSE)%>%
  group_by(VideoType,Emotion, Emotion2, DATASET)%>%
  mutate(mean_in = mean(AnswerRating_Intensity, na.rm = TRUE))%>%
  group_by(ParticipantPrivateID, VideoType,Emotion,Emotion2,DATASET)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(VideoType, AnswerRating_Intensity, 
             color = VideoType, fill = VideoType))+
  geom_split_violin(color = FALSE, alpha = .3)+
  geom_smooth(aes(group = ParticipantPrivateID), method = 'lm', se = F, 
              color = "gray80", alpha = .5,size = .5)+
  geom_point(fill = NA, pch = 21, position = position_jitterdodge(), alpha = .5)+
  stat_summary(fun = mean, geom = 'pointrange', width = 0.1, size = .2,
               color = "black", alpha = .8,position=position_dodge(width=0.3)) +
  stat_summary(fun.data = mean_se, geom='errorbar', width = 0,
               size = .5, color = "black",alpha = .8, linetype = 'solid',
               position=position_dodge(width=0.3)) +
    facet_grid(~Emotion2)+
  geom_smooth(aes(group = Emotion2),method = 'lm', se = F, color = "Black",
               alpha = .8,size = 1)+
  theme_classic()+
  ylab("Intensity")+
  ggtitle("High protypicality")
  # scale_fill_viridis_d()+

paper_plots$ADFES_intensity<- paper_plots$ADFES_intensity +
  p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  theme(axis.title.x = element_blank(), axis.text.x = element_blank())
paper_plots$ADFES_intensity
paper_plots$JeFEE_intensity


```


```{r}

paper_plots$JeFEE_intensity <- subset(db_ASC_NT, db_ASC_NT$Group == "NT" &
                                        db_ASC_NT$DATASET == 'JEFFE')%>%
  filter(outlier_intensity == FALSE)%>%
  group_by(VideoType,Emotion, Emotion2, DATASET)%>%
  mutate(mean_in = mean(AnswerRating_Intensity, na.rm = TRUE))%>%
  group_by(ParticipantPrivateID, VideoType,Emotion,Emotion2,DATASET)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(VideoType, AnswerRating_Intensity, 
             color = VideoType, fill = VideoType))+
  geom_split_violin(color = FALSE, alpha = .3)+
  geom_smooth(aes(group = ParticipantPrivateID), method = 'lm', se = F, 
              color = "gray80", alpha = .5,size = .5)+
  geom_point(fill = NA, pch = 21, position = position_jitterdodge(), alpha = .5)+
  stat_summary(fun = mean, geom = 'pointrange', width = 0.1, size = .2,
               color = "black", alpha = .8,position=position_dodge(width=0.3)) +
  stat_summary(fun.data = mean_se, geom='errorbar', width = 0,
               size = .5, color = "black",alpha = .8, linetype = 'solid',
               position=position_dodge(width=0.3)) +
    facet_grid(~Emotion2)+
  geom_smooth(aes(group = Emotion2),method = 'lm', se = F, color = "Black",
               alpha = .8,size = 1)+
  theme_classic()+
  ylab("Intensity")+
  ggtitle("Low prototypicality")
  # scale_fill_viridis_d()+

  
  
  # scale_colour_Publication()+
paper_plots$JeFEE_intensity<- paper_plots$JeFEE_intensity +
  p$graphstyle+
  scale_y_continuous(breaks = c(0, 50,100), limits = c(0,100))+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  theme(axis.title.x = element_blank(), axis.text.x = element_blank())
paper_plots$JeFEE_intensity




```


Naturality

<!-- paper_plots$ADFES_Naturality -->
```{r}

paper_plots$ADFES_Naturality<- 
  # keep just NT sample and a specific dataset to plot
  subset(db_ASC_NT, db_ASC_NT $Group == "NT"&  db_ASC_NT$DATASET == 'ADFES')%>%
  
  # filter out outliers
  filter(outlier_naturality == FALSE)%>%
  # summarize across participants
  group_by(VideoType,Emotion, Emotion2, DATASET)%>%
  mutate(mean_in = mean(AnswerRating_Naturality, na.rm = TRUE))%>%
  # summarise within participant
  group_by(ParticipantPrivateID, VideoType,Emotion,Emotion2,DATASET)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  
  # 
  ggplot(aes(VideoType, AnswerRating_Naturality, 
             color = VideoType, fill = VideoType))+
  # create half violins splits
  geom_split_violin(color = FALSE, alpha = .3)+
  
  # represent participant variability
  geom_smooth(aes(group = ParticipantPrivateID), method = 'lm', se = F, 
              color = "gray80", alpha = .5,size = .5)+
  # each point is a single participant
  geom_point(fill = NA, pch = 21, position = position_jitterdodge(), alpha = .5)+
  # plot mean per conditions
  stat_summary(fun = mean, geom = 'pointrange', width = 0.1, size = .2,
               color = "black", alpha = .8,position=position_dodge(width=0.3)) +
  stat_summary(fun.data = mean_se, geom='errorbar', width = 0,
               size = .5, color = "black",alpha = .8, linetype = 'solid',
               position=position_dodge(width=0.3)) +
    facet_grid(~Emotion2)+
  # average trend
   geom_smooth(aes(group = Emotion),method = 'lm', se = F, color = "Black",
               alpha = .8,size = 1)+
  theme_classic()+
  ylab("Naturality")+
  ggtitle("High prototypicality")


paper_plots$ADFES_Naturality<- paper_plots$ADFES_Naturality +
  p$graphstyle+
  scale_y_continuous(breaks = c(0, 50,100), limits = c(0,100))+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  theme(axis.text.x = element_blank(), axis.title.x = element_blank())
paper_plots$ADFES_Naturality



```

<!-- paper_plots$JEFFE_Naturality -->
```{r}
install.packages("see")

library(see)

paper_plots$JEFFE_Naturality


paper_plots$JEFFE_Naturality<- subset(db_ASC_NT, db_ASC_NT $Group == "NT" & db_ASC_NT$DATASET == 'JEFFE')%>%
  filter(outlier_naturality == FALSE)%>%
  group_by(VideoType,Emotion, Emotion2, DATASET)%>%
  mutate(mean_in = mean(AnswerRating_Naturality, na.rm = TRUE))%>%
  group_by(ParticipantPrivateID, VideoType,Emotion,Emotion2,DATASET)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(VideoType, AnswerRating_Naturality, 
             color = VideoType, fill = VideoType))+
  geom_split_violin(color = FALSE, alpha = .3)+
  geom_smooth(aes(group = ParticipantPrivateID), method = 'lm', se = F, 
              color = "gray80", alpha = .5,size = .5)+
  geom_point(fill = NA, pch = 21, position = position_jitterdodge(), alpha = .5)+
  stat_summary(fun = mean, geom = 'pointrange', width = 0.1, size = .2,
               color = "black", alpha = .8,position=position_dodge(width=0.3)) +
  stat_summary(fun.data = mean_se, geom='errorbar', width = 0,
               size = .5, color = "black",alpha = .8, linetype = 'solid',
               position=position_dodge(width=0.3)) +
    facet_grid(~Emotion2)+
  geom_smooth(aes(group = Emotion2),method = 'lm', se = F, color = "Black",
               alpha = .8,size = 1)+
  theme_classic()+
  xlab("Emotion")+
  ylab("Naturality")+
  ggtitle("Low prototypicality")

  

paper_plots$JEFFE_Naturality<- paper_plots$JEFFE_Naturality +
  p$graphstyle+
  scale_y_continuous(breaks = c(0, 50,100), limits = c(0,100))+
  scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  theme(axis.text.x = element_blank(), axis.title.x = element_blank())
paper_plots$JEFFE_Naturality


```



Accuracy

Accuracy

```{r}

paper_plots$ADFES_acc <- subset(db_ASC_NT, db_ASC_NT$Group == "NT"
                                & db_ASC_NT$DATASET == 'ADFES')%>%
  # filter(outlier_valence == FALSE)%>%
  group_by(VideoType,Emotion, Emotion2, DATASET)%>%
  mutate(mean_acc = mean(Recognacc, na.rm = TRUE))%>%
  group_by(ParticipantPrivateID, VideoType,Emotion,Emotion2,DATASET)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(VideoType, Recognacc, 
             color = VideoType, fill = VideoType))+
  geom_split_violin(color = FALSE, alpha = .3)+
  geom_smooth(aes(group = ParticipantPrivateID), method = 'lm', se = F, 
              color = "gray80", alpha = .5,size = .5)+
  geom_point(fill = NA, pch = 21, position = position_jitterdodge(), alpha = .5)+
  stat_summary(fun = mean, geom = 'pointrange', width = 0.1, size = .2,
               color = "black", alpha = .8,position=position_dodge(width=0.3)) +
  stat_summary(fun.data = mean_se, geom='errorbar', width = 0,
               size = .5, color = "black",alpha = .8, linetype = 'solid',
               position=position_dodge(width=0.3)) +
    facet_grid(~Emotion2)+
  geom_smooth(aes(group = Emotion2),method = 'lm', se = F, color = "Black",
               alpha = .8,size = 1)+
  theme_classic()+
  ylab("Accuracy")+
  ggtitle("High prototypicality")

paper_plots$ADFES_acc

paper_plots$ADFES_acc<- paper_plots$ADFES_acc +
  p$graphstyle+
  scale_y_continuous(breaks = c(0, .5,1), limits = c(0,1))+
 scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  theme(axis.text.x = element_blank(), axis.title.x = element_blank())
paper_plots$ADFES_acc




```

paper_plots$JEFFE_acc

```{r}

paper_plots$JEFFE_acc<- subset(db_ASC_NT, db_ASC_NT $Group == "NT" 
                               & db_ASC_NT$DATASET == 'JEFFE')%>%
  filter(outlier_valence == FALSE)%>%
  group_by(VideoType,Emotion, Emotion2, DATASET)%>%
  mutate(mean_acc = mean(Recognacc, na.rm = TRUE))%>%
  group_by(ParticipantPrivateID, VideoType,Emotion,Emotion2,DATASET)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(VideoType, Recognacc, 
             color = VideoType, fill = VideoType))+
  geom_split_violin(color = FALSE, alpha = .3)+
  geom_smooth(aes(group = ParticipantPrivateID), method = 'lm', se = F, 
              color = "gray80", alpha = .5,size = .5)+
  geom_point(fill = NA, pch = 21, position = position_jitterdodge(), alpha = .5)+
  stat_summary(fun = mean, geom = 'pointrange', width = 0.1, size = .2,
               color = "black", alpha = .8,position=position_dodge(width=0.3)) +
  stat_summary(fun.data = mean_se, geom='errorbar', width = 0,
               size = .5, color = "black",alpha = .8, linetype = 'solid',
               position=position_dodge(width=0.3)) +
    facet_grid(~Emotion2)+
  geom_smooth(aes(group = Emotion2),method = 'lm', se = F, color = "Black",
               alpha = .8,size = 1)+
  theme_classic()+
  ylab("Accuracy")+
  ggtitle("Low Prototypicality")



paper_plots$JEFFE_acc<- paper_plots$JEFFE_acc +
  p$graphstyle+
  scale_y_continuous(breaks = c(0, .5,1), limits = c(0,1))+
 scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  theme(axis.text.x = element_blank(), axis.title.x = element_blank())

paper_plots$ADFES_acc
paper_plots$JEFFE_acc



```



aggregated accuracy across emotions



```{r}


db_ASC_NT$DATASETnew<- if_else(db_ASC_NT$DATASET == "ADFES", "High prototypicality",
                               "Low prototypicality")
paper_plots$acc_agg1<- subset(db_ASC_NT, db_ASC_NT $Group == "NT")%>%
  filter(outlier_valence == FALSE)%>%
  # group_by(VideoType,Emotion, Emotion2, DATASET)%>%
  # mutate(mean_acc = mean(Recognacc, na.rm = TRUE))%>%
  group_by(ParticipantPrivateID, VideoType,DATASETnew)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(VideoType, Recognacc, 
             color = VideoType, fill = VideoType))+
  
  geom_split_violin(color = FALSE, alpha = .3)+
  geom_smooth(aes(group = ParticipantPrivateID), method = 'lm', se = F, 
              color = "gray80", alpha = .5,size = .5)+
  geom_point(fill = NA, pch = 21, position = position_jitterdodge(), alpha = .5)+
  stat_summary(fun = mean, geom = 'pointrange', width = 0.1, size = .2,
               color = "black", alpha = .8,position=position_dodge(width=0.3)) +
  stat_summary(fun.data = mean_se, geom='errorbar', width = 0,
               size = .5, color = "black",alpha = .8, linetype = 'solid',
               position=position_dodge(width=0.3)) +
  geom_smooth(aes(group = DATASETnew),method = 'lm', se = F, color = "Black",
               alpha = .8,size = 1)+
    facet_grid(~DATASETnew)+
  geom_smooth(aes(group = VideoType),method = 'lm', se = F, color = "Black",
               alpha = .8,size = 1)+
  
  theme_classic()+
  ylab("Accuracy")

paper_plots$acc_agg1
paper_plots$acc_agg1<- paper_plots$acc_agg1 +
  p$graphstyle+
  scale_y_continuous(breaks = c(.2, .6,1), limits = c(.2,1))+
 scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  theme(axis.text.x = element_blank(), axis.title.x = element_blank())

paper_plots$acc_agg1

```



```{r}
paper_plots$acc_agg2<- subset(db_ASC_NT, db_ASC_NT $Group == "NT")%>%
  filter(outlier_valence == FALSE)%>%
  # group_by(VideoType,Emotion, Emotion2, DATASET)%>%
  # mutate(mean_acc = mean(Recognacc, na.rm = TRUE))%>%
  group_by(ParticipantPrivateID, VideoType,DATASETnew)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(DATASETnew, Recognacc, 
             color = VideoType, fill = VideoType))+
  
  geom_split_violin(color = FALSE, alpha = .3)+
  geom_smooth(aes(group = ParticipantPrivateID), method = 'lm', se = F, 
              color = "gray80", alpha = .5,size = .5)+
  geom_point(fill = NA, pch = 21, position = position_jitterdodge(), alpha = .5)+
  stat_summary(fun = mean, geom = 'pointrange', width = 0.1, size = .2,
               color = "black", alpha = .8,position=position_dodge(width=0.3)) +
  stat_summary(fun.data = mean_se, geom='errorbar', width = 0,
               size = .5, color = "black",alpha = .8, linetype = 'solid',
               position=position_dodge(width=0.3)) +
  geom_smooth(aes(group = DATASETnew),method = 'lm', se = F, color = "Black",
               alpha = .8,size = 1)+
    # facet_grid(~DATASET)+
  geom_smooth(aes(group = VideoType),method = 'lm', se = F,
               alpha = .8,size = 1)+
  
  theme_classic()+
  ylab("Accuracy")


paper_plots$acc_agg2
paper_plots$acc_agg2<- paper_plots$acc_agg2 +
  p$graphstyle+
  scale_y_continuous(breaks = c(.2, .6,1), limits = c(.2,1))+
 scale_color_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  theme( axis.title.x = element_blank())

paper_plots$acc_agg2


paper_plots$panel_acc_agg <- 
 (paper_plots$acc_agg1+ paper_plots$acc_agg2)+
 
  plot_layout(guides = "collect") & theme(legend.position = 'top')

paper_plots$panel_acc_agg <- paper_plots$panel_acc_agg+
  plot_annotation(tag_levels = 'A')

# paper_plots$acc_agg2
paper_plots$panel_acc_agg

ggsave("panel_acc_agg.png", paper_plots$panel_acc_agg, 
       device = 'png', width = 12, height =6, dpi = 900)

```

Panel - valence,naturality, intensity and accuracy


```{r}
library(patchwork)

paper_plots$panel_allratings<- 
  ( 
    paper_plots$ADFES_valence+ paper_plots$JEFFE_valence+
   paper_plots$ADFES_intensity+  paper_plots$JeFEE_intensity+
   paper_plots$ADFES_Naturality+  paper_plots$JEFFE_Naturality+ 
  paper_plots$ADFES_acc+  paper_plots$JEFFE_acc)+
  # theme(legend.position = 'top')+
  plot_layout(ncol = 2)+
  plot_annotation(tag_levels = 'A')

  

paper_plots$panel_allratings


```



Panel seems too tight

Panel Valence


```{r}
paper_plots$panel_valence <- 
 paper_plots$ADFES_valence+ paper_plots$JEFFE_valence+
 
  plot_layout(guides = "collect") & theme(legend.position = 'top')

paper_plots$panel_valence <-paper_plots$panel_valence+
  plot_annotation(tag_levels = 'A')

paper_plots$panel_valence

ggsave("panel_valence.png", paper_plots$panel_valence, 
       device = 'png', width = 12, height =6, dpi = 900) 

```



Pane Intensity

Panel Valence


```{r}
paper_plots$panel_intensity <- 
 paper_plots$ADFES_intensity+ paper_plots$JeFEE_intensity+
 
  plot_layout(guides = "collect") & theme(legend.position = 'top')

# plot annotation needs to be used after using plot layout

paper_plots$panel_intensity <-paper_plots$panel_intensity+
  plot_annotation(tag_levels = 'A')

paper_plots$panel_intensity

ggsave("panel_intensity.png", paper_plots$panel_intensity, 
       device = 'png', width = 12, height =6, dpi = 900) 

```



naturality


```{r}

paper_plots$panel_maturality <- 
 paper_plots$ADFES_Naturality + paper_plots$JEFFE_Naturality +
 
  plot_layout(guides = "collect") & theme(legend.position = 'top')

# plot annotation needs to be used after using plot layout

paper_plots$panel_maturality  <-paper_plots$panel_maturality +
  plot_annotation(tag_levels = 'A')

paper_plots$panel_maturality 

ggsave("panel_maturality .png", paper_plots$panel_maturality , 
       device = 'png', width = 12, height =6, dpi = 900) 

```


accurcay panel

```{r}

paper_plots$panel_accuracy <- 
 paper_plots$ADFES_acc + paper_plots$JEFFE_acc +
 
  plot_layout(guides = "collect") & theme(legend.position = 'top')

# plot annotation needs to be used after using plot layout

paper_plots$panel_accuracy  <- paper_plots$panel_accuracy +
  plot_annotation(tag_levels = 'A')

paper_plots$panel_accuracy

ggsave("panel_accuracy.png", paper_plots$panel_accuracy , 
       device = 'png', width = 12, height =6, dpi = 900) 


```


Store into image
```{r}
save(paper_analyses, paper_plots, plots_paper, p, db_ASC_NT, 
     file = "Study2_plots.RData")


```
